---
title: "Extracting S1 global"
params: 
  ExperimentID:
  rootdir: /home/user/Desktop/Documents/TimeSocialDistancing
output:
  html_document: 
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    toc: yes
---



```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = F)
```

```{r, include= F}
library(tidyverse)
source('helpers.R')
library(rmarkdown)
library(stringr)
```

#Read and Describe Data
```{r}
##Extracting 1-Back


OrigNback <- gimmedata(DataDir = file.path(params$rootdir,'data'),UniqueName = '.back',Session = '1') 
#1,760,000 obs

Nback <- OrigNback  %>%
  filter(str_detect(display, "block1back") | str_detect(display, "block3back")) %>%
  select(`Experiment ID`, Session, PID, Run, UniqueName, ILI, duration, randomise_blocks,`Zone Type`, duration, Response, `Reaction Time`, Correct, Attempt, `UTC Timestamp`, `Participant Private ID`, `Spreadsheet Name`) %>%
  rename(country = `Experiment ID`,
          nback = UniqueName,
        Zone.Type = `Zone Type`,
        randomblock = randomise_blocks,
          Spreadsheet = `Spreadsheet Name`,
         timestamp = `UTC Timestamp`,
         Reaction.Time = `Reaction Time`)  %>%
  mutate(timestamp = as.numeric((as.character(timestamp))),
         ILI = as.factor(ifelse(ILI  == 1500, "1500ms", "1800ms")),
         condition = ifelse(duration == "45s"  & ILI == "1500ms", 1, 0),
         condition = ifelse(duration == "90s" & ILI == "1500ms", 2, condition),
         condition = ifelse(duration == "45s"  & ILI == "1800ms", 3, condition),
         condition = ifelse(duration == "90s"  & ILI == "1800ms", 4, condition),
         Spreadsheet = ifelse(Spreadsheet == "nback1" | Spreadsheet == "n_back1", "n_back1", "n_back2"),
                          country = ifelse(country =="15684", "Greece", country),
                          country = ifelse(country =="16612", "Japan", country),
                          country = ifelse(country =="16144", "Turkey", country),
                          country = ifelse(country =="16095", "Italy", country),
                          country = ifelse(country == "16257", "Canada", country),
                          country = ifelse(country =="16271" | country == "16272", "Colombia", country),
                          country = ifelse(country =="16349" | country == "18453", "India", country),
                          country = ifelse(country == "15096" | country == "16303", "France", country),
         country = ifelse(country == "17423" |country == "19856" | country == "19880" | country == "19904"| country == "20044", "Argentina", country)) %>%
  mutate(PID = ifelse(country %in% c("India", "Canada", "Colombia"), `Participant Private ID`, PID)) %>%
  select(-`Participant Private ID`)

#1,492,189
```



```{r}
#list of participants to remove --> some participants logged twice or 3 x with a different login
#removing which participants ID that we don't want
participants_to_rm = c("1377295", "1373766", "1347792", "1358571","1348787","1318460",  "1347194", "1366463", "1330740", "1314652")
Nback<- Nback %>%
  filter(!(PID %in% participants_to_rm))


Nback %>%
  count(PID)   #1190 participants

```



#Read spreadsheets used for each trials and add variable that indicates the number of target letters
```{r}



sprdsheet1b1 <-read.csv2("/home/user/Desktop/Documents/TimeSocialDistancing/data/spreadsheet1back_1.csv",  sep = ",") %>%
  mutate(Spreadsheet = "n_back1")
sprdsheet1b2 <-read.csv2("/home/user/Desktop/Documents/TimeSocialDistancing/data/spreadsheet1back_2.csv", sep = ",")%>%
  mutate(Spreadsheet = "n_back2")
sprdsheet3b1 <-read.csv2("/home/user/Desktop/Documents/TimeSocialDistancing/data/spreadsheet3back_1.csv", sep = ",")%>%
  mutate(Spreadsheet = "n_back1")
sprdsheet3b2 <-read.csv2("/home/user/Desktop/Documents/TimeSocialDistancing/data/spreadsheet3back_2.csv", sep = ",")%>%
  mutate(Spreadsheet = "n_back2")


sprdsheet <- bind_rows(sprdsheet1b1, sprdsheet1b2, sprdsheet3b1, sprdsheet3b2) %>%
   mutate(condition = ifelse(duration == "45s"  & ILI == 1500, 1, 0),
         condition = ifelse(duration == "90s" & ILI == 1500, 2, condition),
         condition = ifelse(duration == "45s"  & ILI == 1800, 3, condition),
         condition = ifelse(duration == "90s"  & ILI == 1800, 4, condition)) %>%
   filter(display == "block1back" | display == "block3back") %>%
        mutate(nback = ifelse(display == "block1back", "1back", "3back"))

 

nb_target <- sprdsheet %>%
  filter(condition != 0) %>%
  group_by(nback, Spreadsheet, condition) %>%
  summarise(ntarget = sum(ANSWER == "Left"), notarget = sum(ANSWER == "Down"))
nb_target

Nback <- left_join(Nback, nb_target, by = c( "nback", "Spreadsheet", "condition"))

Nback %>%
  filter(is.na(notarget))

```





#Retrospective / prospective
```{r}
#add a column "block number" identifying each trial of session 1
#keep only first Run 1 for participants that did 2 or 3 Run1

Nback <- Nback %>%
  mutate(end = `Zone.Type` == "response_rating_scale_likert",
         block_nb = cumsum(end),
         block_nb = ifelse(end == T, block_nb - 1, block_nb)) %>%
  select(-end)


retrosp <- Nback %>%
  group_by(PID, Run, condition) %>%
  filter(!is.na(condition)) %>%
  summarise(block_nb = first(block_nb),timestamp = first(timestamp)) %>%
  group_by(PID) %>%
  dplyr::slice(which.min(timestamp))

Nback <- Nback %>%
  mutate(retro.pro = ifelse(
    block_nb %in% retrosp$block_nb, "retrospective",  "prospective"))
  

Nback %>%
  group_by(block_nb) %>%
  summarise(retro.pro = first(retro.pro)) %>%
  count(retro.pro)


nb_obs <- Nback %>%
  group_by(country) %>%
  summarise(observations = n())
nb_obs



nb_subjects <- Nback %>%
  group_by(PID) %>%
  summarise(country = first(country)) %>%
  group_by(country) %>%
  summarise(numbersubjects = n())
nb_subjects


Nback %>%
  count(PID)   #1190 PID



```






```{r}
ConfTrack <- gimmedata(DataDir = file.path(params$rootdir,'data'),UniqueName = 'ConfinementTrack',Session = '1') %>%
  mutate(PID = ifelse(is.na(PID), `Participant Private ID`, PID)) %>%
  select(`Experiment ID`, Session, PID, Run, `Question Key`, `Response`, `UTC Timestamp`)

#verify number of ID after selection with criterion
countID <- ConfTrack %>%
    group_by(`Experiment ID`, PID) %>%
    summarise(PID = first(PID)) %>%
  group_by(`Experiment ID`) %>%
  summarise(n = n())
countID

ConfTrack %>%
  filter(`Question Key` %in% 'ConfStage' | `Question Key` %in% 'ConfStage-2') %>%
    group_by(`Experiment ID`, PID) %>%
    summarise(PID = first(PID)) %>%
  group_by(`Experiment ID`) %>%
  summarise(n = n())


# Translation "during"
during <- c("during", "pendant", "κατά τη διάρκεια", "sırasında", "durante", "規制（自粛）中", "Durante")


tracker <- ConfTrack %>%
  filter(`Question Key` %in% 'ConfStage' | `Question Key` %in% 'ConfStage-2') %>%
  mutate(Conftrack = Response) %>%
  select(PID, Run, Conftrack)

#number of occurence for each Conftracker response
tracker %>%
  group_by(Conftrack, Run) %>%
  summarise(n = n())

#merge Conftracker and Nback, keep only responses for run made during confinement.
Nback <- left_join(Nback, tracker, by = c("PID", "Run")) %>%
  filter(Conftrack %in% during)





#verify number of participant for each country, no colombian data
nb_subjects <- Nback %>%
  group_by(PID) %>%
  summarise(country = first(country)) %>%
  group_by(country) %>%
  summarise(numbersubjects = n())
nb_subjects


Nback %>%
  count(PID)   #1190 --> 1140 PID



```







  
#Deal with attempts
```{r}

##keyboard response Attempts
Table_Attempts <- Nback %>%  
  group_by(Attempt) %>%
  count() %>%
  filter(as.numeric(Attempt) <10)
paged_table(Table_Attempts)
# ~ out of ~    #%

Nback <- Nback %>%            #removing all responses with more than one Attempt
  filter( Zone.Type != "response_keyboard" | Attempt %in% c("1", NA))
#~ 795 000 obs -->752 000 obs


##Response text entry and likert Attempts

Nback %>% 
  filter(Zone.Type == "response_rating_scale_likert") %>%
  group_by(Attempt) %>%
  count()
#only one Attempts

Nback %>% 
  filter(Zone.Type == "response_text_entry") %>%
  group_by(Attempt) %>%
  count()
# + 50 responses with more than 1 Attempts

entry_attempt <- Nback %>% 
  filter(Zone.Type == "response_text_entry" & Attempt > 1) 
  
  Nback %>% 
    filter(Zone.Type == "response_text_entry") %>%
    filter(PID %in% entry_attempt$PID
           & nback %in% entry_attempt$nback 
           & randomblock %in% entry_attempt$randomblock )
#the responses for both attempts are identical --> keep the first one
  
  
  Nback <- Nback %>%            #removing all responses with more than one Attempt
  filter( Zone.Type != "response_text_entry" | Attempt %in% c("1", NA))
  
  

  #PROBLEM WITH TURKEY: DUPLICATE RESPONSE
  Nback <- Nback %>% distinct


```



#Number of responses   #few trials with too much responses, but lots of trials with few responses
```{r}
Nback %>%
  group_by(block_nb, .add = T) %>%
  filter(Response %in% c("Left", "Down")) %>%
  summarise(n= n(), duration = first(duration)) %>%
  group_by(duration, n) %>%
  summarise(nn = n())

number_resp = Nback %>%
   group_by(duration, ILI, nback) %>%
  group_by(block_nb, .add = T) %>%
  filter(Response %in% c("Left", "Down")) %>%
  summarise(n = n(), duration = first(duration))

number_resp %>%
  filter(!is.na(duration)) %>%
  ggplot(aes(n, group = duration, colour = duration)) +
  facet_grid(duration~ILI) +
           geom_histogram(position = "dodge", binwidth=1,
                   colour = "black" , fill="white") +
  labs(y = "count", x = "Number of Responses", title ="Number of responses (Down or Left) for 45s and 90s tasks") +
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
  # scale_x_continuous(limits = c(0, 70), breaks = seq(from = 0, to = 70, by = 5))

#some task have 2 times or 3 times more responses than expected


nbresp <- Nback %>%
  filter(Zone.Type == "response_keyboard") %>%
  select(block_nb, condition) %>%
    group_by(block_nb) %>%
summarise(n = n(),condition = first(condition))
nbresp

blocktorm15 <- nbresp %>%
  filter(condition == 5 | condition == 1) %>%
  filter(is.na(block_nb) | n > 65)

blocktorm26 <- nbresp %>%
  filter(condition == 6 | condition == 2) %>%
  filter(is.na(block_nb) | n>125)

blocktorm37 <- nbresp %>%
  filter(condition == 3 | condition == 7) %>%
  filter(is.na(block_nb) | n > 57)

blocktorm48 <- nbresp %>%
  filter(condition == 4 | condition == 8) %>%
  filter(is.na(block_nb) | n>107)

blocktorm <- bind_rows(blocktorm15, blocktorm26, blocktorm37, blocktorm48) #8 blocks


Nback <- Nback %>%
  filter(!(block_nb %in% blocktorm$block_nb))

blocknb <-Nback %>%
  group_by(block_nb) %>%
  summarise(n = n()) 
blocknb
#11,933 trials
```







##Filtering and formatting data
```{r}

# Remove excess tasks (for duration estimation and likert response columns)
first_trial <- Nback %>%   #15515 tasks
  filter(Zone.Type == "response_text_entry") %>%
  group_by(PID) %>%
  group_by(nback, .add =T) %>%
  group_by(Run, .add =T) %>%
  group_by(randomblock, .add =T) %>%
  dplyr::slice(which.min(timestamp)) %>%
  select(block_nb)


trials_to_rm <- setdiff(blocknb$block_nb, first_trial$block_nb)  #525 trials

Nback <- Nback %>%
        filter(!(block_nb %in% trials_to_rm))  # --> 1,284,896 observations



#merge entry response (likert scale and duration estimation) with other responses
df1 <- Nback %>% 
  filter(Zone.Type == "response_keyboard") %>%
  select(-timestamp,-Zone.Type) 

df2 <-Nback %>% 
  filter(Zone.Type == "response_text_entry" | Zone.Type == "response_rating_scale_likert") %>% 
  select(-timestamp, - Reaction.Time, - Attempt, -retro.pro, , - ntarget, -notarget) %>% 
  mutate(Response = as.character(Response)) %>% 
  pivot_wider(values_from = Response, names_from = Zone.Type) 


Nback_all <- left_join(df1, df2, by = c("PID", "country", "Session", "nback", "randomblock", "Run", "block_nb",  "Conftrack")) %>%
  select(-Correct.y, - duration.y, -ILI.y, - condition.y) %>%
  filter(!is.na(response_text_entry)) %>%
  rename(duration = duration.x, 
         ILI = ILI.x, 
         Correct = Correct.x,
         condition = condition.x,
         response_arrow = Response,
         likert = response_rating_scale_likert)

#number of subjects
Nback_all %>%  
  group_by(PID) %>%
  summarise(n = n())

#number of blocks
blocks <- Nback %>% 
  group_by(block_nb) %>%
  summarise(n = n())
blocks

blockswithnoresps <- setdiff(first_trial$block_nb, blocks$block_nb)
# 1114 participants + 15510 blocks   (blocks with no responses (~0))
#participants who did not make an estimate have been removed


```






##translating subjective duration estimates and add them to Nback
```{r}
##formatting and translating subjective duration estimate




#getting rid of spaces, punctuation, "::" and words that beginning by m, d or λ (for minutes, dakika and λεπτό))     
subj_duration = Nback %>% filter(Zone.Type == "response_text_entry") %>% 
  select(PID, Response, Run, randomblock, nback) %>% 
  mutate(Response = str_to_lower(as.character(Response)),
          Response = str_replace_all(Response, "０", "0"),
          Response = str_replace_all(Response, "１", "1"),
          Response = str_replace_all(Response, "２", "2"),
          Response = str_replace_all(Response, "３", "3"),
          Response = str_replace_all(Response, "deytera", ""),
          Response = str_replace_all(Response, regex("m([a-z]{0,})"), ":"),
          Response = str_replace_all(Response, regex("d([a-z]{0,})"), ":"),
          Response = str_replace_all(Response, regex("λ([a-z]{0,})"), ":"),
          Response = str_replace_all(Response, regex("[:punct:]"), ":"),
          Response = str_replace_all(Response, regex("[:space:]"), ""),
          Response = str_replace_all(Response, "::", ":"))
#9163 estimations

subj_duration1 <- subj_duration %>% 
  mutate(translated = strtoi(
    as.difftime(Response, format = "00:%M:%S", units = "sec")))  #recognize duration with format (mm:ss)

subj_duration2 <- subj_duration1 %>% 
  filter(is.na(translated)) %>%   #among duration not yet translated
  mutate(translated = strtoi(
    as.difftime(Response, format = "%M:%S", units = "sec")))  #recognize duration with format (mm:ss)

subj_duration3 <- subj_duration2 %>% 
  filter(is.na(translated)) %>%   #among duration not yet translated
  mutate(translated = ifelse(
    str_detect(Response, regex("(\\d{1,2})s([a-z]{0,})")),     #if two digit only, recognize them as (ss)
     strtoi(as.difftime(Response, format = c("%S"), units = "sec")),
    NA)) 

subj_duration4 <- subj_duration3 %>% 
  filter(is.na(translated)) %>%   #among duration not yet translated
  mutate( translated = ifelse(
    str_detect(Response, regex("\\d{4}")),    #if series of 4 digits, recognize them as (mmss)
     strtoi(as.difftime(Response, format = c("%M%S"), units = "sec")),
    NA)) 

subj_duration5 = subj_duration4 %>% 
  filter(is.na(translated)) %>%  #among duration not yet translated
  mutate(translated = parse_number(Response)) #extract only the number from the string


#merge each dataframe with their translated values
subj_duration = full_join(subj_duration1, subj_duration2, copy = F) %>% filter(!is.na(translated))
subj_duration = full_join(subj_duration, subj_duration3, copy = F) %>% filter(!is.na(translated))
subj_duration = full_join(subj_duration, subj_duration4, copy = F) %>% filter(!is.na(translated))
subj_duration = full_join(subj_duration, subj_duration5, copy = F) %>% 
# subj_duration = full_join(subj_duration, subj_duration6, copy = F) %>%
  mutate(translated = ifelse(translated > 500, translated/60, translated),
         translated = ifelse(translated < 6, translated*60, translated))  

#get the duration estimation that ave strange formats and translate them manually 
no_translated = subj_duration  %>% 
  filter(is.na(translated))  
  # write_csv(file.path(outdir,'no_translated.csv'))     #60 no translated 

#merge subj_duration with Nback ==> add translated estimates
Nback_all <- left_join(Nback_all, subj_duration, by = c("PID", "Run", "nback", "randomblock")) %>%
  filter(!is.na(translated))   



paged_table(Nback_all)  #321,000

#Count overall number of trials (8 trials per Run per Participants ) #3850 --> 3785 (75 responses not translated)

Nback_blocks <- Nback_all %>%
  group_by(PID) %>%
  group_by(nback, .add = T) %>%
  group_by(Run, .add = T) %>%
  group_by(duration, ILI, .add = T) %>%
  summarise( translated = first(translated),
            block_nb = first(block_nb)) %>%
  ungroup()

paged_table(Nback_blocks)
#15208

 
```




#Age distribution

# Demographics
```{r}
library(lubridate)
library(eeptools)
library(ggridges)


demo <- gimmedata(DataDir = file.path(params$rootdir,'data'),UniqueName = 'Demographics',Session = '1') %>%
  mutate(PID = ifelse(is.na(PID), `Participant Private ID`, PID),          #In India, no PID
    country = `Experiment ID`,
         country = ifelse(country =="15684", "Greece", country),        
                          country = ifelse(country =="16144", "Turkey", country),
                          country = ifelse(country =="16612", "Japan", country),
                          country = ifelse(country =="16095", "Italy", country),
                          country = ifelse(`Task Name` == "01_Demographics_IN", "India", country),
                          country = ifelse(country == "16257", "Canada", country),
                          country = ifelse(country =="16271" | country == "16272", "Colombia", country),
                          country = ifelse(country == "15096" | country == "16303", "France", country),
     country = ifelse(country == "17423" |country == "19856" | country == "19880" | country == "19904"| country == "20044", "Argentina", country)) 

IDnback <- Nback %>%
  group_by(country, PID) %>%
  summarise()
IDnback   #1139 PID


DemoNbackS1 <- demo %>%
  filter(PID %in% IDnback$PID) %>%
  select(`Experiment ID`, `PID`, `Question Key`, `Response`, `UTC Date`, country) %>%
  mutate(`Question Key` = ifelse(`Question Key` == "Handedness-quantised", "handedness-quantised",`Question Key`),
         `Question Key` = ifelse(`Question Key` == "dob-year", "Age-year",`Question Key` ),
         `Question Key` = ifelse(`Question Key` == "dob-month", "Age-month", `Question Key`)) %>%
  filter(`Question Key` == "Age-year" | `Question Key` == "Age-month" |`Question Key` == "sex-quantised" | `Question Key` == "handedness-quantised" | `Question Key` == "dob") %>%
  mutate(`UTC Date` =  as.Date(str_extract(`UTC Date`, regex("(\\d{4}).(\\d{2}).(\\d{2})")))) %>%
  pivot_wider(values_from = Response, names_from = `Question Key`) %>%
        mutate(sex = ifelse(`sex-quantised` == "2" & country != "Argentina", "F", "M"),
               sex = ifelse(`sex-quantised` == "1" & country == "Argentina", "F", sex),
               handedness = ifelse(`handedness-quantised` == "2" & country != "Italy" & country != "Argentina", "right-handed", "left-handed"),
               handedness = ifelse(`handedness-quantised` == "1" & (country == "Italy" | country == "Argentina"), "right-handed", handedness),
               age = (as.numeric(as.character(`Age-year`)) + as.numeric(as.character(`Age-month`))/12),
      dob =  as.Date(parse_date_time(str_replace_all(dob, regex("[:punct:]"), "-"), orders = c("ymd", "dmy", "mdy")))) 

#Find age from date of birth (dob) and UTC Data for those with no "Age-month" and "Age-years" 
dob <- DemoNbackS1 %>%
  filter(!is.na(dob) & !is.na(`UTC Date`)) %>%     
  mutate( age = age_calc(dob, `UTC Date`, units = "years")) %>%
  select(PID, age, handedness, sex)
  

DemoNbackS1 <- DemoNbackS1 %>%
    select(country, PID, age, handedness, sex)

DemoNbackS1 <- left_join(DemoNbackS1, dob, by = c("PID", "sex", "handedness")) %>%
    mutate(age = ifelse(is.na(age.x), age.y, age.x)) %>%
    select(-age.y, -age.x)


#sex ratio
DemoNbackS1 %>%
  group_by(country, sex) %>%
  summarise(n = n()) 

#handedness ratio
DemoNbackS1 %>%
  group_by(country, handedness) %>%
  summarise(n = n()) 

#Age (year + month)
DemoNbackS1 %>%
  filter(!is.na(age)) %>%
  group_by(country) %>%
  summarise(mean = mean(age), sd = sd(age))

#Graph density ridge, age distribution for each country
# jpeg("DistribAgeS1.jpg", width = 4000, height = 2500, units = "px",res=600)
DemoNbackS1 %>%
   filter(age > 18) %>%
    filter(country != "Columbia") %>%
  
  ggplot( aes(y= country, x= age,  fill= country)) +
    geom_density_ridges(alpha=0.6, bins=50) +
    theme_ridges() +
    theme(legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)) +
  labs(y = "country", x = "Age", title ="Age distribution of S1 participants") +
  scale_y_discrete(labels = c("Turkey (146)", "Japan(104)", "Italy (150)", "India (40)", "Greece (125)", "France (362)", "Colombia (4)",  "Canada (33)", "Argentina(124)")) +
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 20, to = 80, by = 5))
# dev.off()

  nb_subjects <- DemoNbackS1 %>%
  group_by(PID) %>%
  summarise(country = first(country)) %>%
  group_by(country) %>%
  summarise(numbersubjects = n())
nb_subjects
  

Nback_all <- left_join(Nback_all, DemoNbackS1, by = c("PID", "country")) %>%
filter(country != "Columbia")


Nback_all <- Nback_all %>% select(PID, nback, Run, block_nb, ILI, duration, condition, likert, translated, Reaction.Time, response_arrow, ntarget, notarget, Correct, retro.pro, country, age, sex, handedness) %>%
write_csv(file.path("/home/user/Desktop/Documents/TimeSocialDistancing/nback_TSD",'S1global_nback.csv'))

```


