---
title: "Global_nback_analysis"
output: html_document
---



#DEF

##packages
```{r, include= F}
library(tidyverse)
library(rmarkdown)
library(ggpubr)
library(viridis)
library(cowplot)
library(lme4)
library(lmtest)
library(performance)
library(emmeans)
library(lsr)
library(R.utils)
library(RColorBrewer)

library(factoextra)
library(moments)
library(ordinal)
library(sure)
library(stargazer)
```

##Functions
```{r, include= F}
## Standard Error of the Mean (SEM)
sem <- function(x, na.rm=FALSE) {
     if(na.rm==TRUE) x <- na.omit(x)
     sd(x)/sqrt(length(x)) 
}  #Don't forget 10 ms bruit gorilla  

##coefficent of variation
cv <- function(x){sd(x)/mean(x)}

#Z-score
z_score <- function(x){(x - mean(x)) / sd(x)}

## Outliers removal
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}


#state mean symbols
cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1)
symbols = c("***", "***", "**", "*", "n.s.")
symnum <- list(cutpoints = cutpoints, symbols = symbols)
```

##Palettes
```{r, include= F}
#Palettes of colours
bluecontinuous = c("#42A5F5", "#0D47A1")

graycontinuous = c("#90A4AE", "#455A64")

cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")

cbPalette2 <- c("#0072B2", "#CC79A7")

cbPalette2_v2 <- c("#66c2a4", "#fc8d59")

cbPalette4 <- c( "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7")

cbPalette5 <- c( "#CC79A7", "#009E73")
```




#FORMATTING DATA AND OUTLIERS REMOVAL


##Merging dataset from S1 and SC
```{r}
#Session control Retrospective
file <- "/home/cyril/Documents/Cognition & Brain Dynamics/TimeSocialDistancing/nback_TSD/SCglobal_nback.csv"

SCNbackOG <- read.csv2(file, sep = ",") #138.530 obs

  
#Session 1 Retrospective

file <- "/home/cyril/Documents/Cognition & Brain Dynamics/TimeSocialDistancing/nback_TSD/S1global_nback.csv"

S1NbackOG = read.csv2(file, sep = ",") %>% #592.095 obs
mutate(translated = parse_number(translated))

#merge the two dataset



NbackOG <- bind_rows(S1NbackOG, SCNbackOG) #1184190



```





##Formatting dataset
```{r}

# Each row is a participant response
#Defining if the letter is a target letter and if an answer is a hit, a correct reject, a miss or a false alarm. 
Nback_all <- NbackOG %>%           #138530 obs
   filter(!is.na(translated)) %>%
         mutate(PID = as.factor(PID),
         estimate = as.numeric(as.character(translated)),
         relative_timing = estimate / parse_number(as.character(duration)),
         timing_error = estimate - parse_number(as.character(duration)),
         age = as.numeric(as.character(Age)))
        



# Each row is a different trial
Nback_blocksOG <- Nback_all %>%    #15839 trials
  group_by(Session, .add = T) %>%
  group_by(Country, .add = T) %>%
  group_by(PID, .add = T) %>%
  group_by(Run, .add = T) %>%
  group_by(nback, .add =T) %>%
  group_by(ILI, duration, block_nb, .add = T) %>%
  summarise(condition = first(condition),
            likert = first(likert),
            estimate = first(estimate),
            timing_error = first(timing_error),
            relative_timing = first(relative_timing),
            ntarget = first(ntarget),
            notarget = first(notarget),
            mRT = mean(as.numeric(as.character(Reaction_Time))),
            hit = sum(response_arrow == "Left" & Correct == T),
            miss  = sum(response_arrow == "Down" & Correct == F),
            fa = sum(response_arrow == "Left" & Correct == F),
            cr = sum(response_arrow == "Down" & Correct == T),
            HR = sum(response_arrow == "Left" & Correct == T)/ntarget,
            # HR1 = sum(response_arrow == "Left" & Correct == T)/(miss + hit),
            FA = sum(response_arrow == "Left" & Correct == F)/notarget,
            # FA1 = sum(response_arrow == "Left" & Correct == F)/(fa + cr),
            CR = sum(response_arrow == "Down" & Correct == T)/notarget,
            MR = sum(response_arrow == "Down" & Correct == F)/ntarget,
            handedness = first(Handedness),
            age = first(Age),
            sex = first(Sex),
            timestamp = first(timestamp)) %>%
  ungroup() 
 
#translate PoTJ Likert Scale from different countries in English
veryFast = c("muy rápido", "Très rapidement","Πολύ Γρήγορα","Very Fast","Molto veloce","Çok hızlı","とても速かった")
Fast = c("rápido", "Rapidement","Γρήγορα","Fast","Veloce","Hızlı","速かった")
Neutral = c("Normalement", "Κανονικά", "Neutral", "Neutrale", "普通", "Nötr", "normal")
Slow = c("lento","Lentement","Αργά","Slow","Very Slow","Lentamente","Yavaş", "遅かった") 
verySlow = c("Muy lento", "Très lentement","Πολύ Αργά","Molto lentamente","Çok yavaş","とても遅かった")

Nback_blocksOG <- Nback_blocksOG %>%
  mutate(likert = ifelse(likert %in% veryFast, "Very Fast", as.character(likert)),
         likert = ifelse(likert %in% Fast, "Fast", as.character(likert)),
         likert = ifelse(likert %in% Neutral, "Neutral", as.character(likert)),
         likert = ifelse(likert %in% Slow, "Slow", as.character(likert)),
         likert = ifelse(likert %in% verySlow, "Very Slow", as.character(likert))) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast"))

#dprime computation and dealing with score >= 1 or =< 0
Nback_blocksOG <- Nback_blocksOG %>%
  filter(HR < 1.2 & MR < 1.5) %>%
  mutate(HR = ifelse(HR > 1, 1, HR),
         FA = ifelse(FA > 1, 1, FA),
         CR = ifelse(CR > 1, 1, CR),
         HR = ifelse(HR == 0, 0.01, HR),
  HR = ifelse(HR == 1, 0.99, HR),
  FA = ifelse(FA == 0, 0.01, FA),
  FA = ifelse(FA == 1, 0.99, FA),
  zHR = qnorm(HR),
  zFA = qnorm(FA),
  dprime = zHR - zFA,
  beta = exp(-zHR*zHR/2+zFA*zFA/2),
  logbeta = log(beta))


Nback_blocksOG <- Nback_blocksOG %>%
  dplyr::select(-ntarget, -notarget, - hit, -miss, -fa, -cr, -zHR, -zFA)



paged_table(Nback_blocksOG) #19519 obs


```






#Separate
```{r}
Nback_blocksOG <- Nback_blocksOG %>%
  group_by(PID) %>%
  arrange(timestamp) %>%
  mutate(timestamp2 = as.character(timestamp)) %>%
  mutate(order = row_number()) 
  

S1retro_blocks <- Nback_blocksOG %>% #1100
  filter(order == 1 & Session == "S1") %>%
  mutate(paradigm = "retrospective")

SCretro_blocks <- Nback_blocksOG %>% #199
  filter(order == 1 & Session == "SC") %>%
  mutate(paradigm = "retrospective")

S1pro_blocks <- Nback_blocksOG %>% #14691
  filter(order != 1 & Session == "S1") %>%
  mutate(paradigm = "prospective")

SCpro_blocks <- Nback_blocksOG %>% #3529
  filter(order != 1 & Session == "SC") %>%
  mutate(paradigm = "prospective")
```

#Outliers S1 prospective trials
```{r}
#Outliers on d'

perf_outliers <- S1pro_blocks %>%
filter(dprime <= 0) #2487 outliers (750 out of ~7381 1-back tasks -> ~10%, 1737 out of ~7310 3-back -> ~24%)

S1pro_blocks <- S1pro_blocks %>%
filter(dprime > 0)     #14691 --> 12204 obs


#Outliers on TE

S1pro_blocks <- S1pro_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- S1pro_blocks %>%
filter(abs(ZTiming) > 2)    #363  outliers  (159 out of 5960 for 45s : 2.7%, 204 out 6244 of for 90s : 3.3%)

S1pro_blocks <-  S1pro_blocks %>%        #12204 -> 11841 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 
```


#Outliers S1 retrospective trials
```{r}
#Outliers on d'

perf_outliers <- S1retro_blocks %>%
filter(dprime <= 0) #227 outliers (72 1-back)

S1retro_blocks <- S1retro_blocks %>%
filter(dprime > 0)     #1100 --> 873 obs


#Outliers on TE

S1retro_blocks <- S1retro_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- S1retro_blocks %>%
filter(abs(ZTiming) > 2)    #28 outliers  (12 for 45s)

S1retro_blocks <-  S1retro_blocks %>%        #873 -> 845 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 

```


#Outliers SC retrospective trials
```{r}
perf_outliers <- SCretro_blocks %>%
filter(dprime <= 0) #42 outliers out of 199 obs ~ 21 % (11 outliers for 1-back trials)

SCretro_blocks <- SCretro_blocks %>%
filter(dprime > 0)     #199 --> 157 obs 



#Outliers on TE

SCretro_blocks <- SCretro_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- SCretro_blocks %>%
filter(abs(ZTiming) > 2)    #8  outliers --> 5.7% (4 for 45s)

SCretro_blocks <-  SCretro_blocks %>%        #157 -> 149 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 
```


#Outliers SC prospective trials
```{r}
perf_outliers <- SCpro_blocks %>%
filter(dprime <= 0) #598 outliers (out of ~3529 obs ~ 17 %)

SCpro_blocks <- SCpro_blocks %>%
filter(dprime > 0)     #3529 --> 2931 obs (we removed ~17.6% of the tasks)


#Outliers on TE

SCpro_blocks <- SCpro_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- SCpro_blocks %>%
filter(abs(ZTiming) > 2)    #89  outliers --> 3% (39 for 45s)

SCpro_blocks <-  SCpro_blocks %>%        #2931 -> 2842 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 
```


```{r}
Nback_blocks <- bind_rows(SCpro_blocks, SCretro_blocks, S1pro_blocks, S1retro_blocks) #15677
```

```{r}
Nback_blocks %>%  filter(!is.na(dprime))
```



# N-BACK PERFORMANCE 2 (D', Bias, mRT)


##Mixed-effect  models on d', bias and mRT
```{r}
data <- Nback_blocks #15677

## Model for d'



Md1 <-lmer(dprime ~ nback + (1|PID), data=data,  REML=FALSE)

Md2 <-lmer(dprime ~ nback + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md1, Md2)  #p < 0.05*** -> More complex model (Md2) significantly better than Md1

Md3 <-lmer(dprime ~ nback + duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md2, Md3)  #p < 0.05***

Md4 <-lmer(dprime ~ nback * duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md3, Md4)  #p =~ 0.90

Md5 <-lmer(dprime ~ nback + duration * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md3, Md5) #p =~ 0.90

Md6 <-lmer(dprime ~ duration + nback * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md3, Md6) #p =~ 0.90

Md7 <-lmer(dprime ~ duration + nback + ILI + Session + (1|PID), data=data,  REML=FALSE)
lrtest(Md3, Md7) #p =~ 0.90

Md8 <-lmer(dprime ~ duration + nback + ILI + paradigm + (1|PID), data=data,  REML=FALSE)
lrtest(Md3, Md8)  #p < 0.05***

Md9 <-lmer(dprime ~ nback + ILI + paradigm * duration + (1|PID), data=data,  REML=FALSE)
lrtest(Md8, Md9)  #p < 0.05***   other interactions between paradigm and design conditions (Nback and ILI) were not significant

Md10 <-lmer(dprime ~ nback + ILI + duration * paradigm + (nback|PID), data=data,  REML=FALSE)
lrtest(Md9, Md10) #p < 0.05*** 

Md11 <-lmer(dprime ~ nback + ILI + duration * paradigm + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(Md10, Md11) #p < 0.05***  but fit is singular (and duration as a random effect explain very poorly the variance)

Md12 <-lmer(dprime ~ nback + ILI + duration * paradigm + (nback + ILI|PID), data=data,  REML=FALSE)
lrtest(Md10, Md12) #p > 0.05  + the fit is singular

Md13 <-lmer(dprime ~ nback + ILI + duration * paradigm + (nback + paradigm|PID), data=data,  REML=FALSE)
lrtest(Md10, Md13) #p < 0.05*** 


lrtest(Md1, Md2)
lrtest(Md2, Md3)
lrtest(Md3, Md8)
lrtest(Md8, Md9)
lrtest(Md9, Md10)
lrtest(Md10, Md13)

compare_performance(Md1, Md2, Md3, Md4, Md5, Md6, Md7, Md8, Md9, Md10, Md11, Md12, Md13) #Md13 best AIC

summary(Md1)
summary(Md2)
summary(Md3) 
summary(Md4)
summary(Md5)
summary(Md6)
summary(Md7)
summary(Md8)
summary(Md9)
summary(Md10)
summary(Md11)
summary(Md12)
summary(Md13) #best model, show significant effect of design conditions and of the paradigm used (main effect + interaction with duration) + WM Load and Paradigm as random effects


Md13 <-lmer(dprime ~ nback + ILI + duration * paradigm + (nback + paradigm|PID), data=data,  REML= T)

summary(Md13)
confint(Md13, oldNames=FALSE)
stargazer(Md13, type = "text",
           title = "Regression results Md3",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")



emmeans(Md13, ~paradigm,  lmer.df = "satterthwaite")
emmeans(Md13, ~ nback,  lmer.df = "satterthwaite")
emmeans(Md13, ~ ILI,  lmer.df = "satterthwaite")
emmeans(Md13, ~ duration,  lmer.df = "satterthwaite")#Does Md13 meet assumptions ?
emmeans(Md13, pairwise ~ duration + paradigm,  lmer.df = "satterthwaite")


#autocorrelation
check_autocorrelation(Md13)
# durbinWatsonTest(resid(Md13)) # = 2 no autocorrelation

check_heteroscedasticity(Md13) #not OK, but graphically OK
check_collinearity(Md13) #OK


lm <- lm(dprime ~ duration + ILI + nback, data = data)
plot(lm)
plot(Md13)





## residuals distribution : histogramme and shapiro test for normality
hist(resid(Md13), breaks = 30)
qqnorm(residuals(Md13))


## homogeneity : fitted values vs normalized residuals

plot(x = data$dprime, 
     y = resid(Md13), 
     xlab = "d'",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

## independance : residuals vs each model covariable

boxplot(resid(Md13) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(Md13) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(Md13) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)




#heteroscedascity between random effects
plot(Md13, as.factor(PID) ~ resid(., scaled=TRUE),abline=0,pch=16,xlab="Standardised residuals",ylab="Regions")


# require("lattice")
#It is also important to check that the random effect distribution(s) match the assumed (most often Gaussian) dsitrbibution
# lattice::dotplot(ranef(Md7, condVar=TRUE))

```


##d' violin plot
```{r}
GlobalViolindNback <- Nback_blocks %>%
  ggplot(aes(nback, dprime, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "d'", x = "WM Load") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 11),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  scale_colour_manual( values = bluecontinuous) +
  scale_x_discrete(labels = c("1-back", "3-back")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",  tip.length = 0, comparisons = list(c("1back","3back")))


GlobalViolindDuration <- Nback_blocks %>%
  ggplot(aes(duration, dprime)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "d'", x = "Duration (s)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
  scale_x_discrete(labels = c("45", "90")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("45s","90s")))

GlobalViolindILI <- Nback_blocks %>%
  ggplot(aes(ILI, dprime)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "d'", x = "ILI (ms)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
  scale_x_discrete(labels = c("1500", "1800")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("1500ms","1800ms")))



# jpeg("GlobalViolindNback.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolindNback
# dev.off()
  
# jpeg("GlobalViolindILI.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolindILI
# dev.off()

# jpeg("GlobalViolindDuration.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolindDuration
# dev.off()


# #Merge the three graphs
# jpeg("Violind'd'ViolinGlobal.jpg", width = 3500, height = 2500, units = "px",res=600)
right_row <- plot_grid(GlobalViolindDuration + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       GlobalViolindILI + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       labels = c('b', 'c'), align = 'h', ncol = 1)
PanelViolind <- plot_grid(GlobalViolindNback, right_row, labels = c('a', ''), nrow = 1)
PanelViolind
# dev.off()

```



##Models for Bias (log(Beta))
```{r}


MB1 <-lmer(logbeta ~ duration + (1|PID), data=data,  REML=FALSE)

MB2 <-lmer(logbeta ~ duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MB1, MB2)  #p < 0.05** -> More complex model (MB2) significantly better than MB1

MB3 <-lmer(logbeta ~ duration + ILI + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB2, MB3) #p < 0.05*** -> More complex model (MB3) significantly better than MB2

MB4 <-lmer(logbeta ~ ILI + duration * nback + (1|PID), data=data,  REML=FALSE)
lrtest(MB3, MB4)  #p < 0.05*** -> More complex model (MB4) significantly better than MB3

MB5 <-lmer(logbeta ~ ILI * duration + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB5)  #p < 0.05*** -> More complex model (MB5) significantly better than MB4 but MB4 has a better AIC

MB6 <-lmer(logbeta ~ ILI * nback + duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB6) #p < 0.05*** -> More complex model (MB6) significantly better than MB4 but MB4 has a better AIC

MB7 <-lmer(logbeta ~ ILI * nback * duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB7) #p < 0.05*** -> More complex model (MB7) significantly better than MB4  but MODERATE COLLINEARITY

MB8 <-lmer(logbeta ~ ILI * nback * duration + Session + (1|PID), data=data,  REML=FALSE)
lrtest(MB7, MB8) #p = 0.05 . -> More complex model (MB8) not significantly better than MB7  and MODERATE COLLINEARITY but we choose to keep Session

MB9 <-lmer(logbeta ~ ILI * nback * duration + Session + paradigm + (1|PID), data=data,  REML=FALSE)
lrtest(MB8, MB9) #p < 0.05*** -> More complex model (MB9) significantly better than MB8 

MB10 <-lmer(logbeta ~ ILI * nback * duration + paradigm + Session:duration + (1|PID), data=data,  REML=FALSE)
lrtest(MB9, MB10) #p < 0.05**  other interactions with Session not significant

MB11 <-lmer(logbeta ~ ILI * nback * duration + paradigm  + Session + Session:duration + paradigm:duration +  paradigm:ILI + paradigm:nback + (1|PID), data=data,  REML=FALSE)
lrtest(MB10, MB11) #p < 0.05*** -> More complex model (MB10) not significantly better than MB8 AND SINGULAR


MB12 <-lmer(logbeta ~ ILI * nback * duration + paradigm + Session + Session:duration + paradigm:duration +  paradigm:ILI + paradigm:nback + (nback|PID), data=data,  REML=FALSE)
lrtest(MB11, MB12) #p < 0.05*** 

MB13 <-lmer(logbeta ~ ILI * nback * duration + paradigm + Session + Session:duration + paradigm:duration +  paradigm:ILI + paradigm:nback + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(MB12, MB13) #p < 0.05***  but fit is singular (ILI and Session as random model were not significant, Paradigm was significant but the fit was singular)

lrtest(MB1, MB2)
lrtest(MB2, MB3)
lrtest(MB3, MB4)
lrtest(MB4, MB7)
lrtest(MB7, MB8)
lrtest(MB8, MB9)
lrtest(MB9, MB11)
lrtest(MB11, MB12)


compare_performance(MB1, MB2, MB3, MB4, MB5, MB6, MB7, MB8, MB9, MB10, MB11, MB12, MB13) #MB13 (and then MB12)-> best AIC but singular


summary(MB3)
summary(MB4)  
summary(MB5)
summary(MB6)
summary(MB7)
summary(MB8) 
summary(MB9)
summary(MB10)
summary(MB11)
summary(MB12) #best model MB12 --> shows significative main effects of ILI, duration, nback, Session and Paradigmn on Bias + interactions between task duration and session
summary(MB13) 


MB12 <-lmer(logbeta ~ ILI * nback * duration + paradigm + Session + Session:duration + paradigm:duration +  paradigm:ILI + paradigm:nback + (nback|PID), data=data,  REML= T)

summary(MB12)

confint(MB12, oldNames=FALSE)
stargazer(MB12, type = "text",
           title = "Regression results MB12",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

emmeans(MB12, ~nback,  lmer.df = "satterthwaite")
emmeans(MB12, ~duration,  lmer.df = "satterthwaite")
emmeans(MB12, ~ILI,  lmer.df = "satterthwaite")
emmeans(MB12, ~paradigm,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ILI + nback,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ duration + nback,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ILI + duration,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ILI + paradigm,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ duration + paradigm,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ nback + paradigm,  lmer.df = "satterthwaite")
emmeans(MB12, pairwise ~ Session + duration,  lmer.df = "satterthwaite")

#Does MB12 meet assumptions ?

check_autocorrelation(MB12)
durbinWatsonTest(resid(MB12)) # = 2 no autocorrelation


check_heteroscedasticity(MB12) #not OK, but graphically OK
check_collinearity(MB12) #OK, low/moderate correlation

plot(MB12)
qqnorm(residuals(MB12))

## residuals distribution : histogramme and shapiro test for normality
hist(resid(MB12), breaks = 30)

## homogeneity : fitted values vs normalized residuals
plot(x = data$logbeta, 
     y = resid(MB12), 
     xlab = "Bias",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

## independance : residuals vs each model covariable

boxplot(resid(MB12) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(MB12) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(MB12) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)
```



##Bias violin plot
```{r}


GlobalViolinBiasNback <- Nback_blocks %>%
  ggplot(aes(nback, logbeta, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
       geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 11),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  scale_colour_manual(values = bluecontinuous) +
  scale_x_discrete(labels = c("1-back", "3-back")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",  tip.length = 0, comparisons = list(c("1back","3back")))


GlobalViolinBiasDuration <- Nback_blocks %>%
  ggplot(aes(duration, logbeta)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
     geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "Bias", x = "Duration (s)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
  scale_x_discrete(labels = c("45", "90")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",  tip.length = 0, comparisons = list(c("45s","90s")))

GlobalViolinBiasILI <- Nback_blocks %>%
  ggplot(aes(ILI, logbeta)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "Bias", x = "ILI (ms)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
    scale_x_discrete(labels = c("1500", "1800")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",  tip.length = 0, comparisons = list(c("1500ms","1800ms")))


# jpeg("GlobalViolinBiasNback.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinBiasNback
# dev.off()
  
# jpeg("GlobalViolinBiasILI.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinBiasILI
# dev.off()

# jpeg("GlobalViolinBiasDuration.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinBiasDuration
# dev.off()

# jpeg("Violind'BiasViolinGlobal.jpg", width = 3500, height = 2500, units = "px",res=600)
right_row <- plot_grid(GlobalViolinBiasDuration + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       GlobalViolinBiasILI + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       labels = c('e', 'f'), align = 'h', ncol = 1, rel_heights = c(0.8, 0.8))
PanelViolinBias <- plot_grid(GlobalViolinBiasNback, right_row, labels = c('d', ''), nrow = 1)
PanelViolinBias
# dev.off()

#   
# #INTERATIONS  
#   violinBiasdurationSession <- Nback_blocks %>% 
#     mutate(sessionduration = paste(Session, duration),
#            sessionduration =  fct_relevel(sessionduration, "SC 45s", "S1 45s", "SC 90s", "S1 90s")) %>%
#   ggplot(aes(sessionduration, logbeta, colour = sessionduration)) +
#   geom_violin(outlier.shape=NA) +
#   geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
#   geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
# stat_summary(fun = mean)  +
#       # facet_grid(ILI~.) +
#   theme_classic() +
#   labs(y = "Bias", x = "Session : Task Duration", title = "Bias for different Session and Task Duration") +
#   theme( legend.position="none",
#         axis.title.x = element_text(size = 12),
#          axis.title.y = element_text(size = 12),
#         axis.text = element_text(size = 12),
#   plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
#   scale_colour_manual(values = cbPalette4) +
#    stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("SC 45s","S1 45s"), c("SC 90s","S1 90s"))) 

```





## Models for mRT
```{r}
data <- Nback_blocks #15677


MRT1 <-lmer(mRT ~ duration + (1|PID), data=data,  REML=FALSE)

MRT2 <- lmer(mRT ~ duration + ILI +(1|PID), data=data,  REML=FALSE)
lrtest(MRT1, MRT2) #p < 0.05*** -> More complex model (MRT2) significantly better than MRT1

MRT3 <- lmer(mRT ~ duration + ILI + nback + (1|PID), data=data,  REML=FALSE)
lrtest(MRT2, MRT3) #p < 0.05*** -> More complex model (MRT3) significantly better than MRT2

MRT4 <- lmer(mRT ~ duration + nback * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT3, MRT4) #p < 0.05** -> More complex model (MRT4) significantly better than MRT3

MRT5 <- lmer(mRT ~ nback * duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT3, MRT5) #p < 0.05***  but duration x ILI  not significatnt

MRT6 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + (1|PID), data=data,  REML=FALSE)
lrtest(MRT4, MRT6) #p < 0.05*** -> More complex model (MRT6) is significantly better than MRT4 and has a better AIC

MRT7 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + (1|PID), data=data,  REML=FALSE)
lrtest(MRT6, MRT7) #p < 0.05*** -> More complex model (MRT7) significantly better than MRT6 and has a better AIC

MRT8 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + (1|PID), data=data,  REML=FALSE)
lrtest(MRT8, MRT7) #p < 0.05*** -> More complex model (MRT8) significantly better than MRT7 

MRT9 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + (1|PID), data=data,  REML=FALSE)
lrtest(MRT9, MRT8) #p < 0.05*** ->  but no interactions between Session and other factors

MRT10 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + paradigm:ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT10, MRT9) #p < 0.05*** ->  but no interactions between paradigm and duration

MRT11 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + paradigm:ILI + (nback|PID), data=data,  REML=FALSE)
lrtest(MRT11, MRT10) #p < 0.05*** ->  but no interactions between paradigm and duration

MRT12 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + paradigm:ILI + (nback + paradigm|PID), data=data,  REML=FALSE)
lrtest(MRT12, MRT11) #p < 0.05*** -> better model with paradigm as a random effect, but not for Session, ILI and nback, p > 0.05 and fit is singular

MRT13 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + paradigm:ILI + (nback * paradigm|PID), data=data,  REML=FALSE)
lrtest(MRT13, MRT12) #p < 0.05***

compare_performance(MRT1, MRT2, MRT3, MRT4, MRT5, MRT6, MRT7, MRT8, MRT9, MRT10, MRT11, MRT12, MRT13) 

AIC(MRT1, MRT2, MRT3, MRT6, MRT7, MRT8, MRT9, MRT10, MRT11, MRT13)

summary(MRT1)
summary(MRT2) 
summary(MRT4)
summary(MRT5)
summary(MRT6)
summary(MRT7)
summary(MRT8)
summary(MRT9)
summary(MRT10)
summary(MRT11)
summary(MRT12)
summary(MRT13)


lrtest(MRT1, MRT2)
lrtest(MRT2, MRT3)
lrtest(MRT3, MRT6)
lrtest(MRT6, MRT7)
lrtest(MRT7, MRT8)
lrtest(MRT8, MRT9)
lrtest(MRT9, MRT10)
lrtest(MRT10, MRT11)
lrtest(MRT11, MRT13)


MRT13 <- lmer(mRT ~ duration + nback + ILI + duration:nback + ILI:nback + Session + paradigm + paradigm:nback + paradigm:ILI + (nback * paradigm|PID), data=data,  REML=T)
summary(MRT13)
stargazer(MRT13, type = "text",
           title = "Regression results Md7",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
confint(MRT13, oldNames=FALSE)

emmeans(MRT13, ~nback,  lmer.df = "satterthwaite")
emmeans(MRT13, ~duration,  lmer.df = "satterthwaite")
emmeans(MRT13, ~ILI,  lmer.df = "satterthwaite")
emmeans(MRT13, ~Session,  lmer.df = "satterthwaite")
emmeans(MRT13, ~paradigm,  lmer.df = "satterthwaite")
emmeans(MRT13, pairwise ~nback * duration,  lmer.df = "satterthwaite")
emmeans(MRT13, pairwise ~nback * ILI,  lmer.df = "satterthwaite")
emmeans(MRT13, pairwise ~nback * paradigm,  lmer.df = "satterthwaite")
emmeans(MRT13, pairwise ~paradigm * ILI,  lmer.df = "satterthwaite")

 AIC(MRT13)

#Does MRT13 meet assumptions ?

check_heteroscedasticity(MRT13) #not OK, but graphically OK
check_collinearity(MRT13) #OK


check_autocorrelation(MRT13)
durbinWatsonTest(resid(MRT13)) # =~ 2 no autocorrelation


## residuals distribution : histogramme 
hist(resid(MRT13), breaks = 50)


## homogeneity : fitted values vs normalized residuals


plot(x = data$mRT, 
     y = resid(MRT13), 
     xlab = "mRT",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

plot(MRT13)

## independance : residuals vs each model covariable

boxplot(resid(MRT13) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(MRT13) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(MRT13) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)
```


##mRT violin plot
```{r}

GlobalViolinRTNback <- Nback_blocks %>%
  ggplot(aes(nback, mRT, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "RT (ms)", x = "WM Load") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 11),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  scale_colour_manual(values = bluecontinuous) +
  scale_x_discrete(labels = c("1-back", "3-back")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("1back","3back")))


GlobalViolinRTDuration <- Nback_blocks %>%
  ggplot(aes(duration, mRT)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "RT (ms)", x = "Duration (s)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
  scale_x_discrete(labels = c("45", "90")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("45s","90s")))

GlobalViolinRTILI <- Nback_blocks %>%
  ggplot(aes(ILI, mRT)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean, size = 0.3)  +
  theme_classic() +
  labs(y = "RT (ms)", x = "ILI (ms)") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 11),
         axis.title.y = element_text(size = 11),
        axis.text = element_text(size = 10),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +
  # scale_colour_manual(values = graycontinuous) +
    scale_x_discrete(labels = c("1500", "1800")) +
   stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("1500ms","1800ms")))


  
# jpeg("GlobalViolinRTNback.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinRTNback
# dev.off()
  
# jpeg("GlobalViolinRTILI.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinRTILI
# dev.off()

# jpeg("GlobalViolinRTDuration.jpg", width = 2500, height = 2500, units = "px",res=600)
GlobalViolinRTDuration
# dev.off()

# jpeg("ViolinmRTViolinGlobal.jpg", width = 3500, height = 2500, units = "px",res=600)
right_row <- plot_grid(GlobalViolinRTDuration + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       GlobalViolinRTILI + scale_y_continuous(expand = expansion(mult = c(0, 0.1))),
                       labels = c('h', 'i'), align = 'h', ncol = 1, rel_heights = c(1, 1))
right_row
PanelViolinRT <- plot_grid(GlobalViolinRTNback, right_row , labels = c('g', ''), nrow = 1)
PanelViolinRT
# dev.off()

# jpeg("GlobalViolinPanel.jpg", width = 8000, height = 2500, units = "px",res=600)
plot_grid(PanelViolind, PanelViolinBias, PanelViolinRT, ncol = 3, align = 'h')
# dev.off()


# svg("GlobalViolinPanel.svg", width = 16, height = 6)
plot_grid(PanelViolind, PanelViolinBias, PanelViolinRT, ncol = 3, align = 'h')
# dev.off()

```








# RELATIVE DURATION ESTIMATION MODELS


#simplified global model
```{r}
data <- Nback_blocks  #15677

Ms1 <-lmer(relative_timing ~ paradigm + (1|PID), data=data, REML=FALSE)

anova(Ms1)
Ms2 <-lmer(relative_timing ~ paradigm + nback + (1|PID), data=data, REML=FALSE)
lrtest(Ms1, Ms2) #M1 nested #M2 more complex   p <0.05***  #the complex model is significantly more accurate

Ms3 <-lmer(relative_timing ~ paradigm * nback  + (1|PID), data=data, REML=FALSE)
lrtest(Ms2, Ms3) #M2 nested #M3 more complex  p > 0.05  #the complex model is not significantly more accurate

Ms4 <-lmer(relative_timing ~ paradigm + nback  + (paradigm|PID), data=data, REML=FALSE)
lrtest(Ms2, Ms4) # p <0.05*** but paradigm as a random effect explains a very slight portion of the variability

Ms5 <-lmer(relative_timing ~ paradigm * nback  + (nback |PID), data=data, REML=FALSE)
lrtest(Ms2, Ms5) # p <0.05*** but WM Load  as a random effect explains a very slight portion of the variability

compare_performance(Ms1, Ms2, Ms3, Ms4, Ms5) #Ms5 best AIC

lrtest(Ms1, Ms2, Ms3, Ms4, Ms5)

summary(Ms1)
summary(Ms2)
summary(Ms3)
summary(Ms4)
summary(Ms5)

library("stargazer")

Ms3 <-lmer(relative_timing ~ paradigm * nback + (1|PID), data=data, REML=T)

summary(Ms3)
stargazer(Ms3, type = "text",
           title = "Regression results Ms3",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
confint(Ms3, oldNames=FALSE)



# -- Main effect of duration --   => Significant effect
emmeans(Ms3, ~ paradigm) 

# -- Main effect of WM Load --    => no Significant effect
emmeans(Ms3, ~ nback,  lmer.df = "satterthwaite") 

emmeans(Ms3, pairwise ~ nback |paradigm,  lmer.df = "satterthwaite")  

```






## Mixed-effect models rDE
```{r}
data <- Nback_blocks  #15677

M1 <-lmer(relative_timing ~ duration + (1|PID), data=data, REML=FALSE)

anova(M1)
M2 <-lmer(relative_timing ~ duration + nback + (1|PID), data=data, REML=FALSE)
lrtest(M1, M2) #M1 nested #M2 more complex   p <0.05***  #the complex model is significantly more accurate

M3 <-lmer(relative_timing ~ duration + nback + ILI + (1|PID), data=data, REML=FALSE)
lrtest(M2, M3) #M2 nested #M3 more complex  p > 0.05  #the complex model is not significantly more accurate

M4 <-lmer(relative_timing ~ duration + nback + ILI:nback + (1|PID), data=data, REML=FALSE)
lrtest(M2, M4)   #M2 nested #M4 more complex      p <0.05*  #the complex model is significantly more accurate (no interaction between ILI and other factors were found)

M5 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + (1|PID), data=data, REML=FALSE)
lrtest(M4, M5)  #M4 nested #5 more complex    p < 0.05***  #the complex model is significantly more accurate    

M6 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + (1|PID), data=data, REML=FALSE)
lrtest(M5, M6)   #M5 nested #6 more complex   p < 0.05*  #the complex model is  not significantly more accurate

M7 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + (1|PID), data=data, REML=FALSE)
lrtest(M6, M7)   #M6 nested #7 more complex   p < 0.05*** #the complex model is significantly more accurate

M8 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm + (1|PID), data=data, REML=FALSE)
lrtest(M7, M8)   #M7 nested #8 more complex   p > 0.05  #the complex model is not significantly more accurate


M9 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + (1|PID), data=data, REML=FALSE)
lrtest(M7, M9)   #M4 nested #7 more complex    p < 0.05*** #the complex model is significantly more accurate, supplementary interactions between paradigm and other factors were not found

M10 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:logbeta + (1|PID), data=data, REML=FALSE)
lrtest(M9, M10)   #MÇ nested #10 more complex   p < 0.05**, no other interaction between logbeta and other factors

M11 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:logbeta + dprime:duration+ (1|PID), data=data, REML=FALSE)
lrtest(M10, M11)   # p < 0.05*   but no interaction found between WM Load and duration

M12 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:duration + dprime:logbeta + dprime:nback +(1|PID), data=data, REML=FALSE)
lrtest(M11, M12)   # p < 0.05** no interaction between dprime and Paradigm, session or ILI



#Testing multicollinearity (without the interaction terms that could inflate the variance inflation factor (the VIF)

M12b <- lmer(relative_timing ~ duration + nback + ILI + dprime + logbeta + Session +(1|PID), data=data, REML=FALSE)
check_collinearity(M12b) #OK, low correlation



#Testing random effects

M13 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:duration + dprime:logbeta + dprime:nback + (nback|PID), data=data, REML=FALSE)
lrtest(M12, M13)   # p < 0.05***

M14 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:duration + dprime:logbeta + dprime:nback + 
             (nback + paradigm|PID), data=data, REML=FALSE)
lrtest(M13, M14)   # p < 0.05***    ILI, Session and dprime were not significant and the fit was singular

#add ILI, duration, d' or logbeta as a random effect slope yields in "boundary singular error" or the model failed to converge
#Moreover, it explained only a very small part of the variance


compare_performance(M1, M2, M3, M4, M5, M6, M7, M8, M9, M10, M11, M12, M13, M14) #M14 best AIC

lrtest(M1, M2, M4, M5, M6, M7, M9, M10, M11, M12, M13, M14)



summary(M1)
summary(M2)
summary(M3)
summary(M4)
summary(M5)
summary(M6)
summary(M7)
summary(M8)
summary(M9) 
summary(M10)
summary(M11)
summary(M12)
summary(M13) 
summary(M14) #Best !
```


#Main effects
```{r}
library("stargazer")

M14 <-lmer(relative_timing ~ duration + nback + ILI:nback + dprime + logbeta + Session + paradigm:duration + dprime:duration + dprime:logbeta + dprime:nback + 
             (nback + paradigm|PID), data=data, REML=T)

summary(M14)
stargazer(M14, type = "text",
           title = "Regression results M14",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
# confint(M14, oldNames=FALSE)



# -- Main effect of Session --   => Significant effect
emmeans(M14, ~ Session, lmer.df = "satterthwaite") 

# -- Interaction effect of duration x Paradigm --   => Significant effect

emmeans(M14, pairwise ~ paradigm | duration,  lmer.df = "satterthwaite")  

# -- Main effect of duration --   => Significant effect
emmeans(M14, ~ duration) 

# -- Main effect of WM Load --    => no Significant effect
emmeans(M14, ~ nback,  lmer.df = "satterthwaite") 

# -- Main effect of dprime --    => no Significant effect
emmeans(M14, ~ dprime,at = list(dprime = c(1, 2, 3, 4,5)))

# -- Main effect of Interaction duration / nback 

emmeans(M14, pairwise ~ duration | dprime,  at = list(dprime = c(0.01, 1, 2, 3, 4,5)), lmer.df = "satterthwaite")

emmeans(M14, pairwise ~ nback | ILI,  lmer.df = "satterthwaite")  

emmeans(M14, pairwise ~ dprime | nback, at = list(dprime = c(0, 1, 2, 3, 4,5)))
```


# Verification of model assumptions ####
```{r}

R1 <- resid(M14)
F1 <- fitted(M14)

## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)

# shapiro.test(R1)

## homogeneity : fitted values vs normalized residuals

plot(x = F1, 
     y = R1, 
     xlab = "Fitted Values",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

#timing_error
plot(x = data$relative_timing, 
     y = R1, 
     xlab = "relative_timing",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)


## independance : residuals vs each model covariable

# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

# nback
boxplot(R1 ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)



# data %>%
#  ggplot(aes(timing_error, R1, colour = dprime)) + 
#            geom_point() +
#       # geom_density(aes(y = ..density..*(500 * 0.02)), alpha=.4, fill="lightgreen") +
#   labs(y = "residuals", x = "timing_error", title ="model for 1-back retrospective tasks, residuals vs TE") + 
#   theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
#   # scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
#   #                limits = c(-0.01,1.01))



check_heteroscedasticity(M14) #not OK, but graphically OK:
plot(M14)

check_autocorrelation(M14)
durbinWatsonTest(resid(M14)) # =~ 2 (1.6) no autocorrelation


```









##D' effect on Relative Duration Estimation - Visualization
```{r}


# jpeg("d'WMLoadGlobal.jpg", width = 3500, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime, relative_timing), color = nback) +
  geom_point(size = 0.005, alpha = 0.7) +
  geom_smooth(method="lm", fill="#69b3a2", se= T, size = 0.6) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .6, linetype = "dashed") +
  theme_classic() +
   facet_grid(.~nback,  labeller = labeller(nback = c(`1back` = "1-back", `3back` = "3-back"))) +
   # scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
   #                   limits = c(0, 2.7)) +
   labs(y = "rDE", x = "d'") +
  theme(axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 11)) +
 scale_colour_manual(values = bluecontinuous)
# dev.off()
 
#with mixed-effect model regression

emm_options(lmerTest.limit = 17000)
emm_options(pbkrtest.limit = 17000)


ref_grid(M14)
# predict_gam(M14, l)

predictions <- summary(emmeans(M14, ~ dprime, at = list(dprime = seq(0,5, by = 0.01), rg.limit = 20000)))
                                 
                                 nuisance = c("Session", "ILI", "logbeta", "nback")))

Nback_blocks %>%
  ggplot(aes(dprime, relative_timing)) +
  geom_point(size = 0.005, alpha = 0.3) +
  geom_point(predictions, size = 0.005, alpha = 0.7) +
  geom_smooth(method="lm", fill="#69b3a2", se= T, size = 0.6) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .6, linetype = "dashed") +
  theme_classic() +
   # scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
   #                   limits = c(0, 2.7)) +
   labs(y = "rDE", x = "d'") +
  theme(axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 11)) +
 scale_colour_manual(values = bluecontinuous)



# Nback_blocks %>%
#   ggplot(aes(dprime, relative_timing), color = nback) +
#   geom_point(size = 0.005, alpha = 0.3) +
#   # geom_point(predictions, size = 0.005, alpha = 0.7) +
#   geom_smooth(method="lm", fill="#69b3a2", se= T, size = 0.6) +
#   geom_hline(aes(yintercept = 1), colour = 'black', size = .6, linetype = "dashed") +
#   theme_classic() +
#    facet_grid(.~nback,  labeller = labeller(nback = c(`1back` = "1-back", `3back` = "3-back"))) +
#    # scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
#    #                   limits = c(0, 2.7)) +
#    labs(y = "rDE", x = "d'") +
#   theme(axis.title.x = element_text(size = 12),
#          axis.title.y = element_text(size = 12),
#           axis.text = element_text(size = 11)) +
#  scale_colour_manual(values = bluecontinuous) 

install.packages('sjPlot')
library("sjPlot")
install.packages('glmmTMB')
library("glmmTMB")
plot_model(M14, type="re")

plot_model(M14, grid=T, sort.est="sort.all", y.offset=1.0)
plot_model(M14, grid=T, type="diag")
# plot_model(M14, type="eff")
plot_model(M14, show.values = TRUE, value.offset = .3)
plot_model(M14, type="re") 
plot_model(M14, type="std")  
plot_model(M14, type="slope") 
plot_model(M14, type="resid")

plot_model(model.q.t.r, type="pred", grid=T, terms=c("time [all]", "treatm"))
plot_model(model.q.t.r, type="pred", pred.type = "re", grid=T, terms=c("time [all]", "treatm"))
plot_model(model.q.t.r, type="pred", show.data = TRUE, pred.type = "fe", grid=T, terms=c("time [all]", "treatm"))
tab_model(model.q.t.r, 
          show.std=T, 
          show.r2=T, 
          show.aic=T, 
          show.aicc = T, 
          show.dev=T, 
          show.re.var=T)

predictions <- emmeans(M14, ~ dprime, at = list(dprime = c(0, 1, 2, 3, 4,5)))
summary(M14)

predictions <- summary(emmeans(M14, ~ dprime, at = list(dprime = seq(0,5, by = 0.01))))



?ref_grid

'rg.limit = <new limit>'

# #Bias
# 


predictions <- summary(emmeans(M13, ~ logbeta, at = list(dprime = seq(-2,2, by = 0.01))))
# 
# # jpeg("predictionBiasproS1.jpg", width = 2500, height = 2500, units = "px",res=600)
ggplot(data, aes(logbeta, relative_timing)) +
geom_point(size = 0.1) +
    geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  theme_classic() +
     scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
geom_point(predictions, colour ="blue", mapping = aes(y= emmean), size = 0.8) +
  labs(y = "rDE", x = "Bias")
# # dev.off()
```

#barplot rDE x D'
```{r}

rDExSD <- Nback_blocks %>% 
  # mutate(dprime = ifelse(likert < 1))
  group_by(paradigm, .add =T) %>%
  # group_by(dprime, .add =T) %>%
  summarise(rDE = mean(relative_timing), 
            semSD = sd(rDE)/sqrt(n())) 

  # mutate(likert = ifelse(likert %in% veryFast, "Very Fast", as.character(likert)),



SDvar_duration_nback <- ggplot(data = SD_Var,
             aes(x = nback,
                 y = VarSD,
                 group = duration,
                 fill = interaction(duration, nback))) +
  labs(x = "WM load", y = "Subjective duration variance (s²)") +
  theme_classic() +
  theme(legend.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 12),
        plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_fill_manual(values = cbPalette4, name = "Duration",
  labels = c("45s", "90s", "45s", "90s")) +
  geom_bar(stat = "identity", width = .7, position = "dodge", alpha = 0.5) +
  geom_errorbar(aes(ymin =VarSD - semSD, ymax = VarSD + semSD),
  width = 0.1,
  show.legend = FALSE)
  # position = position_dodge(.8)) 
  # geom_signif(stat="identity",
  #             data=data.frame(x=c(0.875, 1.875), xend=c(1.125, 2.125),
  #                             y=c(5.8, 8.5), annotation=c("**", "**")),
  #             aes(x=x,xend=xend, y=y, yend=y, annotation=annotation)) 
  # geom_signif(comparisons=list(c("S1", "S2")), annotations="***",
  #             y_position = 9.3, tip_length = 0, vjust=0.4) 

#location of the cuts
data <- data %>%
  mutate( tertile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/3))), include.lowest=TRUE)) %>%
  mutate(quantile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/5))), include.lowest=TRUE))

summary(data)

Nback_blocks <- data %>%
  mutate(quantile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/5))), include.lowest=TRUE),
  quantile = ifelse(quantile == "[0,0.444]", "1st     \n [0, 0.444]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.444,0.667]", "2nd     \n (0.444, 0.667]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.667,0.889]", "3rd     \n (0.667, 0.889]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.889,1.33]", "4th     \n (0.889, 1.33]", as.character(quantile)),
  quantile = ifelse(quantile == "(1.33,2.67]", "5th     \n (1.33, 2.67]", as.character(quantile)),     
  tertile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/3))), include.lowest=TRUE),
  tertile = ifelse(tertile == "[0,0.667]", "1st     \n [0, 0.667]", as.character(tertile)),
  tertile = ifelse(tertile == "(0.667,1]", "2nd     \n (0.667, 1]", as.character(tertile)),
  tertile = ifelse(tertile == "(1,2.78]", "3rd     \n (1, 2.78]", as.character(tertile)))
```



#histogram rDE for retro and prospective
```{r}
retroHistorDE <- Nback_blocks %>%
  filter(paradigm == "retrospective") %>%
  ggplot(aes(x= relative_timing, fill = nback, color = nback)) +
    geom_histogram(binwidth= 0.3, alpha=0.4) +
  facet_grid(nback~.,  labeller = labeller(nback = c(`1back` = "1-back", `3back` = "3-back"))) +
   geom_vline(aes(xintercept = 1), colour = 'black', size = .6, linetype = "dashed") +
  labs(x = "rDE", title = "retrospective") +
  theme_classic() +
  theme(legend.position="none",
          plot.title = element_text(face = "bold", "hjust" = 0.5),
          title = element_text(size = 9),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 11)) +
  scale_colour_manual(values = c("1back" = "#42A5F5", "3back" = "#0D47A1")) +
  scale_fill_manual(values = c("1back" = "#42A5F5", "3back" = "#0D47A1")) 
  
proHistorDE <-Nback_blocks %>%
  filter(paradigm == "prospective") %>%
  ggplot( aes(x= relative_timing, fill = nback, color = nback)) +
    geom_histogram(binwidth= 0.3, alpha=0.9) +
  facet_grid(nback~.,  labeller = labeller(nback = c(`1back` = "1-back", `3back` = "3-back"))) +
   geom_vline(aes(xintercept = 1), colour = 'black', size = .6, linetype = "dashed") +
  labs(x = "rDE", title = "prospective") +
  theme_classic() +
  theme(legend.position="none",
          plot.title = element_text(face = "bold", "hjust" = 0.5),
         title = element_text(size = 9),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 11)) +
  scale_colour_manual(values = c("1back" = "#42A5F5", "3back" = "#0D47A1")) +
  scale_fill_manual(values = c("1back" = "#42A5F5", "3back" = "#0D47A1")) 

  # jpeg("DoubleHistorDE.jpg", width = 4000, height = 2500, units = "px",res=600)
# right_row <- plot_grid(GlobalViolinRTDuration, GlobalViolinRTILI, labels = c('h', 'i'), align = 'h', ncol = 1, rel_heights = c(0.8, 0.8))
DoubleHistorDE <- plot_grid(retroHistorDE, proHistorDE, nrow = 1)
DoubleHistorDE
# dev.off()

```



#d' x WM Load
```{r}
DD <- Nback_blocks %>%
   group_by(paradigm) %>%
  group_by(nback, .add =T) %>% 
  summarize(DD = mean(relative_timing), 
            semDD = sem(relative_timing))


WMLoadParadigmrDE <- DD %>%
  ggplot (aes(x = nback,
                 y = DD)) +
  scale_y_continuous(breaks = seq(from = 0.70, to = 1.10, by = 0.10),
                     limits = c(0.70, 1.10)) +
  geom_hline(aes(yintercept = 1), 
             colour = 'black', 
             size = 0.6, 
             linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = paradigm, colour = paradigm), size = 1) +
  theme_classic() +
  labs(y = "rDE", 
       x = "WM Load") +
  theme( legend.text = element_text(size = 11),
         legend.title  = element_text(size = 12),
          axis.text = element_text(size = 12),
  legend.position = c(.5, .87),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD),
                colour = "black",
                width = .05) +
  scale_colour_manual(name = "", values = graycontinuous, labels = c("prospective", "retrospective")) +
   scale_x_discrete(labels = c("1-back", "3-back")) 

WMLoadParadigmrDE 
```




##Interaction effect ParadigmxDuration on rDE - Visualization
```{r}


   
  violinrDEdurationParadigm<- Nback_blocks %>% 
    mutate(paradigmduration = paste(paradigm, duration),
           paradigmduration =  fct_relevel(paradigmduration, "retrospective 45s", "prospective 45s", "retrospective 90s", "prospective 90s")) %>%
  ggplot(aes(paradigmduration, relative_timing, colour = paradigmduration)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
      # facet_grid(ILI~.) +
  theme_classic() +
  labs(y = "rDE", x = "Paradigm : Task Duration", title = "rDE for different Parradigm and Task Duration") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("retrospective 45s", "prospective 45s"), c("retrospective 90s", "prospective 90s"))) 
   
     

# jpeg("violinrDEdurationParadigm", width = 5000, height = 3500, units = "px",res=600)
   violinrDEdurationParadigm
# dev.off()
```


##rDE  Direction x WM Load / Direction x Duration
```{r}
##Duration graphs without ILI

DD <- Nback_blocks %>%
   group_by(paradigm) %>%
  group_by(nback, .add =T) %>% 
  summarize(DD = mean(relative_timing), 
            semDD = sem(relative_timing))

WMLoadParadigmrDE <- DD %>%
  ggplot (aes(x = nback,
                 y = DD)) +
  scale_y_continuous(breaks = seq(from = 0.80, to = 1, by = 0.05),
                     limits = c(0.80, 1.02)) +
  geom_hline(aes(yintercept = 1), 
             colour = 'black', 
             size = 0.6, 
             linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = paradigm, linetype = paradigm, colour = paradigm), size = 1) +
  theme_classic() +
  labs(y = "rDE", 
       x = "WM Load") +
  theme( legend.text = element_text(size = 10),
         legend.position = "None",
         legend.title  = element_text(size = 11),
          axis.text = element_text(size = 11),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD),
                colour = "black",
                width = .05) +
  scale_colour_manual(name = "", values = c("retrospective" ="#90A4AE" , "prospective" = "#455A64")) +
  scale_linetype_manual(values = c("retrospective" = "dashed", "prospective" = "solid")) +
   scale_x_discrete(labels = c("1-back", "3-back")) 



DD <- Nback_blocks %>%
   group_by(paradigm) %>%
  group_by(duration, .add =T) %>% 
  summarize(DD = mean(relative_timing), 
            semDD = sem(relative_timing))

DurationParadigmrDE <- DD %>%
  ggplot (aes(x = duration,
                 y = DD)) +
  scale_y_continuous(breaks = seq(from = 0.80, to = 1, by = 0.05),
                     limits = c(0.80, 1.02)) +
  geom_hline(aes(yintercept = 1), 
             colour = 'black', 
             size = 0.6, 
             linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = paradigm, linetype = paradigm, colour = paradigm), size = 1) +
  theme_classic() +
  labs(y = "rDE", 
       x = "Duration (s)") +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD),
                colour = "black",
                width = .05) +
  scale_colour_manual(name = "Direction",values = c("retrospective" ="#90A4AE" , "prospective" = "#455A64")) +
    scale_linetype_manual (name = "Direction", values = c("retrospective" = "dashed", "prospective" = "solid")) +
  theme( legend.text = element_text(size = 10),
         legend.title  = element_text(size = 11),
          axis.text = element_text(size = 11),
         legend.position = "bottom",
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
   scale_x_discrete(labels = c("45", "90")) 
   
legend <- get_legend(DurationParadigmrDE)
# svg("WMLDirectionLegend.svg", width = 16, height = 6)
legend
# dev.off()


# jpeg("WMLoadParadigmrDE.jpg", width = 2500, height = 2500, units = "px",res=600)
WMLoadParadigmrDE
# dev.off()

# jpeg("DurationParadigmrDE.jpg", width = 2500, height = 2500, units = "px",res=600)
DurationParadigmrDE
# dev.off()

# jpeg("DirectionCrossedEffectGlobal", width = 4000, height = 2500, units = "px",res=600)
 Toprow <- plot_grid( WMLoadParadigmrDE, DurationParadigmrDE +  theme(legend.position="none"), ncol = 2, labels = c('a', 'b'), align = 'v')
 Toprow
 # plot_grid(Toprow,  legend, nrow = 2)
  # dev.off()
 
 # svg("WMLDirection.svg2", width = 10, height = 6)
  Toprow
 # dev.off()
  
  
  
  plotgrid(Toprow)
```




##Session effect on Relative Duration Estimation - Visualization
```{r}
# jpeg("violinSessionrDEGlobal.jpg", width = 2500, height = 2500, units = "px",res=600)

rDESessionGlobal <- Nback_blocks %>% 
   ggplot(aes(y = relative_timing, x = Session, colour = Session)) + 
  geom_violin(outlier.shape=NA, aes(alpha = Session)) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "rDE", x ="Session") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 10), 
 axis.title = element_text(size = 11)) +
  scale_colour_manual(values = c("SC" = "#90A4AE", "S1" = "black")) +
    scale_x_discrete(labels = c("Lockdown", "Control")) +
    stat_compare_means(symnum.args = symnum, method = "wilcox.test", label.y = 2.70, paired = FALSE, label = "p.signif", tip.length = 0, comparisons = list(c("SC","S1"))) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))
rDESessionGlobal
# dev.off()

```




































#PASSAGE OF TIME JUDGMENT (PoTJ)


##PoTJ tables - % respondant for each likert answer
```{r}
Likert_nback <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(nback, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(nback) %>%
	spread(likert, perc) %>% 
  rename(design = nback)
   
Likert_ILI <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(ILI, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(ILI) %>%
	spread(likert, perc) %>% 
  rename(design = ILI) %>% 
  mutate(design = fct_recode(design, "1500ms" = "1500", "1800ms" = "1800"))

Likert_duration <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(duration, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(duration) %>%
	spread(likert, perc) %>% 
  rename(design = duration) %>%
  mutate(design = fct_recode(design, "45s" = "45", "90s" = "90"))
   

Likert_all <- bind_rows(Likert_ILI, Likert_nback, Likert_duration)
  
paged_table(Likert_all)  
```

##PoTJ VS ILI, WM Load & Duration (design paramaters) - 3 diverging stacked bar
```{r}
#PoTJ vs Duration
likert_hi_lo <- Likert_duration %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("duration", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

POTJduration <- ggplot() + 
    	geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	labs(x = "Duration (s)", y = "") +
 scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-62,60)) +
     scale_x_discrete(labels = c("45", "90")) +
	theme_classic() +
  theme(legend.position = "none") +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "45s", "90s", "***"), y.position = 59, label = "signif", tip.length = 0)

	
	
	
	#PoTJ vs ILI
likert_hi_lo <- Likert_ILI %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("ILI", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

POTJILI <- ggplot() + 
    	geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5,  alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5,  alpha = 0.9) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	labs(x = "ILI (ms)", y ="") +
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-62,60)) +
     scale_x_discrete(labels = c("1500", "1800")) +
	theme_classic() +
  theme(legend.position = "none") +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "1500ms", "1800ms", "***"), y.position = 59, label = "signif", tip.length = 0)

	

#PoTJ vs WM Load
	likert_hi_lo <- Likert_nback %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("nback", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

POTJNback <- ggplot() + 
    	geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	labs(x = "WM Load", y = "") +
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-62,60)) +
     scale_x_discrete(labels = c("1-back", "3-back")) +
	theme_classic() +
  theme(legend.position = "none") +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "1back", "3back", "***"), y.position = 59, label = "signif", tip.length = 0)

  
	

#Merge the three graphs

          
# jpeg("divergingBarGlobalPoTJ", width = 4000, height = 2500, units = "px",res=600)
 plot_grid( POTJNback, POTJduration, POTJILI, legend, ncol = 4, labels = c('a', 'b', 'c'), align = 'v')
  # dev.off()
```

##PoTJ Vs paradigm diverging stacked bar
```{r}
#PoTJ vs Paradigm


Nback_blocks <- Nback_blocks %>%
  mutate(paradigm = fct_relevel(paradigm, "prospective", "retrospective"))


Likert_paradigm <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Fast", "Fast", "Neutral", "Slow", "Very Slow"  )) %>%
	group_by(paradigm, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(paradigm) %>%
	spread(likert, perc) %>% 
  rename(design = paradigm)


likert_hi_lo <- Likert_paradigm %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Fast`, Fast, midlow, midhigh, Slow, `Very Slow`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("paradigm", "response", "perc"))

	
likert_lo <- likert_hi_lo %>%
	filter(response %in% c("Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c("midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c( "Very Slow", "Slow","midhigh", "midlow", "Fast", "Very Fast" )

POTJParadigm  <- ggplot() + 
    	geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast", "Neutral", "Slow", "Very Slow" )) +
	labs(x = "", y = "PoT") +
 scale_y_continuous(breaks = seq(from = -80, to = 60, 20),
                     limits = c(-78,68)) +
     scale_x_discrete(	breaks = c( "prospective", "retrospective"),labels = c("prospective", "retrospective")) +
	theme_classic() + theme(legend.position = "none", axis.text.x = element_text(size = 10.5)) +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "retrospective", "prospective", "***"), y.position = 60, label = "signif", tip.length = 0)

# jpeg("PoTJParadigmGlobal", width = 2000, height = 3000, units = "px",res=600)
POTJParadigm
# dev.off()

# # jpeg("divergingBarGlobalPoTJ2", width = 4000, height = 2500, units = "px",res=600)
#  plot_grid( POTJNback, POTJduration, POTJILI, POTJParadigm, ncol = 4,  align = 'v')
#   # dev.off()
#   
#   # jpeg("divergingBarGlobalPoTJ3", width = 5000, height = 3000, units = "px",res=600)
#  plot_grid( POTJNback, POTJduration, POTJILI, POTJParadigm, nrow = 2, ncol = 2,  align = 'v')
#   # dev.off()
#  
#  jpeg("divergingBarGlobalPoTJ4", width = 2500, height = 3500, units = "px",res=600)
#  plot_grid( POTJNback +coord_flip(), POTJduration +coord_flip(), POTJILI +coord_flip(), POTJParadigm +coord_flip(), nrow = 4,  align = 'v')
#   dev.off()

# svg("DirectionPoT.svg", width = 3, height = 6)
POTJParadigm
# dev.off()
```
#PoTJ vs Session
```{r}
Likert_session <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Fast", "Fast",   "Neutral", "Slow",  "Very Slow" )) %>%
	group_by(Session, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(Session) %>%
	spread(likert, perc) %>% 
  rename(design = Session) 


	likert_hi_lo <- Likert_session %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Fast`, `Fast`, midlow, midhigh, `Slow`, `Very Slow`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("session", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c("Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c( "Very Slow", "Slow","midhigh", "midlow", "Fast", "Very Fast" )

POTJSession  <- ggplot() + 
  	geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) + 
	scale_fill_manual(values = legend_pal,
	                  name = "PoT",
		breaks = c("Very Slow", "Slow","midhigh", "Fast", "Very Fast"  ),
		labels = c("Very Slow", "Slow","Neutral", "Fast", "Very Fast" )) +
	labs(x = "Session", y = "")  +
  scale_x_discrete(labels = c("Lockdown", "Control")) +
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-60,60)) +
	theme_classic() + theme(axis.text = element_text(size = 10), 
 axis.title = element_text(size = 11)) +
  stat_pvalue_manual(tibble::tribble(
  ~group1, ~group2,   ~signif,
    "SC",     "S1", "*"), y.position = 60, label = "signif", tip.length = 0)

legend <- get_legend(POTJSession)

# jpeg("PoTJSessionGlobal", width = 3000, height = 2500, units = "px",res=600)
POTJSession
# dev.off()
  
   # jpeg("SessionGlobal.jpg", width = 4000, height = 2500, units = "px",res=600)
SessionGlobal <- plot_grid(rDESessionGlobal, POTJSession + theme(legend.position = "None"), legend, labels = c('a', 'b'), align = 'h', nrow = 1)
SessionGlobal
# dev.off()

# svg("SessionGlobal.svg", width = 12, height = 6)
SessionGlobal
# dev.off()

```








#Passing of time statistic models
```{r}

data <- Nback_blocks  %>%
  filter(!is.na(likert)) #15620 obs

library(MASS)

m1 = clmm(likert ~ duration + (1|PID), data, Hess=T, nAGQ= 7)

m2 = clmm(likert ~ duration + nback + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m1,m2)  # p < 0.05*** m2 is significantly better than m1

m3 = clmm(likert ~ duration + ILI + nback + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m2,m3) #p < 0.05***

m4 = clmm(likert ~ duration + ILI + nback + dprime + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m3,m4) #p > 0.05 m4 best likelihood and AIC

m5 = clmm(likert ~ duration + ILI + dprime + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m3,m5) # comparable likelihood ratio, but M3 better AIC than m5

m6 = clmm(likert ~ duration + ILI + nback + logbeta + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m3,m6) #p < 0.05 ***

m7 = clmm(likert ~ duration + ILI + nback + logbeta + Session + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m6,m7)  #p > 0.05 m4 best likelihood and AIC

m8 = clmm(likert ~  duration + ILI + nback + logbeta + paradigm + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m6,m8)  # p > 0.05***

m9 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:paradigm + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m8,m9) # p > 0.05 

m10 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m8,m10) # p < 0.05 ***

m11 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m10,m11) # p < 0.05*  no interaction between Session and ILI, dprime,logbeta

m12 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + paradigm:duration + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m11,m12) # p < 0.05** no interaction between paradigm and nback, ILI, dprime, or logbeta

m13 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + paradigm:duration + nback:duration + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m12,m13) # p > 0.05 m13 not better than m12

m14 = clmm(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + paradigm:duration + nback:duration + dprime:duration + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m12,m14) # p > 0.05 m14 not better than m12


compare_performance(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14) #m12, m13, m14 best AIC

lrtest(m1,m2)
lrtest(m2,m3)
lrtest(m3,m6)
lrtest(m6,m8)
lrtest(m8,m10)
lrtest(m10,m11)
lrtest(m11,m12)



summary(m1)
summary(m2)
summary(m3)
summary(m4)
summary(m5)
summary(m6) 
summary(m7)
summary(m8)
summary(m9)  
summary(m10) 
summary(m11)
summary(m12) #best model
summary(m13)
summary(m14)

#to verify without mixed model
m12b <- polr(likert ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + paradigm:duration, data, Hess=T)
summary(m12b)

summary(m12)
coeffs <- coef(summary(m12))
p <- pnorm(abs(coeffs[, "z value"]), lower.tail = FALSE) * 2
cbind(coeffs, "p value" = round(p,3)) #get the p-value for each effect
confint(m12, oldNames=FALSE)

exp(cbind(OR = coef(m12), ci = confint(m12))) #logit effects are difficult to interpret --> exp() to have % change


emmeans(m12, pairwise ~ duration + paradigm)
#cclm assumptions


#collinearity
check_collinearity(m12) #ok, moderate correlation



##Proportional odds assumption
require(Hmisc)

sf <- function(y) {
  c(
    'Y>=1' = qlogis(mean(y >= 1)),
    'Y>= 2' = qlogis(mean(y >= 2)),
    'Y>= 3' = qlogis(mean(y >= 3)),
    'Y>= 4' = qlogis(mean(y >= 4)),
    'Y>=5' = qlogis(mean(y >= 5)))
}

s <- with(data, summary(as.numeric(likert) ~ duration + ILI + nback + logbeta + paradigm + Session:duration + Session:nback + paradigm:duration, fun=sf))
s

s[, 6] <- s[, 6] - s[, 3]
s[, 5] <- s[, 5] - s[, 3]
s[, 4] <- s[, 4] - s[, 3]
s[, 3] <- s[, 3] - s[, 3]
s

plot(s, which=1:5, pch=1:5, xlab='logit', main=' ', xlim=range(s[,3:6]))


```





##PoTJ tables - % respondant for each likert answer Session x Duration
```{r}
Likert_SessionDuration <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(Session, duration, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(Session, duration) %>%
	spread(likert, perc) %>% 
  mutate(design = paste(Session,duration)) %>%
  ungroup() %>%
  dplyr::select(-duration, -Session)

Likert_SessionDuration

likert_hi_lo <- Likert_SessionDuration %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("design", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))


# Use RColorBrewer to store a preset diverging colour palette as a vector of colour codes 
legend_pal <- brewer.pal(name = "RdBu", n = 5)

# Duplicate the middle value, remember that "Sometimes" is actually two groups, "midhigh" and "midlow"
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

# Replace the ugly white colour for "Sometimes" with a pleasant dishwater grey
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

# jpeg("PotSessionDuration.jpg", width = 5000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	coord_flip() + 
	labs(x = "Session:Duration", y = "Percentage of respondents (%)", title = "Diverging stacked bar of likert scale PoTJ for different conditions") +
  scale_y_continuous(breaks = seq(from = -60, to = 70, 10),
                     limits = c(-65,70)) +
	theme_classic()
# dev.off()
   

```
##PoTJ tables - % respondant for each likert answer Session x WM Load
```{r}
Likert_SessionWMLoad <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(Session, nback, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(Session, nback) %>%
	spread(likert, perc) %>% 
  mutate(design = paste(Session,nback)) %>%
  ungroup() %>%
  dplyr::select(-nback, -Session)

Likert_SessionWMLoad

likert_hi_lo <- Likert_SessionWMLoad %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("design", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))


# Use RColorBrewer to store a preset diverging colour palette as a vector of colour codes 
legend_pal <- brewer.pal(name = "RdBu", n = 5)

# Duplicate the middle value, remember that "Sometimes" is actually two groups, "midhigh" and "midlow"
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

# Replace the ugly white colour for "Sometimes" with a pleasant dishwater grey
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

# jpeg("PotSessionWMLoad.jpg", width = 5000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	coord_flip() + 
	labs(x = "Session:WMLoad", y = "Percentage of respondents (%)", title = "Diverging stacked bar of likert scale PoTJ for different conditions") +
  scale_y_continuous(breaks = seq(from = -60, to = 70, 10),
                     limits = c(-65,70)) +
	theme_classic()
# dev.off()
   

```



##d' X PoTJ violin plot
```{r}
my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(filter(Nback_blocks, paradigm == "retrospective")$likert),")", sep="")
my_comparison = list( c("Very Slow", "Neutral"), c("Neutral", "Very Fast"), c("Very Slow", "Very Fast"))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- rev(legend_pal)

# jpeg("PoTdretro", width = 3000, height = 2500, units = "px",res=600)
PoTdretro<- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
  filter(paradigm == "retrospective") %>%
   ggplot(aes(y = dprime, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1, alpha = 0.10) +
  geom_boxplot(alpha = 0.2, width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  scale_y_continuous(breaks = seq(from = 0, to = 5, by = 1),
  limits = c(0, 5.2)) +
  stat_summary(fun = mean)  +
  scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
   theme_classic() +  
  labs(y = "d'", x ="PoT") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 10),
          axis.text.x = element_text(size = 9.5), 
 axis.title = element_text(size = 11),
 legend.position ="None") +
 stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",
 comparison = my_comparison, label.y = c(4.55,4.55,4.9), tip.length = 0)
 PoTdretro
# dev.off()

 
my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(filter(Nback_blocks, paradigm == "prospective")$likert),")", sep="")
my_comparison = list( c("Very Slow", "Neutral"), c("Neutral", "Very Fast"), c("Very Slow", "Very Fast"))

# jpeg("PoTJDJpro", width = 3000, height = 2500, units = "px",res=600)
PoTdpro<- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
  filter(paradigm == "prospective") %>%
   ggplot(aes(y = dprime, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1, alpha = 0.25) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  scale_y_continuous(breaks = seq(from = 0, to = 5, by = 1),
  limits = c(0, 5.2)) +
  stat_summary(fun = mean)  +
  scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
   theme_classic() +  
  labs(y = "d'", x ="PoT") +  
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 10),
          axis.text.x = element_text(size = 9.5), 
 axis.title = element_text(size = 11),
 legend.position ="None") +
 stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif",
 label.y = c(4.55,4.55,4.9), comparison = my_comparison,  tip.length = 0)
 PoTdpro
# dev.off()
 
```


Direction x WM Load : PoT
```{r}


#RETRO
Likert_retroWMLoad <-  Nback_blocks %>%
   filter(!is.na(likert)) %>%
  filter(paradigm == "retrospective") %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(nback, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(nback) %>%
	spread(likert, perc) %>% 
  rename(design = nback)


likert_hi_lo <- Likert_retroWMLoad %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("design", "response", "perc"))
	
likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

POTretroWMLoad <- ggplot() + 
    	geom_hline(yintercept = 0, color =c("black"), size = 0.3 ) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.6) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.6) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	coord_flip() + 
	labs(x = "WM Load", y = "PoT") +
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-62,62)) +
     scale_x_discrete(labels = c("1-back", "3-back")) +
	theme_classic() +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "1back", "3back", "***"), y.position = 60, label = "signif", tip.length = 0, coord.flip = TRUE) +
  theme(legend.position = "none") 
POTretroWMLoad


#PRO
Likert_proWMLoad <-  Nback_blocks %>%
   filter(!is.na(likert)) %>%
  filter(paradigm == "prospective") %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(nback, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(nback) %>%
	spread(likert, perc) %>% 
  rename(design = nback)


likert_hi_lo <- Likert_proWMLoad %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(design, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("design", "response", "perc"))
	
likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)
names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

POTproWMLoad <- ggplot() +   	
  geom_hline(yintercept = 0, color =c("black"), size = 0.3) + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.9) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
	coord_flip() + 
	labs(x = "WM Load", y = "PoT") +
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-62,60)) +
     scale_x_discrete(labels = c("1-back", "3-back")) +
	theme_classic() + theme(legend.position = "none") +
   stat_pvalue_manual(tibble::tribble(~group1, ~group2, ~signif, "1back", "3back", "n.s."), y.position = 55, label = "signif", tip.length = 0, coord.flip = TRUE) 


POTproWMLoad



#Merge 4 figures
# jpeg("4barsDirectionPerf", width = 6000, height = 4500, units = "px",res=600)

leftcol <- plot_grid(POTproWMLoad + labs(title = "prospective") + theme(plot.title = element_text(size = 10, "hjust" = 0.5)),
                          PoTdpro, nrow = 2,  align = 'v',labels = c('a', 'c'),  rel_heights = c(0.8, 1.2))

rightcol <- plot_grid(POTJParadigm, labels = 'e')

  middlecol <- plot_grid(POTretroWMLoad + labs(title = "retrospective") + theme(plot.title = element_text(size = 10, "hjust" = 0.5)), 
                       PoTdretro, nrow = 2,  align = 'v', labels = c('b', 'd'), rel_heights = c(0.8, 1.2))
  
   
  svg("Fig5Direction.svg", width = 12, height = 6)
  plot_grid( leftcol, middlecol, rightcol, ncol = 3,  align = 'v', rel_widths =  c(1.2, 1.2, 0.9))
  dev.off()
  
# svg("4barsDirectionPerfl.svg", width = 10, height = 6)
  plot_grid( leftcol, middlecol , ncol = 2,  align = 'v')
# dev.off()
```










##Relative Timing X PoTJ violin plot
```{r}
my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(Nback_blocks$likert),")", sep="")
my_comparison = list( c("Very Slow", "Neutral"), c("Neutral", "Very Fast"), c("Very Slow", "Very Fast"))

legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- rev(legend_pal)


# jpeg("PoTJrDEglobal", width = 3000, height = 2500, units = "px",res=600)
PoTJrDEglobal <- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
   ggplot(aes(y = relative_timing, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1,       alpha = 0.3) +
  
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  stat_summary(fun = mean)  +
scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
   scale_y_continuous(breaks = c(0, 1, 2, 3),
                     limits = c(0, 3.1)) +
   theme_classic() +  
  labs(y = "rDE", x ="PoT") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 11),
 legend.position ="None") +
 stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", 
                    label.y = c(2.67,2.67,2.9),  tip.length = 0, comparison = my_comparison) 
PoTJrDEglobal
# dev.off()

my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(filter(Nback_blocks, paradigm == "prospective")$likert),")", sep="")
my_comparison = list( c("Very Slow", "Neutral"), c("Neutral", "Very Fast"), c("Very Slow", "Very Fast"))

# jpeg("PoTJrDEpro", width = 3000, height = 2500, units = "px",res=600)
PoTJrDEpro <- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
    filter(paradigm == "prospective") %>%
   ggplot(aes(y = relative_timing, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1,       alpha = 0.3) +
  
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  stat_summary(fun = mean)  +
scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
   scale_y_continuous(breaks = c(0, 1, 2, 3),
                     limits = c(0, 3.1)) +
   theme_classic() +  
  labs(y = "rDE", x ="PoT") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 11),
 legend.position ="None") +
 stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", 
                    label.y = c(2.67,2.67,2.9),  tip.length = 0, comparison = my_comparison) 
PoTJrDEpro
# dev.off()

my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(filter(Nback_blocks, paradigm == "retrospective")$likert),")", sep="")
my_comparison = list( c("Very Slow", "Neutral"), c("Neutral", "Very Fast"), c("Very Slow", "Very Fast"))

# jpeg("PoTJrDEretro", width = 3000, height = 2500, units = "px",res=600)
PoTJrDEretro <- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
    filter(paradigm == "retrospective") %>%
   ggplot(aes(y = relative_timing, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1,       alpha = 0.3) +
  
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  stat_summary(fun = mean)  +
scale_fill_manual(values = legend_pal, 
	                  name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
   scale_y_continuous(breaks = c(0, 1, 2, 3),
                     limits = c(0, 3.1)) +
   theme_classic() +  
  labs(y = "rDE", x ="PoT") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 11),
 legend.position ="None") +
 stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.signif", 
                    label.y = c(2.67,2.67,2.9),  tip.length = 0, comparison = my_comparison) 
PoTJrDEretro
# dev.off()


```




#Break Relative timing in tertiles or quantiles
```{r}


#location of the cuts
data <- Nback_blocks %>%
  mutate( tertile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/3))), include.lowest=TRUE)) %>%
  mutate(quantile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/5))), include.lowest=TRUE))

summary(data)

Nback_blocks <- data %>%
  mutate(quantile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/5))), include.lowest=TRUE),
  quantile = ifelse(quantile == "[0,0.444]", "1st     \n [0, 0.444]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.444,0.667]", "2nd     \n (0.444, 0.667]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.667,0.889]", "3rd     \n (0.667, 0.889]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.889,1.33]", "4th     \n (0.889, 1.33]", as.character(quantile)),
  quantile = ifelse(quantile == "(1.33,2.67]", "5th     \n (1.33, 2.67]", as.character(quantile)),     
  tertile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/3))), include.lowest=TRUE),
  tertile = ifelse(tertile == "[0,0.667]" , "1st [0, 0.67]", as.character(tertile)),
  tertile = ifelse(tertile == "(0.667,1]", "2nd (0.67, 1]", as.character(tertile)),
  tertile = ifelse(tertile == "(1,2.78]", "3rd (1, 2.78]", as.character(tertile)))

  # mutate(tertile = fct_relevel(tertile, "[0,0.667]","(0.667, 1]","(1,2.78]", levels = c("[0,0.667]","(0.667, 1]","(1,2.78]")))

    
  summary(Nback_blocks)

Likert_quantile <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(quantile, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(quantile) %>%
	spread(likert, perc) 

Likert_quantile

Likert_tertile <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slow", "Slow",  "Neutral", "Fast", "Very Fast")) %>%
	group_by(tertile, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(tertile) %>%
	spread(likert, perc) 

Likert_tertile
```


##PoTJ X Relative Timing - Diverging stacked bar 
```{r}

#PoTJ vs Relative Timing (tertiles)
likert_hi_lo <- Likert_tertile %>%
	mutate(midlow = Neutral / 2,
		midhigh = Neutral / 2) %>%
	dplyr::select(tertile, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("tertile", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))


legend_pal <- brewer.pal(name = "BrBG", n = 5)
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
legend_pal <- rev(legend_pal)

names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )

# jpeg("PoTJBarsrDEtertile.jpg", width = 4000, height = 2500, units = "px",res=600)
PoTJrDEtertile <- ggplot() + 
    geom_hline(yintercept = 0, color =c("black"), size = 0.3) +
	geom_bar(data = likert_hi, aes(x = tertile, y=perc, fill = response), stat="identity", width = 0.5, alpha = 0.7) +
	geom_bar(data = likert_lo, aes(x = tertile, y=-perc, fill = response), stat="identity", width = 0.5, alpha = 0.7) + 
	scale_fill_manual(values = legend_pal, 
	                  name = "PoT (retrospective, prospective)",
		breaks =c("Very Slow", "Slow","midhigh","Fast", "Very Fast" ),
		labels = c("Very Slow", "Slow", "Neutral", "Fast", "Very Fast")) +
  labs(x = "rDE", y ="") + 
   theme_classic() +
  theme(axis.text = element_text(size = 10.5), 
 axis.title = element_text(size = 11), legend.position="bottom", legend.text = element_text(size = 9)) +
	coord_flip() + 
  scale_y_continuous(breaks = seq(from = -60, to = 60, 20),
                     limits = c(-60,60)) +
 stat_pvalue_manual(tibble::tribble(
  ~group1, ~group2,   ~signif,
    "1st [0, 0.67]", "3rd (1, 2.78]", "***"), y.position = 60, label = "signif", tip.length = 0, coord.flip = TRUE) +
  scale_x_discrete(labels = c("[0, 0.67]","(0.67, 1]","(1, 2.78]")) 


	
legend <- get_legend(PoTJrDEtertile)
legend
PoTJrDEtertile
# dev.off()

# jpeg("PoTJvsrDE", width = 3000, height = 3500, units = "px",res=600)
  plot_grid( PoTJrDEtertile, PoTJrDEglobal, nrow = 2,  align = 'v',  labels = c('a', 'b'),  rel_heights = c(0.8, 1.2))
  # dev.off()
  
  
svg("PoTJvsrDE.svg", width = 7, height = 6)
plot_grid(PoTJrDEtertile, PoTJrDEglobal, nrow = 2,   labels = c('a', 'b'), align = 'v', rel_heights = c(0.8, 1.2))
dev.off()

```





#Ordinal Regression Model - Does rDE a good predictor of PoTJ - interaction with Session and paradigm ?
```{r}

#effect of relative Duration Estimation (rDE) on PoTJ likert scale

data = Nback_blocks %>%
  filter(!is.na(likert)) #15620 obs

library(MASS)

mm1 = clmm(likert ~ relative_timing + (1|PID), lin = "logit", data, Hess=T, nAGQ= 7)


mm2 = clmm(likert ~ relative_timing + relative_timing:Session + (1|PID), lin = "logit", data, Hess=T, nAGQ= 7)
lrtest(mm1, mm2) #p > 0.05 no interaction effect between rDE and Session was found

mm3 = clmm(likert ~ relative_timing + relative_timing:paradigm +(1|PID), lin = "logit", data, Hess=T, nAGQ= 7)
lrtest(mm1, mm3) #p < 0.05*** 


lrtest(mm1, mm2, mm3)
AIC(mm1, mm2, mm3)


summary(mm3)
  confint(mm3, oldNames=FALSE)
coeffs <- coef(summary(mm3))
p <- pnorm(abs(coeffs[, "z value"]), lower.tail = FALSE) * 2
cbind(coeffs, "p value" = round(p,3)) #get the p-value for each effect
exp(cbind(OR = coef(mm3), ci = confint(mm3))) #logit effects are difficult to interpret --> exp() to have % change

# newdat <- data.frame(nback =c(,1))
# (phat <- predict(object = m, newdat, type="p"))

summary(mm3)
emmeans(mm3,  ~ relative_timing , at = list(relative_timing = c(0.33, 0.66, 1, 1.33, 1.66)))
emmeans(mm3, pairwise ~ paradigm + relative_timing , at = list(relative_timing = c(0.33, 0.66, 1, 1.33, 1.66)))
emmeans(mm3, pairwise ~ paradigm + relative_timing , at = list(relative_timing = c(0.33, 0.8, 1.5, 2.3)))

##Proportional odds assumption
require(Hmisc)

sf <- function(y) {
  c(
    'Y>=1' = qlogis(mean(y >= 1)),
    'Y>= 2' = qlogis(mean(y >= 2)),
    'Y>= 3' = qlogis(mean(y >= 3)),
    'Y>= 4' = qlogis(mean(y >= 4)),
    'Y>=5' = qlogis(mean(y >= 5)))
}

s <- with(data, summary(as.numeric(likert) ~ relative_timing + relative_timing:paradigm, fun=sf))
s

s[, 6] <- s[, 6] - s[, 3]
s[, 5] <- s[, 5] - s[, 3]
s[, 4] <- s[, 4] - s[, 3]
s[, 3] <- s[, 3] - s[, 3]
s

plot(s, which=1:5, pch=1:5, xlab='logit', main=' ', xlim=range(s[,3:6]))
```






<!-- ##Interaction effect ParadigmxDuration on rDE - Visualization -->
<!-- ```{r} -->



<!--   violinrDEdurationParadigm<- Nback_blocks %>%  -->
<!--     mutate(paradigmduration = paste(paradigm, duration), -->
<!--            paradigmduration =  fct_relevel(paradigmduration, "retrospective 45s", "prospective 45s", "retrospective 90s", "prospective 90s")) %>% -->
<!--   ggplot(aes(paradigmduration, relative_timing, colour = paradigmduration)) + -->
<!--   geom_violin(outlier.shape=NA) + -->
<!--   geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) + -->
<!--   geom_hline(aes(yintercept = 1), colour = 'black', size = 0.3, linetype = "dashed") + -->
<!-- stat_summary(fun = mean)  + -->
<!--       # facet_grid(ILI~.) + -->
<!--   theme_classic() + -->
<!--   labs(y = "rDE", x = "Paradigm : Task Duration", title = "rDE for different Paradigm and Task Duration") + -->
<!--   theme( legend.position="none", -->
<!--         axis.title.x = element_text(size = 12), -->
<!--          axis.title.y = element_text(size = 12), -->
<!--         axis.text = element_text(size = 12), -->
<!--   plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) +  -->
<!--   scale_colour_manual(values = cbPalette4) + -->
<!--    stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("retrospective 45s", "prospective 45s"), c("retrospective 90s", "prospective 90s")))  -->



<!-- # jpeg("violinrDEdurationParadigm", width = 5000, height = 3500, units = "px",res=600) -->
<!--    violinrDEdurationParadigm -->
<!-- # dev.off() -->
<!-- ``` -->




```{r}
# #PoTJ vs Relative Timing (Quantiles)
# likert_hi_lo <- Likert_quantile %>%
# 	mutate(midlow = Neutral / 2,
# 		midhigh = Neutral / 2) %>%
# 	dplyr::select(quantile, `Very Slow`, Slow, midlow, midhigh, Fast, `Very Fast`) %>%
# 	gather(key = response, value = perc, 2:7) 
# 	colnames <- (c("quantile", "response", "perc"))
# 
# 
# likert_lo <- likert_hi_lo %>%
# 	filter(response %in% c( "midlow", "Slow", "Very Slow")) %>%
# 	mutate(response = factor(response, levels = c("Very Slow", "Slow", "midlow")))
# 
# likert_hi <- likert_hi_lo %>%
# 	filter(response %in% c( "Very Fast", "Fast", "midhigh")) %>%
# 	mutate(response = factor(response, levels = c("Very Fast", "Fast", "midhigh")))
# 
# 
# legend_pal <- brewer.pal(name = "RdBu", n = 5)
# 
# legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])
# 
# legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)
# 
# names(legend_pal) <- c("Very Fast", "Fast","midhigh", "midlow", "Slow", "Very Slow" )
# 
# # jpeg("BarslikertRelativeTiming1ProS1.jpg", width = 4000, height = 2500, units = "px",res=600)
# ggplot() + 
# 	geom_bar(data = likert_hi, aes(x = quantile, y=perc, fill = response), stat="identity", width = 0.5) +
# 	geom_bar(data = likert_lo, aes(x = quantile, y=-perc, fill = response), stat="identity", width = 0.5) + 
# 	geom_hline(yintercept = 0, color =c("black")) + 
# 	scale_fill_manual(values = legend_pal, 
# 	                  name = "In the last round,\nthe time seemed \nto have passed:",
# 		breaks = c("Very Fast", "Fast", "midhigh", "Slow", "Very Slow" ),
# 		labels = c("Very Fast", "Fast","Neutral", "Slow", "Very Slow")) +
#   labs(x = "rDE", y ="Percentage of Respondants (%)", title = "Relative Duration Estimation vs Passage of Time Judgment") +
#   coord_flip() + 
#   scale_y_continuous(breaks = seq(from = -70, to = 75, 60),
#                      limits = c(-75,60)) +
# 	theme_classic()
# # dev.off()
```

<!-- ##Bias X PoTJ violin plot 2 -->
<!-- ```{r} -->

<!-- Nback_blocks <- Nback_blocks %>% -->
<!--   mutate(relative_timing = estimate / parse_number(as.character(duration)), -->
<!--          likert2 = ifelse(likert == "Very Slow" | likert == "Slow", "Slow", as.character(likert)), -->
<!--          likert2 = ifelse(likert == "Very Fast" | likert == "Fast", "Fast", as.character(likert2)), -->
<!--          likert2 = fct_relevel(likert2, c("Slow", "Neutral", "Fast"))) -->


<!-- my_xlab <- paste(levels(Nback_blocks$likert2),"\n(N=",table(Nback_blocks$likert2),")", sep="") -->
<!-- my_comparison = list( c("Slow", "Neutral"), c("Neutral", "Fast"), c("Slow", "Fast")) -->


<!-- violin_likert <- Nback_blocks %>%  -->
<!--   filter( !is.na(likert2)) %>% -->
<!--    ggplot(aes(y = relative_timing, x = likert2, fill = likert2)) +  -->
<!--   geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1) + -->
<!--   geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") + -->
<!--   geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) + -->
<!--   scale_x_discrete(labels = my_xlab) + -->
<!--   scale_y_continuous(breaks = seq(from = 0, to = 3, by = .5), -->
<!--                      limits = c(0, 3)) + -->
<!--   stat_summary(fun = mean)  + -->
<!--   scale_fill_viridis(discrete = TRUE, alpha=0.3, name = "In the last round,\nthe time seemed \nto have passed:", -->
<!-- 		labels = c("Slow", "Neutral", "Fast")) + -->
<!--    theme_classic() +   -->
<!--   labs(y = "Relative Timing", x ="PoTJ", title = "Relative Timing vs Passage of Time Judgment") +  -->
<!--   theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) + -->
<!--   theme( legend.text = element_text(size = 10), -->
<!--           axis.text = element_text(size = 11),  -->
<!--  axis.title = element_text(size = 12)) + -->
<!--  stat_compare_means(symnum.args = symnum, method = "wilcox.test", paired = FALSE, label = "p.format",  -->
<!--                     label.y = c(2.7,2.8,3), comparison = my_comparison) -->



<!-- # jpeg("ViolinLikertproS1", width = 3000, height = 2500, units = "px",res=600) -->
<!--  violin_likert -->
<!--   # dev.off() -->
<!-- ``` -->
