---
title: "S1 Global N-back analysis"
output: html_document
---

#packages
```{r, include= F}
library(tidyverse)
library(rmarkdown)
library(ggpubr)
library(viridis)
library(cowplot)
library(RColorBrewer)
library(R.utils)

library(lme4)
library(lmtest)
library(emmeans)
library(stargazer)

library(factoextra)
library(moments)
library(ordinal)
```

#functions
```{r, include= F}
## Standard Error of the Mean (SEM)
 #Don't forget 10 ms bruit gorilla
sem <- function(x, na.rm=FALSE) {
     if(na.rm==TRUE) x <- na.omit(x)
     sd(x)/sqrt(length(x)) 
}

##coefficent of variation
cv <- function(x){sd(x)/mean(x)}

#Z-score
z_score <- function(x){(x - mean(x)) / sd(x)}

## Outliers removal
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}

```

#palettes
```{r, include= F}
#Palettes of colours
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")

cbPalette2 <- c("#0072B2", "#CC79A7")

cbPalette2_v2 <- c("#66c2a4", "#fc8d59")

cbPalette4 <- c( "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7")

cbPalette5 <- c( "#CC79A7", "#009E73")
```

#Formatting duration estimations 
```{r}

#Extract processed data for session 1
file <- "/home/user/Desktop/Documents/TimeSocialDistancing/nback_TSD/S1global_nback.csv"

Nback = read.csv2(file, sep = ",")


# Each row is a participant response
#Defining if the letter is a target letter and if an answer is a hit, a correct reject, a miss or a false alarm. 
Nback_all <- Nback %>%           #134086 observations
   filter(!is.na(translated)) %>%
         mutate(PID = as.factor(PID),
         timing_error = as.numeric(as.character(translated)) - parse_number(as.character(duration)))
        


# Each row is a different trial
Nback_blocks <- Nback_all %>%    #3785 trials
  group_by(PID) %>%
  group_by(Run, .add = T) %>%
  group_by(nback, .add =T) %>%
  group_by(ILI, duration, block_nb, .add = T) %>%
  summarise(condition = first(condition),
            retro.pro = first(retro.pro),
            likert = first(likert),
            translated = first(translated),
            timing_error = first(timing_error),
            ntarget = first(ntarget),
            notarget = first(notarget),
            mRT = mean(as.numeric(as.character(Reaction.Time))),
            hit = sum(response_arrow == "Left" & Correct == T),
            miss  = sum(response_arrow == "Down" & Correct == F),
            fa = sum(response_arrow == "Left" & Correct == F),
            cr = sum(response_arrow == "Down" & Correct == T),
            HR = sum(response_arrow == "Left" & Correct == T)/ntarget,
            FA = sum(response_arrow == "Left" & Correct == F)/notarget,
            CR = sum(response_arrow == "Down" & Correct == T)/notarget,
            MR = sum(response_arrow == "Down" & Correct == F)/ntarget) %>%
  ungroup() 


 
# %Correct (perf) = Hit Rate + Correct rejection Rate / number of letters displayed during the trial
Nback_blocks <- Nback_blocks %>%
  mutate(likert = fct_relevel(likert, "Très lentement", "Lentement",  "Normalement", "Rapidement", "Très rapidement"),
  likert_n = as.factor(recode(likert, "Très lentement" = -2, "Lentement" = -1, "Normalement" = 0, "Rapidement" = 1, "Très rapidement" = 2))) 


Nback_blocks <- Nback_blocks %>%
  filter(HR < 1.2 & MR < 1.5) %>%
  mutate(HR = ifelse(HR > 1, 1, HR),
         FA = ifelse(FA > 1, 1, FA),
         CR = ifelse(CR > 1, 1, CR),
         HR = ifelse(HR == 0, 0.01, HR),
  HR = ifelse(HR == 1, 0.99, HR),
  FA = ifelse(FA == 0, 0.01, FA),
  FA = ifelse(FA == 1, 0.99, FA),
  dprime2 = qnorm(HR) - qnorm(FA))


paged_table(Nback_blocks) #15141



#STD indices

Nback_blocks <- Nback_blocks %>%
  mutate(dprime = psycho::dprime(
  n_hit = hit,
  n_fa = fa,
  n_miss = miss,
  n_cr = cr,
  n_targets = ntarget,
  n_distractors = notarget)$dprime)
  


```



#Remove prospective tasks (first trial of the first run for each participant)
```{r}
#What is the first design condition encountered by the subject ?
Nback_blocks %>%
  filter(retro.pro == "retrospective") %>%
  count(condition)

Nback_blocks %>%
  filter(retro.pro == "retrospective")
#1089 retrospective trials (1089 participants)


#keep only prospective trials
Nback_blocks <- Nback_blocks %>%
  filter(retro.pro == "retrospective")

#15141 --> 1089 trials

#222 3-back tasks and 867 1-back task
```




```{r}

#HR DISTRIBUTION


jpeg("DistributionHRS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 dev.off()

#FA DISTRIBUTION

jpeg("DistributionFAS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(500 * 0.02)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 dev.off()

#CR DISTRIBUTION


# jpeg("DistributionCRS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 # dev.off()



jpeg("DistributionD'S1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime2)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
  # scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
  #                limits = c(-0.01,1.01))
 dev.off()

```
#Outliers on d'
```{r}
perf_outliers <- Nback_blocks %>%
filter(dprime2 <= 0)
#192 outliers (121 1-back)

Nback_blocks <- Nback_blocks %>%
filter(dprime2 > 0)
```




```{r}

#HR DISTRIBUTION


# jpeg("DistributionHRS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 # dev.off()

#FA DISTRIBUTION

# jpeg("DistributionFAS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(500 * 0.02)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 # dev.off()

#CR DISTRIBUTION


# jpeg("DistributionCRS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                 limits = c(-0.01,1.01))
 # dev.off()



# jpeg("DistributionD'S1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
  # scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
  #                limits = c(-0.01,1.01))
 # dev.off()

```






## N-BACK PERFORMANCE (Correct Response Rate, False Alarm Rate, mRT)


#N-back Performance table and N-Back Performance Graphs for different WM load and Task duration
```{r}
perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, duration) %>%
  summarise(HR = mean(HR),
            mRT = mean(mRT),
            FA = mean(FA))

semHR <- aggregate(HR ~ nback + duration, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + duration, Nback_blocks, sem) #apply sem function 
semFA <- aggregate(FA ~ nback + duration, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)

# Correct response rate VS WM load and task duration
perf_HR = perfNback %>% ggplot (aes(x = nback,
                                              y = HR,
                                              group = duration,
                                              colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR),
                colour = "black",
                width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0.30, to = 0.80, by = 0.10),
limits = c(0.29, 0.80))

# False Alarm rate VS WM load and task duration
perf_FA = perfNback %>% ggplot (aes(x = nback,
                                              y = FA,
                                              group = duration,
                                              colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA),
                colour = "black",
                width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0, to = 0.20, by = 0.05),
limits = c(0, 0.22)) 

# mean Reaction Time VS WM load and task duration
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT,
              group = duration,
              colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11),
         legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
   legend.position = c(.8, .2))  +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT),
                colour = "black",
                width = .05)  +
  scale_y_continuous(breaks = seq(from = 560, to = 620, by = 20),
limits = c(560, 620)) +
  scale_colour_manual(values = cbPalette2, labels = c("45s", "90s"))


#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA + theme(legend.position = "none")
perf_mRT = perf_mRT 

title <- ggdraw() + draw_label(
    "Fig.1: N-back performance VS working memory load and task duration",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
    
# jpeg("PerfNbackDurationproS1.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1))  # rel_heights values control vertical title margins
# dev.off()
```




#N-back Performance table and N-Back Performance Graphs for different WM load and ILI (Inter-letter interval)
```{r}

perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, ILI) %>%
  summarise(HR = mean(HR),
            mRT = mean(mRT),
            FA = mean(FA))

semHR <- aggregate(HR ~ nback + ILI, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + ILI, Nback_blocks, sem)  #apply sem function 
semFA <- aggregate(FA ~ nback + ILI, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)


perf_HR = perfNback %>% ggplot (aes(x = nback,
                                              y = HR,
                                              group = ILI,
                                              colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR),
                colour = "black",
                width = .05) +
  scale_colour_manual(values = cbPalette2_v2) +
  scale_y_continuous(breaks = seq(from = 0.40, to = 0.80, by = 0.10),
limits = c(0.35, 0.80))


perf_FA = perfNback %>% ggplot (aes(x = nback,
                                              y = FA,
                                              group = ILI,
                                              colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA),
                colour = "black",
                width = .05) +
  scale_colour_manual(values = cbPalette2_v2)  +
  scale_y_continuous(breaks = seq(from = 0.05, to = 0.20, by = 0.05),
limits = c(0.05, 0.20)) 


# mean Reaction Time VS WM load and ILI
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT,
              group = ILI,
              colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11),
         legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
   legend.position = c(.8, .4))  +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT),
                colour = "black",
                width = .05) +
  scale_y_continuous(breaks = seq(from = 560, to = 660, by = 20),
limits = c(550, 660)) +
  scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms"))


#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA + theme(legend.position = "none")
perf_mRT = perf_mRT 

title <- ggdraw() + draw_label(
    "Fig.1: N-back performance VS working memory load and ILI",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
          
# jpeg("PerfNbackILIproS1.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1)) # rel_heights values control vertical title margins
# dev.off()
```

#Timing Error
```{r}

# jpeg("DistribTES1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(8000 * 1)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Timing Error", title ="Timing Error distribution for 45s/90s tasks (before outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 220, by = 30),
  limits = c(-90, 230))
# dev.off()
```




#Outliers removal on Timing Error
```{r}
#Outliers on d'

Nback_blocks <- Nback_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error))

estimation_outliers <- Nback_blocks %>%
filter(abs(ZTiming) > 2)    #37 outliers  (27 for 45s)
  
Nback_blocks %>%
  ggplot() + geom_histogram(mapping = aes(ZTiming))

Nback_blocks <-  Nback_blocks %>%        #897 -> 860 trials
  filter(abs(ZTiming) <= 2 )
```

#Timing Error
```{r}

# jpeg("DistribTE2S1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(5000 * 1)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Timing Error", title ="Timing Error distribution for 45s/90s tasks (after outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 90, by = 15),
  limits = c(-100, 100))
# dev.off()
```







# mean Reaction Time distribution for 1-back and 3-back 
```{r}
 mRT_1back <-  Nback_blocks %>%
  filter(nback == "1back") 
 mRT_3back <- Nback_blocks %>%
  filter(nback == "3back") 
 

# QQ plot
 title <- ggdraw() + 
   draw_label("Normal QQ plot of mean Reaction Time for 1-back and 3-back",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 0, 15 ,0))

plot_row = plot_grid(ggqqplot(mRT_1back$mRT, size = 0.2),
                     ggqqplot(mRT_3back$mRT, size = 0.2), 
                     nrow=1, labels=c('1-back', '3-back'),
  label_size = 11,
  hjust = -0.5, vjust = -0.5)
          
# jpeg("QQplotmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1))
# dev.off()

#shapiro-wilk test  H0 = normal
shapiro.test(mRT_1back$mRT)
shapiro.test(mRT_3back$mRT)


#the two distribution are skewed ! 


# jpeg("DistributionmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(mRT)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth= 30,
                   colour = "black" , fill="white") + 
      geom_density(aes(y = ..density..*(1800 * 30)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Hit Rate", title ="Mean Reaction Time Distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1300, by = 250),
                 limits = c(0,1300))
 # dev.off()



skewness(filter(
  Nback_blocks, nback == "1back")$mRT, na.rm = TRUE)   #positive asymetrie

skewness(filter(
  Nback_blocks, nback == "3back")$mRT, na.rm = TRUE)   #positive asymetrie


Nback_blocks$normRT <- log10(Nback_blocks$mRT)
mRT_1back$normRT <- log10(mRT_1back$mRT)
mRT_3back$normRT <- log10(mRT_3back$mRT)


skewness(filter(
  Nback_blocks, nback == "1back")$normRT, na.rm = TRUE)   #positive asymetrie

skewness(filter(
  Nback_blocks, nback == "3back")$normRT, na.rm = TRUE)   #negative asymetrie
#sqrt(x) pour les données asymétriques positives ?

# jpeg("DistributionmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(normRT)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth= 0.01,
                   colour = "black" , fill="white") + 
      geom_density(aes(y = ..density..), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Hit Rate", title ="Mean Reaction Time Distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
  # scale_x_continuous(breaks = seq(from = 0, to = 1300, by = 250),
  #                limits = c(0,1300))
 # dev.off()

shapiro.test(mRT_1back$normRT)
shapiro.test(mRT_3back$normRT)
```









##Subjective vs Objective Duration (with and without ILI)
```{r}
#Duration estimation tables 

durations <- Nback_blocks %>%
  group_by(nback) %>% 
  group_by(duration, .add = T) %>% 
  summarize(DD = mean(timing_error), semDD = sem(timing_error))

durations_by_ILI <- Nback_blocks%>%
  group_by(duration, .add = T) %>%   
  group_by(ILI, .add = T) %>%
  group_by(nback, .add = T) %>%
  summarize(DD = mean(timing_error), semDD = sem(timing_error))



#Subjective vs Objective Duration graph
DD_vs_OD_Nback = durations %>% ggplot (aes(x = duration,
                                              y = DD,
                                              group = nback,
                                              colour = nback)) +
scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = nback), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration (s)") +
  theme(legend.text = element_text(size = 11),
         legend.title  = element_text(size = 12),
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  legend.position = c(.90, .65),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD),
                colour = "black",
                width = .05) +
  scale_colour_manual(values = cbPalette, labels = c("1-back", "3-back"), name = "WM load")

#Subjective vs Objective Duration with ILI
DD_vs_OD_ILI = durations_by_ILI %>%
  ggplot (aes(x = duration,
                 y = DD,
                group = ILI,
                colour = ILI)) +
  scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration (s)") +
  theme( legend.text = element_text(size = 11),
         legend.title  = element_text(size = 12),
         axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  legend.position = c(.90, .7),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD),
                colour = "black",
                width = .05) +
 scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms")) +
  facet_grid(.~nback)


#Merge the two graphs
title <- ggdraw() + draw_label(
    "Subjective Duration Deviation VS Objective Duration for different conditions",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(DD_vs_OD_Nback + theme(plot.margin = margin(0, 30, 0, 0)),
  DD_vs_OD_ILI + theme(plot.margin = margin(0, 10, 0, 0)),  
  nrow=1, labels=c('A', 'B'),  rel_widths =  c(3, 5))
          
# jpeg("SD_ODproS1.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1))
# dev.off()


```


