---
title: "S1 Global N-back Retrospective analysis"
output: html_document
---

#DEF

##packages
```{r, include= F}
library(tidyverse)
library(rmarkdown)
library(ggpubr)
library(viridis)
library(cowplot)

library(lme4)
library(lmtest)
library(performance)
library(emmeans)

library(R.utils)
library(RColorBrewer)

library(factoextra)
library(moments)
library(ordinal)
library(sure)
```

##Functions
```{r, include= F}
## Standard Error of the Mean (SEM)
sem <- function(x, na.rm=FALSE) {
     if(na.rm==TRUE) x <- na.omit(x)
     sd(x)/sqrt(length(x)) 
}  #Don't forget 10 ms bruit gorilla  

##coefficent of variation
cv <- function(x){sd(x)/mean(x)}

#Z-score
z_score <- function(x){(x - mean(x)) / sd(x)}

## Outliers removal
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}

```

##Palettes
```{r, include= F}
#Palettes of colours
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")

cbPalette2 <- c("#0072B2", "#CC79A7")

cbPalette2_v2 <- c("#66c2a4", "#fc8d59")

cbPalette4 <- c( "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7")

cbPalette5 <- c( "#CC79A7", "#009E73")
```

#FORMATTING DATA AND OUTLIERS REMOVAL

##Formatting dataset
```{r}

#Extract processed data for session 1
file <- "/home/cyril/Documents/Cognition & Brain Dynamics/TimeSocialDistancing/nback_TSD/S1global_nback.csv"

Nback = read.csv2(file, sep = ",")


# Each row is a participant response
#Defining if the letter is a target letter and if an answer is a hit, a correct reject, a miss or a false alarm. 
Nback_all <- Nback %>%           #564579 observations
   filter(!is.na(translated)) %>%
         mutate(PID = as.factor(PID),
         estimate = as.numeric(as.character(translated)),
         relative_timing = estimate / parse_number(as.character(duration)),
         timing_error = estimate - parse_number(as.character(duration)),
         age = as.numeric(as.character(age)))
        


# Each row is a different trial
Nback_blocks <- Nback_all %>%    #3785 trials
  group_by(country) %>%
  group_by(PID, .add = T) %>%
  group_by(Run, .add = T) %>%
  group_by(nback, .add =T) %>%
  group_by(ILI, duration, block_nb, .add = T) %>%
  summarise(condition = first(condition),
            likert = first(likert),
            estimate = first(estimate),
            timing_error = first(timing_error),
            relative_timing = first(relative_timing),
            ntarget = first(ntarget),
            notarget = first(notarget),
            mRT = mean(as.numeric(as.character(Reaction.Time))),
            hit = sum(response_arrow == "Left" & Correct == T),
            miss  = sum(response_arrow == "Down" & Correct == F),
            fa = sum(response_arrow == "Left" & Correct == F),
            cr = sum(response_arrow == "Down" & Correct == T),
            HR = sum(response_arrow == "Left" & Correct == T)/ntarget,
            # HR1 = sum(response_arrow == "Left" & Correct == T)/(miss + hit),
            FA = sum(response_arrow == "Left" & Correct == F)/notarget,
            # FA1 = sum(response_arrow == "Left" & Correct == F)/(fa + cr),
            CR = sum(response_arrow == "Down" & Correct == T)/notarget,
            MR = sum(response_arrow == "Down" & Correct == F)/ntarget,
            handedness = first(handedness),
            age = first(age),
            sex = first(sex),
            timestamp = first(timestamp)) %>%
  ungroup() 


 
#translate PoTJ Likert Scale from different countries in English
veryquickly = c("muy rápido", "Très rapidement","Πολύ Γρήγορα","Very Fast","Molto veloce","Çok hızlı","とても速かった")
quickly = c("rápido", "Rapidement","Γρήγορα","Fast","Veloce","Hızlı","速かった")
normally = c("Normalement", "Κανονικά", "Neutral", "Neutrale", "普通", "Nötr", "normal")
slowly = c("lento","Lentement","Αργά","Slow","Very Slow","Lentamente","Yavaş", "遅かった") 
veryslowly = c("Muy lento", "Très lentement","Πολύ Αργά","Molto lentamente","Çok yavaş","とても遅かった")

Nback_blocks <- Nback_blocks %>%
  mutate(likert = ifelse(likert %in% veryquickly, "Very Quickly", as.character(likert)),
         likert = ifelse(likert %in% quickly, "Quickly", as.character(likert)),
         likert = ifelse(likert %in% normally, "Normally", as.character(likert)),
         likert = ifelse(likert %in% slowly, "Slowly", as.character(likert)),
         likert = ifelse(likert %in% veryslowly, "Very Slowly", as.character(likert))) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly"),
  likert_n = as.factor(recode(likert, "Very Slowly" = -2, "Slowly" = -1, "Normally" = 0, "Quickly" = 1, "Very Quickly" = 2))) 

#dprime computation and dealing with score >= 1 or =< 0
Nback_blocks <- Nback_blocks %>%
  filter(HR < 1.2 & MR < 1.5) %>%
  mutate(HR = ifelse(HR > 1, 1, HR),
         FA = ifelse(FA > 1, 1, FA),
         CR = ifelse(CR > 1, 1, CR),
         HR = ifelse(HR == 0, 0.01, HR),
  HR = ifelse(HR == 1, 0.99, HR),
  FA = ifelse(FA == 0, 0.01, FA),
  FA = ifelse(FA == 1, 0.99, FA),
  zHR = qnorm(HR),
  zFA = qnorm(FA),
  dprime = zHR - zFA,
  beta = exp(-zHR*zHR/2+zFA*zFA/2),
  logbeta = log(beta))


Nback_blocks <- Nback_blocks %>%
  dplyr::select(-ntarget, -notarget, - hit, -miss, -fa, -cr, -zHR, -zFA)



paged_table(Nback_blocks) #14893

```



##Identify retrospective and first prospective tasks
```{r}
Nback_blocks <- Nback_blocks %>%
  group_by(PID) %>%
  arrange(timestamp) %>%
  mutate(timestamp2 = as.character(timestamp)) %>%
  mutate(order = row_number()) 
  
pro1 = Nback_blocks %>%
  filter(order == 2)
retro = Nback_blocks %>%
  filter(order == 1)

var(retro$timing_error) #2526.881
var(pro1$timing_error) #2134.567



#Remove prospective tasks (first trial of the first run for each participant)
Nback_blocks = Nback_blocks %>%
  filter(order == 1)

#15141 --> 1097 trials


Nback_blocks %>%
  group_by(country, nback) %>%
  summarise(n = n())

#What is the first design condition encountered by the subject ? --> equally distributed
Nback_blocks %>%
  group_by(condition) %>%
  count()
```


##Retro VS 1stPro
```{r}
#Timing Error distrib - retrospective trials
ggretro <- retro %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distrib for 45s/90s retro tasks (before outliers removal)") + 
  theme_light() +
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 270, by = 30),
  limits = c(-90, 270))

#Timing Error distrib - prospective trials
ggpro <- pro1 %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(8000 * 1)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distrib for 45s/90s 1st pro tasks (before outliers removal)") + 
  theme_light() +
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 270, by = 30),
  limits = c(-90, 270))


plot_row = plot_grid(ggpro, ggretro, nrow=2, labels=c('A', 'B', 'C'))
    
# jpeg("DistribRetroPro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid( plot_row, ncol = 1, rel_heights = c(1, 1))
# dev.off()
  
  
SD_Var_retro <- retro %>% 
  group_by(nback) %>%
  group_by(duration, .add =T) %>%
  summarise(VarSD = var(estimate), 
            semSD = sd(estimate)/sqrt(n()))

SDvar_retro <- ggplot(data = SD_Var_retro,
             aes(x = nback, y = VarSD, group = duration,
                 fill = interaction(duration, nback))) +
  labs(x = "WM load", y = "Subjective duration variance (s²)", title = "retrospective tasks") +
  theme_classic() +
  theme(legend.title = element_text(size = 12), legend.text = element_text(size = 11),
        axis.title = element_text(size = 13), axis.text = element_text(size = 12),
        plot.title = element_text("hjust" = 0.5, size = 11)) +
  scale_fill_manual(values = cbPalette4, name = "Duration", labels = c("45s", "90s", "45s", "90s")) +
  geom_bar(stat = "identity", width = .7, position = "dodge", alpha = 0.5)
 

SD_Var_pro1 <- pro1 %>% 
  group_by(nback) %>%
  group_by(duration, .add =T) %>%
  summarise(VarSD = var(estimate), 
            semSD = sd(estimate)/sqrt(n()))

SDvar_pro1 <- ggplot(data = SD_Var_pro1,
             aes(x = nback,
                 y = VarSD,
                 group = duration,
                 fill = interaction(duration, nback))) +
  labs(x = "WM load", y = "Subjective duration variance (s²)", title = "1st prospective tasks") +
  theme_classic() +
  theme(legend.title = element_text(size = 12), legend.text = element_text(size = 11),
        axis.title = element_text(size = 13), axis.text = element_text(size = 12),
        plot.title = element_text("hjust" = 0.5, size = 11)) +
  scale_fill_manual(values = cbPalette4, name = "Duration", labels = c("45s", "90s", "45s", "90s")) +
  geom_bar(stat = "identity", width = .7, position = "dodge", alpha = 0.5) 

title <- ggdraw() + draw_label(
    "Subjective duration variance for the two first trials of each participant",
    fontface = 'bold', size = 13,) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(SDvar_retro, SDvar_pro1, nrow=1)
          
# jpeg("VarRetroPro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
```





##Signal detection theory - HR, CR, FA and d' distribution (before outliers removal)
```{r}

#HR DISTRIBUTION

# jpeg("DistributionHRretro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFAretro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRretro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'retro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```




##Performance Outliers - no discrimination (d' = 0) or inverse discrimination (d' <0)
```{r}

#Outliers on d'

perf_outliers <- Nback_blocks %>%
filter(dprime <= 0) #250 outliers (65 1-back)

Nback_blocks <- Nback_blocks %>%
filter(dprime > 0)     #1097 --> 847 obs


#HR DISTRIBUTION

# jpeg("DistributionHRretro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFAretro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRretro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'retro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```





##Outliers removal on Timing Error
```{r}
# jpeg("DistribTEretro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (before outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
# dev.off()


#Outliers on TE

Nback_blocks <- Nback_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- Nback_blocks %>%
filter(abs(ZTiming) > 2)    #30 outliers  (13 for 45s)

Nback_blocks <-  Nback_blocks %>%        #847 -> 817 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 


# jpeg("DistribTEretro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (after outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 90, by = 15),
  limits = c(-91, 91))
# dev.off()
```

##Demographics
```{r}
#sex ratio
Nback_blocks %>%
  group_by(sex) %>%
  summarise(n = n()) 

#handedness ratio
Nback_blocks %>%
  group_by(country, handedness) %>%
  summarise(n = n()) 

#Age (year + month)
Nback_blocks %>%
  filter(!is.na(age)) %>%
  summarise(mean = mean(as.numeric(as.character(age))), sd = sd(as.numeric(as.character(age))))


#Graph density ridge, age distribution for each country
# # jpeg("DistribAge2S1.jpg", width = 4000, height = 2500, units = "px",res=600)
# Nback_blocks %>%
#    filter(age > 18) %>%
#     filter(country != "Columbia") %>%
#   mutate(country = as.factor(country)) %>%
#   ggplot( aes(y= country, x= age,  fill= country)) +
#     geom_density_ridges(alpha=0.6) +
#     theme_ridges() +
#     theme(legend.position="none",
#       panel.spacing = unit(0.1, "lines"),
#       strip.text.x = element_text(size = 8),
#       axis.title.y = element_text("vjust" = 0.5),
#       axis.title.x = element_text("hjust" = 0.5)) +
#   labs(y = "Country", x = "Age", title ="Age distribution of participants for each country") +
#   scale_y_discrete(labels = c("France (278)", "Turkey (109)", "Argentina (106)", "Italy (101)", "Greece (93)",  "Japan (69)",  "India (37)",  "Canada (24)")) +
#   theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
#   scale_x_continuous(breaks = seq(from = 20, to = 75, by = 5))
# # dev.off()

  nb_subjects <- Nback_blocks %>%
  group_by(PID) %>%
  summarise(country = first(country)) %>%
  group_by(country) %>%
  summarise(numbersubjects = n())
nb_subjects
```


# N-BACK PERFORMANCE 2 (D', Bias, mRT)


##Linear Multiple Regression models on d', bias and mRT
```{r}
data <- Nback_blocks #817 obs


## Model for D'

Md1 <-lm(dprime ~ duration, data=data)

Md2 <-lm(dprime ~ duration + ILI, data=data)
lrtest(Md1, Md2)  #p > 0.05 n.s -> More complex model (Md2) not significantly better than Md1

Md3 <-lm(dprime ~ duration + nback, data=data)
lrtest(Md1, Md3) #p < 0.05 -> More complex model (Md3) significantly better than Md1

Md4 <- lm(dprime ~ duration * nback, data=data)
lrtest(Md3, Md4) #p > 0.05 n.s complex model (Md4) is not better

compare_performance(Md1, Md2, Md3, Md4) #Md3 -> best AIC

summary(Md1)
summary(Md2)
summary(Md3) #best model --> shows significative effects of duration and nback on d'
summary(Md4)


#Does Md3 meet assumptions ?

check_normality(Md3) #not OK, but graphically OK
check_heteroscedasticity(Md3) #not OK, but graphically OK
check_autocorrelation(Md3) #OK
check_collinearity(Md3) #OK
plot(Md3)




##Models for Bias (log(Beta))

MB1 <-lm(logbeta ~ duration, data=data)

MB2 <-lm(logbeta ~ duration + ILI, data=data)
lrtest(MB1, MB2)  #p < 0.05 -> More complex model (MB2) significantly better than MB1

MB3 <-lm(logbeta ~ duration + ILI + nback, data=data)
lrtest(MB2, MB3)  #p > 0.05 -> complex model (MB3) is not better

MB4 <-lm(logbeta ~ duration * nback + ILI, data=data)
lrtest(MB2, MB4)  #p < 0.05 -> More complex model (MB4) significantly better than MB2

MB5 <-lm(logbeta ~ duration * nback * ILI, data=data)
lrtest(MB4, MB5)  #p > 0.05 -> complex model (MB5) is not better


compare_performance(MB1, MB2, MB3, MB4, MB5) #MB4 -> best AIC

summary(MB1)
summary(MB2)
summary(MB3)
summary(MB4)  #best model --> shows significative effects of ILI, duration, nback and duration:nback on Bias
summary(MB5)

#Does MB4 meet assumptions ?

check_heteroscedasticity(MB4) #not OK, but graphically OK:
plot(MB4)

check_autocorrelation(MB4) #OK
check_collinearity(MB4)  #OK

check_normality(MB4) #not OK, but graphically OK:
R1 <- resid(MB4) #residuals
hist(R1, breaks = 30)




## Models for mRT

MRT1 <- lm(mRT ~ duration, data = data)

MRT2 <- lm(mRT ~ duration + ILI, data = data)
lrtest(MRT1, MRT2)

MRT3 <- lm(mRT ~ duration + ILI +  nback, data = data)
lrtest(MRT2, MRT3) #n.s

MRT4 <- lm(mRT ~ duration * ILI, data = data)
lrtest(MRT2, MRT4) #n.s

MRT5 <- lm(mRT ~ duration * nback + ILI, data = data)
lrtest(MRT2, MRT5) #n.s

compare_performance(MRT1, MRT2, MRT3, MRT4) #MRT2 -> best AIC

summary(MRT1)
summary(MRT2) #best model --> shows significative effects of duration and ILI on mean Reaction Time
summary(MRT3)
summary(MRT4)

#Does MRT2 meet assumptions ?

check_normality(MRT2) #not OK, but graphically OK:
check_heteroscedasticity(MRT2) #not OK, but graphically OK:
plot(MRT2)

check_autocorrelation(MRT2) #OK
check_collinearity(MRT2) #OK




#compute emmeans
# emmeans(MB4, pairwise ~ nback | duration)
# emmeans(MB4, pairwise ~ nback)
# emmeans(MB4, "nback")
# summary(MB4)
# 
# emmeans(MB4, pairwise ~ nback)




```




##mRT violin plot
```{r}
mRTILI <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = ILI, colour = ILI)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "mRT (ms)", x ="ILI") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1400, comparison = list(c("1500ms", "1800ms")))


mRTDuration <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = duration, colour = duration)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "mRT (ms)", x ="Task Duration") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), axis.title = element_text(size = 12)) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  scale_colour_manual(values = cbPalette2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1390, comparison = list(c("45s", "90s")))


title <- ggdraw() + draw_label("mRT for different ILI and Task Duration", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(mRTILI, mRTDuration, nrow=1)
          
# jpeg("mRTViolinRetro.jpg", width = 3000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
```

##D' violin plot
```{r}

violindnback <- Nback_blocks %>% 
  ggplot(aes(nback, dprime, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "WM Load", title = "WM Load x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violindduration <- Nback_blocks %>% 
  ggplot(aes(duration, dprime, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "Task Duration", title = "Duration x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))


#Merge the two graphs
title <- ggdraw() + draw_label("D' distribution vs Task Duration and WM Load",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violindnback + theme(plot.margin = margin(0, 30, 0, 0)),
  violindduration + theme(plot.margin = margin(0, 10, 0, 0)), nrow=1)
          
# jpeg("ViolinD'retro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()

```

##Bias violin plot
```{r}

violinBiasnback <- Nback_blocks %>% 
  ggplot(aes(nback, logbeta, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load", title = "WM Load x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violinBiasduration <- Nback_blocks %>% 
  ggplot(aes(duration, logbeta, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "Task Duration", title = "Duration x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))


violinBiasILI <- Nback_blocks %>% 
  ggplot(aes(ILI, logbeta, colour = ILI)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "ILI", title = "ILI x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("Bias distribution vs Task Duration, ILI and WM Load", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violinBiasnback, violinBiasduration, violinBiasILI, nrow=1)
          
# jpeg("ViolinBiasretro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
  
  
#INTERATIONS
  violinBiasdurationnback <- Nback_blocks %>% 
    mutate(nbackduration = paste(nback, duration),
           nbackduration =  fct_relevel(nbackduration, "1back 45s", "3back 45s", "1back 90s", "3back 90s")) %>%
  ggplot(aes(nbackduration, logbeta, colour = nbackduration)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load : Task Duration", title = "Bias for different WM Load and Task Duration") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) 
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back45s","3back45S"), c("1back90s","3back90S")))

# jpeg("violinBiasretrointeraction.jpg", width = 3000, height = 2500, units = "px",res=600)
  violinBiasdurationnback
# dev.off()
```



#DURATION JUDGMENTS - RELATIVE TIMING MODELS

## Linear models Effects of duration, D' and bias on Relative Timing (Why not using the relative timing ?)
```{r}
data <- Nback_blocks 


M1 <-lm(relative_timing ~ dprime, data=data)

M2 <-lm(relative_timing ~ logbeta + dprime, data=data)
lrtest(M1, M2)  #n.s p > 0.05  M1 better than M2

M3 <-lm(relative_timing ~ dprime + ILI, data=data)
lrtest(M1, M3) #n.s p > 0.05  M1 better than M3

M4 <-lm(relative_timing ~ dprime + nback, data=data)
lrtest(M1, M4) #n.s p > 0.05  M1 better than M4

M5 <-lm(relative_timing ~ dprime + duration, data=data)
lrtest(M1, M5) #n.s p > 0.05  M1 better than M5

M6 <-lm(relative_timing ~ dprime + duration + logbeta, data=data)
lrtest(M1, M6) #n.s p > 0.05  M1 better than M6

M7 <-lm(relative_timing ~ logbeta + duration * dprime, data=data)
lrtest(M1, M7) #n.s p > 0.05  M1 better than M7

M8 <-lm(relative_timing ~ logbeta * duration + dprime, data=data)
lrtest(M1, M8) #n.s p = 0.14

M9 <-lm(relative_timing ~ logbeta * duration * dprime, data=data)
lrtest(M1, M9)  #n.s p = 0.11


compare_performance(M1, M2, M3, M4, M5, M6, M7, M8, M9) # ~equivalent AIC for every model, but better R2 for M8 and M9


summary(M1)
summary(M2)
summary(M3)
summary(M4)
summary(M5)
summary(M6)
summary(M7)
summary(M8)
summary(M9)

#we verify model assumptions for M8 and M9

summary(M9)
check_heteroscedasticity(M9) #not ok 
check_autocorrelation(M9) #OK
check_collinearity(M9) #NOT OK --> High correlation !!


summary(M8)
check_heteroscedasticity(M8) #not ok with check, but ok graphically with plot()
check_autocorrelation(M8) #OK
check_collinearity(M8) #OK (only low correlation) residuals are independent and not auto-correlated

#we choose M8 model

summary(M8)
anova(M8)


# Verification of model assumptions ####

plot(M8)

R1 <- resid(M8) #residuals
F1 <- fitted(M8) #fitted values


## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)
check_normality(M8) #non-normality --> to resolve


## independance : residuals vs each model covariable

# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

#D' 
predictions <- summary(emmeans(M8, ~ duration * logbeta + dprime, at = list(dprime = seq(0,5, by = 0.1))))

# jpeg("model", width = 4000, height = 2500, units = "px",res=600)
ggplot(data, aes(dprime, relative_timing)) +
geom_point(size = 0.7) +
  theme_classic() +
geom_point(predictions, mapping = aes(y= emmean, colour = duration)) +
  labs(y = "Timing Error (s)", x = "d'")
# dev.off()


#Bias
predictions <- summary(emmeans(M8, ~ duration * logbeta + dprime, at = list(logbeta = seq(-3,3, by = 0.1))))

# jpeg("model", width = 4000, height = 2500, units = "px",res=600)
ggplot(data, aes(y = relative_timing, x =logbeta)) +
geom_point(size = 0.7) +
  theme_classic() +
geom_point(predictions, mapping = aes(y= emmean, colour = duration)) +
  labs(y = "Relative timing", x = "log(β)")
# dev.off()


#determine emmeans
emmeans(M8, "dprime", at = list(dprime = c(1, 2, 3, 4)))
emmeans(M8, ~ duration | logbeta, at = list(logbeta = c(-1, 0, 1)))
```


##D' effect on Relative Timing - Visualization
```{r}
# jpeg("d'pointretro.jpg", width = 2500, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime, relative_timing)) +
  geom_point(size = 0.5) +
  geom_smooth(method=lm, fill="#69b3a2", se= T) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .3, linetype = "dashed") +
  theme_classic() +
   labs(y = "Relative Timing (s)", x = "d'", title = "Relative Timing vs D'") +
  theme(axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) 
# dev.off()
```


##Bias effect on Relative Timing - Visualization
```{r}
#Log(beta) distribution


# jpeg("logbetadistribretro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(logbeta)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
  labs(y = "count", x = "log(β)", title ="log(β) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

# jpeg("logbetadistribretro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(logbeta)) + 
  facet_grid(nback~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02,
                   colour = "black" , fill="white") + 
  labs(y = "count", x = "log(β)", title ="log(β) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()


#Bias effect on Relative Timing

# jpeg("Biaspointretro.jpg", width = 2800, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(logbeta, relative_timing, colour = duration)) +
  geom_point(size = 0.5) +
  geom_smooth(method=lm, fill="#69b3a2", se= T) +
    geom_hline(aes(yintercept = 1), colour = 'black', size = .3, linetype = "dashed") +
  theme_classic() +
   labs(y = "Relative Timing (s)", x = "Bias", title = "Relative Timing vs Bias") +
  theme(axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
        legend.position = c(.1, .8),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) 
# dev.off()
```









#PASSAGE OF TIME JUDGMENT (PoTJ)


##PoTJ tables - % respondant for each likert answer
```{r}
Likert_nback <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(nback, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(nback) %>%
	spread(likert, perc) %>% 
  rename(design = nback)
   
Likert_ILI <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(ILI, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(ILI) %>%
	spread(likert, perc) %>% 
  rename(design = ILI) %>% 
  mutate(design = fct_recode(design, "1500ms" = "1500", "1800ms" = "1800"))

Likert_duration <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(duration, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(duration) %>%
	spread(likert, perc) %>% 
  rename(design = duration) %>%
  mutate(design = fct_recode(design, "45s" = "45", "90s" = "90"))
   

Likert_all <- bind_rows(Likert_ILI, Likert_nback, Likert_duration)
  
paged_table(Likert_all)  
```





##PoTJ VS ILI, WM Load & Duration (design paramaters) - All together
```{r}
#PoTJ vs ALL
likert_hi_lo <- Likert_all %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(design, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("duration", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))


# Use RColorBrewer to store a preset diverging colour palette as a vector of colour codes 
legend_pal <- brewer.pal(name = "RdBu", n = 5)

# Duplicate the middle value, remember that "Sometimes" is actually two groups, "midhigh" and "midlow"
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

# Replace the ugly white colour for "Sometimes" with a pleasant dishwater grey
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

# jpeg("divergingBarLikertretro1.jpg", width = 5000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
	coord_flip() + 
	labs(x = "        ILI                  WM Load                  Duration ", y = "Percentage of respondents (%)", title = "Diverging stacked bar of likert scale PoTJ for different durations") +
  scale_y_continuous(breaks = seq(from = -40, to = 75, 10),
                     limits = c(-45,80)) +
	theme_classic()
# dev.off()
```



##Passing of time statistic ordinal regression model
```{r}

#no effect of d'
#effect of ILI, duration and nback + interaction Bias / nback

data = Nback_blocks %>%
  filter(!is.na(likert_n))

library(MASS)

m1 = polr(likert ~ duration, data, Hess=T)

m2 = polr(likert ~ duration + ILI, data, Hess=T)
lrtest(m1,m2)  # p < 0.05 m2 is better than m1 (likelihood ratio test)

m3 = polr(likert ~ duration + ILI + nback, data, Hess=T)
lrtest(m2,m3)  # p < 0.05 m3 is better than m2

m4 = polr(likert ~ duration + ILI + nback + dprime, data, Hess=T)
lrtest(m3,m4)  # n.s m4 is not better than m4

m5 = polr(likert ~ duration + ILI + nback + logbeta, data, Hess=T)
lrtest(m3,m5)   # n.s m4 is not better than m5

m6 = polr(likert ~ duration * nback * ILI , data, Hess=T)
lrtest(m3,m6)  # n.s m4 is not better than m6

m7 = polr(likert ~ duration *dprime + nback + ILI , data, Hess=T)
lrtest(m3,m7) # n.s m4 is not better than m7

m8 = polr(likert ~ duration + dprime * nback + ILI, data, Hess=T)
lrtest(m3,m8) # n.s m4 is not better than m8

m9 = polr(likert ~ duration + nback + ILI * dprime , data, Hess=T)
lrtest(m3,m9) # n.s m4 is not better than m9

m10 = polr(likert ~ duration * nback * ILI * dprime , data, Hess=T)
lrtest(m3,m10) # n.s m4 is not better than m10

m11 = polr(likert ~ duration + nback + ILI * logbeta, data, Hess=T)
lrtest(m3,m11) # n.s  m4 is not better than m11

m12 = polr(likert ~ duration * logbeta + nback + ILI , data, Hess=T)
lrtest(m3,m12) # n.s  m4 is not better than m12

m13 = polr(likert ~ duration + logbeta * nback + ILI , data, Hess=T)
lrtest(m3,m13) # p < 0.05 More complex model (M13) better than M3

m14 = polr(likert ~ duration + logbeta * nback * ILI , data, Hess=T)
lrtest(m13,m14) # n.s  m14 is not better than m13

m15 = polr(likert ~ duration * logbeta * nback * ILI , data, Hess=T)
lrtest(m13,m15) # n.s  m15 is not better than m13


compare_performance(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15) #m11, m13, m14 --> best AIC

summary(m1)
summary(m2)
summary(m3)
summary(m13)
summary(m14)
#we choose m13

summary(m13)
coeffs <- coef(summary(m13))
p <- pnorm(abs(coeffs[, "t value"]), lower.tail = FALSE) * 2
cbind(coeffs, "p value" = round(p,3)) #get the p-value for each effect

exp(cbind(OR = coef(m13), ci = confint(m13))) #logit effects are difficult to interpret --> exp() to have % change
```

#Ordinal regression assumptions
```{r}
# sres <- resids(m13)
# autoplot(sres)
# 
# ##covariate : heteroscedasticity
# ggplot2::autoplot(m13, what = "covariate", x = data$duration)
# autoplot(sres, what = "covariate", x = data$nback)
# autoplot(sres, what = "covariate", x = data$ILI)
# autoplot(sres, what = "covariate", x = data$logbeta)
# 
# 
# #QQ plot : normality
# autoplot(sres, what = "qq", distribution = qnorm)
# ggplot2::autoplot(m1, output = "covariate", distribution = qnorm, data)

#collinearity
check_collinearity(m13)

##Proportional odds assumption
require(Hmisc)

sf <- function(y) {
  c(
    'Y>=1' = qlogis(mean(y >= 1)),
    'Y>= 2' = qlogis(mean(y >= 2)),
    'Y>= 3' = qlogis(mean(y >= 3)),
    'Y>= 4' = qlogis(mean(y >= 4)),
    'Y>=5' = qlogis(mean(y >= 5)))
}

s <- with(data, summary(as.numeric(likert) ~ duration + ILI + nback + nback:logbeta, fun=sf))
s

s[, 6] <- s[, 6] - s[, 3]
s[, 5] <- s[, 5] - s[, 3]
s[, 4] <- s[, 4] - s[, 3]
s[, 3] <- s[, 3] - s[, 3]
s

plot(s, which=1:5, pch=1:5, xlab='logit', main=' ', xlim=range(s[,3:6]))

```




## Bias X PoTJ - violin plot (3-back ! --> interaction Bias x WM Load)
```{r}

data <- Nback_blocks %>% 
  filter( !is.na(likert)) %>%
  filter(nback == "3back") 

my_xlab <- paste(levels(data$likert),"\n(N=",table(data$likert),")", sep="")
my_comparison = list( c("Very Slowly", "Normally"), c("Normally", "Very Quickly"), c("Very Slowly", "Very Quickly"))

# jpeg("BiasxPoTJviolin.jpg", width = 3000, height = 2500, units = "px",res=600)
data%>%
   ggplot(aes(y = logbeta, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  stat_summary(fun = mean)  +
  scale_fill_viridis(discrete = TRUE, alpha=0.3, name = "In the last round,\nthe time seemed \nto have passed:",
		labels = c("Very slowly", "Slowly", "Normally", "Quickly","Very quickly"  )) +
   theme_classic() +  
  labs(y = "Bias", x ="PoTJ", title = "Bias vs Passage of Time Judgment for 3-back tasks") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 10),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = c(2.7,2.75,3.1), comparison = my_comparison) + theme(legend.position = "none")
# dev.off()



```








#Ordinal Regression Model - Does Relative Timing a good predictor of PoTJ
```{r}

#effect of Relative Timing on PoTJ likert scale

data = Nback_blocks %>%
  filter(!is.na(likert_n))

library(MASS)

m1 = polr(likert ~ relative_timing, data, Hess=T)

summary(m1)

coeffs <- coef(summary(m1))
p <- pnorm(abs(coeffs[, "t value"]), lower.tail = FALSE) * 2
cbind(coeffs, "p value" = round(p,3)) #get the p-value for each effect
exp(cbind(OR = coef(m1), ci = confint(m1))) #logit effects are difficult to interpret --> exp() to have % change

# newdat <- data.frame(nback =c(,1))
# (phat <- predict(object = m, newdat, type="p"))




##Proportional odds assumption
require(Hmisc)

sf <- function(y) {
  c(
    'Y>=1' = qlogis(mean(y >= 1)),
    'Y>= 2' = qlogis(mean(y >= 2)),
    'Y>= 3' = qlogis(mean(y >= 3)),
    'Y>= 4' = qlogis(mean(y >= 4)),
    'Y>=5' = qlogis(mean(y >= 5)))
}

s <- with(data, summary(as.numeric(likert) ~ relative_timing, fun=sf))
s

s[, 6] <- s[, 6] - s[, 3]
s[, 5] <- s[, 5] - s[, 3]
s[, 4] <- s[, 4] - s[, 3]
s[, 3] <- s[, 3] - s[, 3]
s

plot(s, which=1:5, pch=1:5, xlab='logit', main=' ', xlim=range(s[,3:6]))
```












##Relative Timing X PoTJ violin plot
```{r}
my_xlab <- paste(levels(Nback_blocks$likert),"\n(N=",table(Nback_blocks$likert),")", sep="")
my_comparison = list( c("Very Slowly", "Normally"), c("Normally", "Very Quickly"), c("Very Slowly", "Very Quickly"))

# jpeg("PoTJDJretro", width = 3000, height = 2500, units = "px",res=600)
Nback_blocks %>% 
  filter( !is.na(likert)) %>%
   ggplot(aes(y = relative_timing, x = likert, fill = likert)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  scale_y_continuous(breaks = seq(from = 0, to = 3, by = .5),
                     limits = c(0, 3)) +
  stat_summary(fun = mean)  +
  scale_fill_viridis(discrete = TRUE, alpha=0.3, name = "In the last round,\nthe time seemed \nto have passed:",
		labels = c("Very slowly", "Slowly", "Normally", "Quickly","Very quickly"  )) +
   theme_classic() +  
  labs(y = "Relative Timing", x ="PoTJ", title = "Relative Timing vs Passage of Time Judgment") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 10),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12),
 legend.position ="None") +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = c(2.7,2.8,3), comparison = my_comparison)
# dev.off()
```


#Break Relative timing in tertiles or quantiles
```{r}

Nback_blocks <- data %>%
  mutate(quantile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/5))), include.lowest=TRUE),
  quantile = ifelse(quantile == "[0,0.444]", "1st     \n [0, 0.444]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.444,0.667]", "2nd     \n (0.444, 0.667]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.667,0.778]", "3rd     \n (0.667, 0.778]", as.character(quantile)),
  quantile = ifelse(quantile == "(0.778,1.33]", "4th     \n (0.778, 1.33]", as.character(quantile)),
  quantile = ifelse(quantile == "(1.33,2.67]", "5th     \n (1.33, 2.67]", as.character(quantile)),     
  tertile = cut(relative_timing, breaks = unique(quantile(relative_timing,
                                        probs=seq.int(0,1, by=1/3))), include.lowest=TRUE),
  tertile = ifelse(tertile == "[0,0.667]", "1st     \n [0, 0.667]", as.character(tertile)),
  tertile = ifelse(tertile == "(0.667,1]", "2nd     \n (0.667, 1]", as.character(tertile)),
  tertile = ifelse(tertile == "(1,2.67]", "3rd     \n (1, 2.67]", as.character(tertile)))
  
  summary(Nback_blocks)

Likert_quantile <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(quantile, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(quantile) %>%
	spread(likert, perc) 

Likert_quantile

Likert_tertile <- Nback_blocks %>%
   filter(!is.na(likert)) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(tertile, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(tertile) %>%
	spread(likert, perc) 

Likert_tertile
```



##PoTJ X Relative Timing - Diverging stacked bar 
```{r}
#PoTJ vs Relative Timing (Quantiles)
likert_hi_lo <- Likert_quantile %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(quantile, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("quantile", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))


legend_pal <- brewer.pal(name = "RdBu", n = 5)

legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

# jpeg("BarslikertRelativeTiming1.jpg", width = 4000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x = quantile, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = quantile, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
  labs(x = "Relative Timing", y ="Percentage of Respondants (%)", title = "Relative Timing vs Passage of Time Judgment") +
  coord_flip() + 
  scale_y_continuous(breaks = seq(from = -40, to = 75, 10),
                     limits = c(-45,80)) +
	theme_classic()
# dev.off()




#PoTJ vs Relative Timing (tertiles)
likert_hi_lo <- Likert_tertile %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(tertile, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("tertile", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))


legend_pal <- brewer.pal(name = "RdBu", n = 5)

legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

# jpeg("BarslikertRelativeTiming2.jpg", width = 4000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x = tertile, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = tertile, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
  labs(x = "Relative Timing", y ="Percentage of Respondants (%)", title = "Relative Timing vs Passage of Time Judgment") + 
	coord_flip() + 
  scale_y_continuous(breaks = seq(from = -40, to = 75, 10),
                     limits = c(-45,80)) +
	theme_classic()
# dev.off()
```




##PoTJ vs Relative Timing - Heatmap
```{r}

#Quantiles

nPoTJ <- Nback_blocks %>%
  filter(!is.na(likert)) %>%
  group_by(likert) %>%
  summarise(nPoTJ = n())

nPoTJxQ <- Nback_blocks %>%
  group_by(likert, quantile) %>%
  tally() 

Heatquantile <- left_join(nPoTJxQ, nPoTJ, by = c("likert")) %>%
  group_by(likert, quantile) %>%
  summarise(percentage = n/nPoTJ)

# Heatmap 
# jpeg("HeatmapPoTJxRT1.jpg", width = 4000, height = 2500, units = "px",res=600)
ggplot(Heatquantile, aes(likert, quantile, fill= percentage)) + 
  geom_tile()
# dev.off()




#Tertile

nPoTJ <- Nback_blocks %>%
  filter(!is.na(likert)) %>%
  group_by(likert) %>%
  summarise(nPoTJ = n())

nPoTJxQ <- Nback_blocks %>%
  group_by(likert, tertile) %>%
  tally() 

Heatquantile <- left_join(nPoTJxQ, nPoTJ, by = c("likert")) %>%
  group_by(likert, tertile) %>%
  summarise(percentage = n/nPoTJ)

# Heatmap 
# jpeg("HeatmapPoTJxRT2.jpg", width = 4000, height = 2500, units = "px",res=600)
ggplot(Heatquantile, aes(likert, tertile, fill= percentage)) + 
  geom_tile()
# dev.off()

```
















#SUPPLEMENTARY CHUNKS





#N-BACK PERFORMANCE 1 (HR, FA, mRT)


##N-back Performance table and N-Back Performance Graphs for different WM load and Task duration
```{r}
perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, duration) %>%
  summarise(HR = mean(HR), mRT = mean(mRT), FA = mean(FA))

semHR <- aggregate(HR ~ nback + duration, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + duration, Nback_blocks, sem) #apply sem function 
semFA <- aggregate(FA ~ nback + duration, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)

# Hit Rate VS WM load and task duration
perf_HR = perfNback %>% ggplot (aes(x = nback, y = HR, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0.30, to = 0.90, by = 0.10), limits = c(0.29, 0.90))


# False Alarm rate VS WM load and task duration
perf_FA = perfNback %>% ggplot (aes(x = nback, y = FA, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
    legend.position = c(.7, .15))  +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0, to = 0.25, by = 0.05), limits = c(0, 0.25))


# mean Reaction Time VS WM load and task duration
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11), legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
   legend.position = c(.8, .2))  +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT), colour = "black", width = .05)  +
    scale_colour_manual(values = cbPalette2, labels = c("45s", "90s")) +
  scale_y_continuous(breaks = seq(from = 560, to = 640, by = 20), limits = c(560, 640)) 



#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA 
perf_mRT = perf_mRT + theme(legend.position = "none")

title <- ggdraw() + draw_label("N-back performance VS working memory load and task duration",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
    
# jpeg("PerfNbackDurationretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))  
# dev.off()
```




##N-back Performance table and N-Back Performance Graphs for different WM load and ILI (Inter-letter interval)
```{r}

perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, ILI) %>%
  summarise(HR = mean(HR), mRT = mean(mRT), FA = mean(FA))

semHR <- aggregate(HR ~ nback + ILI, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + ILI, Nback_blocks, sem)  #apply sem function 
semFA <- aggregate(FA ~ nback + ILI, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)


perf_HR = perfNback %>% ggplot (aes(x = nback, y = HR, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2_v2) +
  scale_y_continuous(breaks = seq(from = 0.40, to = 0.90, by = 0.10), limits = c(0.35, 0.90))


perf_FA = perfNback %>% ggplot (aes(x = nback, y = FA, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 10),
          axis.text = element_text(size = 10),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
  legend.position = c(.72, .15)) +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2_v2)  +
  scale_y_continuous(breaks = seq(from = 0.05, to = 0.20, by = 0.05), limits = c(0.05, 0.23)) 


# mean Reaction Time VS WM load and ILI
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11), legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT), colour = "black", width = .05) +
  scale_y_continuous(breaks = seq(from = 560, to = 660, by = 20), limits = c(550, 660)) +
  scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms"))


#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA 
perf_mRT = perf_mRT + theme(legend.position = "none")

title <- ggdraw() + draw_label(
    "N-back performance VS working memory load and ILI",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
          
# jpeg("PerfNbackILIretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1)) 
# dev.off()
  
  
```


#Subjective vs Objective Duration (with and without ILI)
```{r}
#Duration estimation tables 

durations <- Nback_blocks %>%
  group_by(nback) %>% 
  group_by(duration, .add = T) %>% 
  summarize(DD = mean(timing_error), semDD = sem(timing_error))

durations_by_ILI <- Nback_blocks%>%
  group_by(duration, .add = T) %>%   
  group_by(ILI, .add = T) %>%
  group_by(nback, .add = T) %>%
  summarize(DD = mean(timing_error), semDD = sem(timing_error))


#Subjective vs Objective Duration graph
DD_vs_OD_Nback = durations %>% ggplot (aes(x = duration,y = DD, group = nback, colour = nback)) +
scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = .5, linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = nback), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration") +
  theme(legend.text = element_text(size = 11), legend.title  = element_text(size = 12), axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12), axis.text = element_text(size = 12),
  legend.position = c(.90, .65),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette, labels = c("1-back", "3-back"), name = "WM load")

#Subjective vs Objective Duration with ILI
DD_vs_OD_ILI = durations_by_ILI %>%
  ggplot (aes(x = duration, y = DD, group = ILI, colour = ILI)) +
  scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0),  colour = 'black',size = .5, linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration") +
  theme(legend.text = element_text(size = 11), legend.title  = element_text(size = 12), axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12), axis.text = element_text(size = 12),
  legend.position = c(.50, .6),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD), colour = "black", width = .05) +
 scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms")) +
  facet_grid(.~nback)


#Merge the two graphs
title <- ggdraw() + draw_label("Subjective Duration Deviation VS Objective Duration for different conditions",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(DD_vs_OD_Nback + theme(plot.margin = margin(0, 30, 0, 0)),
  DD_vs_OD_ILI + theme(plot.margin = margin(0, 10, 0, 0)),  
  nrow=1, labels=c('A', 'B'),  rel_widths =  c(3, 5))
          
# jpeg("SD_ODretro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()


```





#Coefficient of variation and Variance
```{r}
#Variance
SD_Var <- Nback_blocks %>% 
  group_by(nback) %>%
  group_by(duration, .add =T) %>%
  summarise(VarSD = var(estimate), 
            semSD = sd(estimate)/sqrt(n()))

SDvar_duration_nback <- ggplot(data = SD_Var,
             aes(x = nback,
                 y = VarSD,
                 group = duration,
                 fill = interaction(duration, nback))) +
  labs(x = "WM load", y = "Subjective duration variance (s²)") +
  theme_classic() +
  theme(legend.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 12),
        plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_fill_manual(values = cbPalette4, name = "Duration",
  labels = c("45s", "90s", "45s", "90s")) +
  geom_bar(stat = "identity", width = .7, position = "dodge", alpha = 0.5) 

#Coefficient of Variation
CVtime <- Nback_blocks %>%
  group_by(duration, .add =T) %>% 
  summarise(CV = sd(estimate)/mean(estimate), semCV = sem(estimate)/100)

CV_WM_duration <- CVtime %>%  
  ggplot (aes(x = duration, y = CV)) +
  geom_point(size = 2) +
  geom_line(aes(x = duration, y = CV), size = 1) +
  theme_classic() +
    labs(y = "estimation CV", x = "Task Duration") +
  theme(legend.title = element_text(size = 10), 
    legend.text = element_text(size = 9),
          axis.text = element_text(size = 12),
  legend.position = c(.8, .8),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = CV - semCV, ymax = CV + semCV),
                width = .05,
                color = "black") 


title <- ggdraw() + draw_label("Subjective duration variance and CV vs Task Dr((uration",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(SDvar_duration_nback, CV_WM_duration, nrow=1, labels=c('A', 'B'), rel_widths =  c(2, 1.4))
          
# jpeg("CV_Varianceretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
```


# Linear models Effects of duration, D' and bias on Timing Error
```{r}
data <- Nback_blocks 


M1 <-lm(timing_error ~ dprime, data=data)

M2 <-lm(timing_error ~ logbeta + dprime, data=data)
lrtest(M1, M2)  #n.s

M3 <-lm(timing_error ~ dprime + ILI, data=data)
lrtest(M1, M3) #n.s

M4 <-lm(timing_error ~ dprime + nback, data=data)
lrtest(M1, M4) #n.s

M5 <-lm(timing_error ~ dprime + duration, data=data)
lrtest(M1, M5) #p < 0.05

M6 <-lm(timing_error ~ dprime * duration, data=data)
lrtest(M5, M6) #n.s

M7 <-lm(timing_error ~ logbeta + duration + dprime, data=data)
lrtest(M5, M7) #n.s

M8 <-lm(timing_error ~ logbeta * duration + dprime, data=data)
lrtest(M5, M8) #p =~ 0.05 

M9 <-lm(timing_error ~ logbeta * duration * dprime, data=data)
lrtest(M5, M9) #p < 0.05  But very high correlation between explanatory variables

M10 <-lm(timing_error ~ logbeta + duration * dprime, data=data)
lrtest(M5, M10) #n.s

compare_performance(M1, M2, M3, M4, M5, M6, M7, M8, M9, M10) #M8 best AIC

summary(M1)
summary(M5)
summary(M6)
summary(M7)
summary(M8)
summary(M9)
summary(M10)

# M11 <-lm(timing_error ~ duration:logbeta + logbeta + duration + dprime, data=data)

summary(M8)
summary(M11)
check_heteroscedasticity(M8) #OK
check_autocorrelation(M8) #OK
check_collinearity(M8) #OK (only low correlation) residuals are independent and not auto-correlated


anova(M8)


# Verification of model assumptions ####

plot(M8)

R1 <- resid(M8) #residuals
F1 <- fitted(M8) #fitted values


## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)
check_normality(M8) #non-normality


## independance : residuals vs each model covariable

# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

#D' 
predictions <- summary(emmeans(M8, ~ duration * logbeta + dprime, at = list(dprime = seq(0,5, by = 0.1))))

# jpeg("model", width = 4000, height = 2500, units = "px",res=600)
ggplot(data, aes(dprime, timing_error)) +
geom_point(size = 0.7) +
  theme_classic() +
geom_point(predictions, mapping = aes(y= emmean, colour = duration)) +
  labs(y = "Timing Error (s)", x = "d'")
# dev.off()


#Bias
predictions <- summary(emmeans(M8, ~ duration * logbeta + dprime, at = list(logbeta = seq(-3,3, by = 0.1))))

# jpeg("model", width = 4000, height = 2500, units = "px",res=600)
ggplot(data, aes(y = timing_error, x =logbeta)) +
geom_point(size = 0.7) +
  theme_classic() +
geom_point(predictions, mapping = aes(y= emmean, colour = duration)) +
  labs(y = "Timing Error (s)", x = "log(β)")
# dev.off()


summary(M8)

emmeans(M8, "dprime", at = list(dprime = c(1, 2, 3, 4)))
emmeans(M8, ~ duration | logbeta, at = list(logbeta = c(-1, 0, 1)))

```




#Passing of Time: Duration x WM load
```{r}
Likert_1backduration <- Nback_blocks %>%
  mutate(duration = paste(duration, nback)) %>%
   filter(!is.na(likert)) %>%
  filter(nback == "1back") %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(duration, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(duration) %>%
	spread(likert, perc) 

Likert_3backduration <- Nback_blocks %>%
  mutate(duration = paste(duration, nback)) %>%
   filter(!is.na(likert)) %>%
  filter(nback == "3back") %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly")) %>%
	group_by(duration, likert) %>%  # grouping by these two variables
	tally() %>%  # counting the number of responses
	mutate(perc = n / sum(n) * 100) %>%
	dplyr::select(-n) %>%
	group_by(duration) %>%
	spread(likert, perc) 

Likert_1backduration 
Likert_3backduration
Likert_duration<- bind_rows(Likert_1backduration, Likert_3backduration)
Likert_duration


likert_hi_lo <- Likert_duration %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(duration, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("duration", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))



# Use RColorBrewer to store a preset diverging colour palette as a vector of colour codes 
legend_pal <- brewer.pal(name = "RdBu", n = 5)

# Duplicate the middle value, remember that "Sometimes" is actually two groups, "midhigh" and "midlow"
legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

# Replace the ugly white colour for "Sometimes" with a pleasant dishwater grey
legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

# Assign names to the vector based on the colours we want for each group
# legend_pal =  c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
#                 "#D55E00", "#CC79A7")
names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

# jpeg("divergBarNbackXduration.jpg", width = 5000, height = 2500, units = "px",res=600)
ggplot() + 
	geom_bar(data = likert_hi, aes(x =duration, y=perc, fill = response), stat="identity", width = 0.7) +
	geom_bar(data = likert_lo, aes(x = duration, y=-perc, fill = response), stat="identity", width = 0.7) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, name = "In the last round,\nthe time seemed \nto have passed:",
		breaks = c("Very Quickly", "Quickly", "midhigh",  "Slowly", "Very Slowly"  ),
		labels = c("Very quickly", "Quickly", "Normally", "Slowly", "Very slowly"  )) +
	coord_flip() + 
	labs(x = "Duration x WM loaD", y = "Percentage of respondents (%)", title = "Diverging stacked bar of likert scale responses (WM Load x duration)") +
  scale_y_continuous(breaks = seq(from = -50, to = 80, by = 10),
                     limits = c(-55,85)) +
	theme_classic()
# dev.off()


#useless because durations effect is big compared to wm load effect
```

#Correlation  Duration Judgment X PoTJ
```{r}
cor(Nback_blocks$timing_error, as.numeric(as.character(Nback_blocks$likert_n)), method = "spearman", use = "complete.obs")
```

##PoTJ VS ILI, WM Load & Duration (design paramaters) - 3 diverging stacked bar
```{r}
#PoTJ vs Duration
likert_hi_lo <- Likert_duration %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(design, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("duration", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))

legend_pal <- brewer.pal(name = "RdBu", n = 5)

legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

POTJduration <- ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
	coord_flip() + 
	labs(x = "duration", y = "Percentage of respondents (%)") +
  scale_y_continuous(breaks = seq(from = -40, to = 80, 20),
                     limits = c(-45,80)) +
	theme_classic()
	
	
	
	#PoTJ vs ILI
likert_hi_lo <- Likert_ILI %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(design, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("ILI", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))


legend_pal <- brewer.pal(name = "RdBu", n = 5)

legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

POTJILI <- ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
	coord_flip() + 
	labs(x = "ILI", y = "Percentage of respondents (%)") +
  scale_y_continuous(breaks = seq(from = -40, to = 80, 20),
                     limits = c(-45,80)) +
	theme_classic()
	
	


#PoTJ vs WM Load
	likert_hi_lo <- Likert_nback %>%
	mutate(midlow = Normally / 2,
		midhigh = Normally / 2) %>%
	dplyr::select(design, `Very Slowly`, Slowly, midlow, midhigh, Quickly, `Very Quickly`) %>%
	gather(key = response, value = perc, 2:7) 
	colnames <- (c("nback", "response", "perc"))


likert_lo <- likert_hi_lo %>%
	filter(response %in% c( "midlow", "Slowly", "Very Slowly")) %>%
	mutate(response = factor(response, levels = c("Very Slowly", "Slowly", "midlow")))

likert_hi <- likert_hi_lo %>%
	filter(response %in% c( "Very Quickly", "Quickly", "midhigh")) %>%
	mutate(response = factor(response, levels = c("Very Quickly", "Quickly", "midhigh")))

legend_pal <- brewer.pal(name = "RdBu", n = 5)

legend_pal <- insert(legend_pal, ats = 3, legend_pal[3])

legend_pal <- gsub("#F7F7F7", "#9C9C9C", legend_pal)

names(legend_pal) <- c("Very Quickly", "Quickly","midhigh", "midlow", "Slowly", "Very Slowly" )

POTJNback <- ggplot() + 
	geom_bar(data = likert_hi, aes(x = design, y=perc, fill = response), stat="identity", width = 0.5) +
	geom_bar(data = likert_lo, aes(x = design, y=-perc, fill = response), stat="identity", width = 0.5) + 
	geom_hline(yintercept = 0, color =c("black")) + 
	scale_fill_manual(values = legend_pal, 
		breaks = c("Very Quickly", "Quickly", "midhigh", "Slowly", "Very Slowly" ),
		labels = c("Very Quickly", "Quickly","Normally", "Slowly", "Very Slowly")) +
	coord_flip() + 
	labs(x = "WM Load", y = "Percentage of respondents (%)") +
  scale_y_continuous(breaks = seq(from = -40, to = 80, 20),
                     limits = c(-45,80)) +
	theme_classic()
	

POTJNback <- POTJNback + theme(legend.position = "none")
POTJduration <- POTJduration+ theme(legend.position = "none")
POTJILI = POTJILI + theme(legend.position = "none")

#Merge the three graphs

          
# jpeg("divergingBarLikertretro2", width = 3000, height = 2500, units = "px",res=600)
  plot_grid( POTJNback, POTJduration, POTJILI, nrow = 3)
  # dev.off()
```

##Bias X PoTJ violin plot 2
```{r}

Nback_blocks <- Nback_blocks %>%
  mutate(relative_timing = estimate / parse_number(as.character(duration)),
         likert2 = ifelse(likert == "Very Slowly" | likert == "Slowly", "Slowly", as.character(likert)),
         likert2 = ifelse(likert == "Very Quickly" | likert == "Quickly", "Quickly", as.character(likert2)),
         likert2 = fct_relevel(likert2, c("Slowly", "Normally", "Quickly")))


my_xlab <- paste(levels(Nback_blocks$likert2),"\n(N=",table(Nback_blocks$likert2),")", sep="")
my_comparison = list( c("Slowly", "Normally"), c("Normally", "Quickly"), c("Slowly", "Quickly"))


Nback_blocks %>% 
  filter( !is.na(likert2)) %>%
   ggplot(aes(y = relative_timing, x = likert2, fill = likert2)) + 
  geom_violin(varwidth = TRUE, width= 1, outlier.size = 0.1) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_x_discrete(labels = my_xlab) +
  scale_y_continuous(breaks = seq(from = 0, to = 3, by = .5),
                     limits = c(0, 3)) +
  stat_summary(fun = mean)  +
  scale_fill_viridis(discrete = TRUE, alpha=0.3, name = "In the last round,\nthe time seemed \nto have passed:",
		labels = c("Slowly", "Normally", "Quickly")) +
   theme_classic() +  
  labs(y = "Relative Timing", x ="PoTJ", title = "Relative Timing vs Passage of Time Judgment") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.text = element_text(size = 10),
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = c(2.7,2.8,3), comparison = my_comparison)
```
