---
title: "S1global_nback_prospective_analysis"
output: html_document
---


#DEF

##packages
```{r, include= F}
library(tidyverse)
library(rmarkdown)
library(ggpubr)
library(viridis)
library(cowplot)
library(ggridges)

library(lme4)
library(lmtest)
library(performance)
library(emmeans)

library(R.utils)
library(RColorBrewer)

library(factoextra)
library(moments)
library(ordinal)
library(sure)
```

##Functions
```{r, include= F}
## Standard Error of the Mean (SEM)
sem <- function(x, na.rm=FALSE) {
     if(na.rm==TRUE) x <- na.omit(x)
     sd(x)/sqrt(length(x)) 
}  #Don't forget 10 ms bruit gorilla  

##coefficent of variation
cv <- function(x){sd(x)/mean(x)}

#Z-score
z_score <- function(x){(x - mean(x)) / sd(x)}

## Outliers removal
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}

```

##Palettes
```{r, include= F}
#Palettes of colours
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")

cbPalette2 <- c("#0072B2", "#CC79A7")

cbPalette2_v2 <- c("#66c2a4", "#fc8d59")

cbPalette4 <- c( "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7")

cbPalette5 <- c( "#CC79A7", "#009E73")
```

#FORMATTING DATA AND OUTLIERS REMOVAL

##Formatting dataset
```{r}

#Extract processed data for session 1
file <- "/home/cyril/Documents/Cognition & Brain Dynamics/TimeSocialDistancing/nback_TSD/S1global_nback.csv"

Nback = read.csv2(file, sep = ",")


# Each row is a participant response
#Defining if the letter is a target letter and if an answer is a hit, a correct reject, a miss or a false alarm. 
Nback_all <- Nback %>%           #564579 observations
   filter(!is.na(translated)) %>%
         mutate(PID = as.factor(PID),
         estimate = as.numeric(as.character(translated)),
         relative_timing = estimate / parse_number(as.character(duration)),
         timing_error = estimate - parse_number(as.character(duration)),
         age = as.numeric(as.character(age)))
        


# Each row is a different trial
Nback_blocks <- Nback_all %>%    #3785 trials
  group_by(country) %>%
  group_by(PID, .add = T) %>%
  group_by(Run, .add = T) %>%
  group_by(nback, .add =T) %>%
  group_by(ILI, duration, block_nb, .add = T) %>%
  summarise(condition = first(condition),
            likert = first(likert),
            estimate = first(estimate),
            timing_error = first(timing_error),
            relative_timing = first(relative_timing),
            ntarget = first(ntarget),
            notarget = first(notarget),
            mRT = mean(as.numeric(as.character(Reaction.Time))),
            hit = sum(response_arrow == "Left" & Correct == T),
            miss  = sum(response_arrow == "Down" & Correct == F),
            fa = sum(response_arrow == "Left" & Correct == F),
            cr = sum(response_arrow == "Down" & Correct == T),
            HR = sum(response_arrow == "Left" & Correct == T)/ntarget,
            # HR1 = sum(response_arrow == "Left" & Correct == T)/(miss + hit),
            FA = sum(response_arrow == "Left" & Correct == F)/notarget,
            # FA1 = sum(response_arrow == "Left" & Correct == F)/(fa + cr),
            CR = sum(response_arrow == "Down" & Correct == T)/notarget,
            MR = sum(response_arrow == "Down" & Correct == F)/ntarget,
            handedness = first(handedness),
            age = first(age),
            sex = first(sex),
            timestamp = first(timestamp)) %>%
  ungroup() 


 
#translate PoTJ Likert Scale from different countries in English
veryquickly = c("muy rápido", "Très rapidement","Πολύ Γρήγορα","Very Fast","Molto veloce","Çok hızlı","とても速かった")
quickly = c("rápido", "Rapidement","Γρήγορα","Fast","Veloce","Hızlı","速かった")
normally = c("Normalement", "Κανονικά", "Neutral", "Neutrale", "普通", "Nötr", "normal")
slowly = c("lento","Lentement","Αργά","Slow","Very Slow","Lentamente","Yavaş", "遅かった") 
veryslowly = c("Muy lento", "Très lentement","Πολύ Αργά","Molto lentamente","Çok yavaş","とても遅かった")

Nback_blocks <- Nback_blocks %>%
  mutate(likert = ifelse(likert %in% veryquickly, "Very Quickly", as.character(likert)),
         likert = ifelse(likert %in% quickly, "Quickly", as.character(likert)),
         likert = ifelse(likert %in% normally, "Normally", as.character(likert)),
         likert = ifelse(likert %in% slowly, "Slowly", as.character(likert)),
         likert = ifelse(likert %in% veryslowly, "Very Slowly", as.character(likert))) %>%
  mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly"),
  likert_n = as.factor(recode(likert, "Very Slowly" = -2, "Slowly" = -1, "Normally" = 0, "Quickly" = 1, "Very Quickly" = 2))) 

#dprime computation and dealing with score >= 1 or =< 0
Nback_blocks <- Nback_blocks %>%
  filter(HR < 1.2 & MR < 1.5) %>%
  mutate(HR = ifelse(HR > 1, 1, HR),
         FA = ifelse(FA > 1, 1, FA),
         CR = ifelse(CR > 1, 1, CR),
         HR = ifelse(HR == 0, 0.01, HR),
  HR = ifelse(HR == 1, 0.99, HR),
  FA = ifelse(FA == 0, 0.01, FA),
  FA = ifelse(FA == 1, 0.99, FA),
  zHR = qnorm(HR),
  zFA = qnorm(FA),
  dprime = zHR - zFA,
  beta = exp(-zHR*zHR/2+zFA*zFA/2),
  logbeta = log(beta))


Nback_blocks <- Nback_blocks %>%
  dplyr::select(-ntarget, -notarget, - hit, -miss, -fa, -cr, -zHR, -zFA)



paged_table(Nback_blocks) #14893

```




##Remove retrospective tasks (first trial of the first run for each participant)
```{r}
Nback_blocks <- Nback_blocks %>%
  group_by(PID) %>%
  arrange(timestamp) %>%
  mutate(timestamp2 = as.character(timestamp)) %>%
  mutate(order = row_number()) 
  


#Remove retrospective tasks (first trial of the first run for each participant)
Nback_blocks = Nback_blocks %>%
  filter(order != 1)

#14,893 --> 13,796 trials


Nback_blocks %>%
  group_by(country, nback) %>%
  summarise(n = n())

#What is the first design condition encountered by the subject ? --> equally distributed
Nback_blocks %>%
  group_by(condition) %>%
  count()
```



##Signal detection theory - HR, CR, FA and d' distribution (before outliers removal)
```{r}

#HR DISTRIBUTION

# jpeg("DistributionHRpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFApro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'pro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```




##Performance Outliers - no discrimination (d' = 0) or inverse discrimination (d' <0)
```{r}

#Outliers on d'

perf_outliers <- Nback_blocks %>%
filter(dprime <= 0) #2348 outliers (665 out of ~6500 1-back tasks -> ~10%, 1683 out of ~7500 3-back -> ~20%)

Nback_blocks <- Nback_blocks %>%
filter(dprime > 0)     #13796 --> 11448 obs


#HR DISTRIBUTION

# jpeg("DistributionHRpro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFApro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRpro.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'pro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```


##Outliers removal on Timing Error
```{r}
# jpeg("DistribTEpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (before outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
# dev.off()


#Outliers on TE

Nback_blocks <- Nback_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- Nback_blocks %>%
filter(abs(ZTiming) > 2)    #334  outliers  (147 for 45s)

Nback_blocks <-  Nback_blocks %>%        #11448 -> 11114 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 


# jpeg("DistribTEpro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (after outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 90, by = 15),
  limits = c(-91, 91))
# dev.off()
```











##Demographics
```{r}
#sex ratio
Nback_blocks %>%
  group_by(sex) %>%
  summarise(n = n()) 

#handedness ratio
Nback_blocks %>%
  group_by(country, handedness) %>%
  summarise(n = n()) 

#Age (year + month)
Nback_blocks %>%
  filter(!is.na(age)) %>%
  summarise(mean = mean(as.numeric(as.character(age))), sd = sd(as.numeric(as.character(age))))


#Graph density ridge, age distribution for each country
# jpeg("DistribAge2S1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
   filter(age > 18) %>%
    filter(country != "Columbia") %>%
  mutate(country = as.factor(country)) %>%
  ggplot( aes(y= country, x= age,  fill= country)) +
    geom_density_ridges(alpha=0.6) +
    theme_ridges() +
    theme(legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8),
      axis.title.y = element_text("vjust" = 0.5),
      axis.title.x = element_text("hjust" = 0.5)) +
  labs(y = "Country", x = "Age", title ="Age distribution of participants for each country") +
  # scale_y_discrete(labels = c("France (278)", "Turkey (109)", "Argentina (106)", "Italy (101)", "Greece (93)",  "Japan (69)",  "India (37)",  "Canada (24)")) +
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  scale_x_continuous(breaks = seq(from = 20, to = 75, by = 5))
# dev.off()

  nb_subjects <- Nback_blocks %>%
  group_by(PID) %>%
  summarise(country = first(country)) %>%
  group_by(country) %>%
  summarise(numbersubjects = n())
nb_subjects
```



# N-BACK PERFORMANCE 2 (D', Bias, mRT)




# N-BACK PERFORMANCE 2 (D', Bias, mRT)


##Mixed-effect  models on d', bias and mRT
```{r}
data <- Nback_blocks #11114


## Model for D'


Md1 <-lmer(dprime ~ duration + (1|PID), data=data,  REML=FALSE)

Md2 <-lmer(dprime ~ duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md1, Md2)  #p < 0.05*** -> More complex model (Md2) significantly better than Md1

Md3 <-lmer(dprime ~ duration + ILI + nback + (1|PID), data=data,  REML=FALSE)
lrtest(Md2, Md3) #p < 0.05 -> More complex model (Md3) significantly better than Md1

Md4 <-lmer(dprime ~ duration * ILI + nback + (1|PID), data=data,  REML=FALSE)   #every interaction was tested, none is significantly better than md3
lrtest(Md3, Md4) #p > 0.05 n.s complex model (Md4) is not better

Md5 <-lmer(dprime ~ duration + ILI + nback + (nback|PID), data=data,  REML=FALSE)
lrtest(Md3, Md5) #p < 0.05 -> More complex model (Md5) significantly better than Md3

Md6 <-lmer(dprime ~ duration + ILI + nback + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(Md5, Md6) #p < 0.05 -> More complex model (Md6) significantly better than Md5

Md7 <-lmer(dprime ~ duration + ILI + nback + (nback + duration + ILI|PID), data=data,  REML=FALSE)
lrtest(Md6, Md7) #p > 0.05 n.s complex model (Md7) is not better

Md8 <-lmer(dprime ~ duration + ILI + nback + (nback + ILI|PID), data=data,  REML=FALSE)
lrtest(Md6, Md8) #p < 0.05 -> More complex model (Md8) significantly better than Md6

compare_performance(Md1, Md2, Md3, Md4, Md5, Md6, Md7, Md8) #Md6 -> best AIC

summary(Md1)
summary(Md2)
summary(Md3) #best model --> shows significative main effects of duration, ILI and WM Load on d'
summary(Md4)
summary(Md5)
summary(Md6)
summary(Md7)


#Does Md3 meet assumptions ?

# check_normality(Md3) #not OK, but graphically OK

check_heteroscedasticity(Md3) #not OK, but graphically OK
check_autocorrelation(Md3) #not OK
check_collinearity(Md3) #OK
plot(Md3)

# library(see)
# 
# check_heteroscedasticity(Md6) #not OK, but graphically OK
# check_autocorrelation(Md6) #not OK
# check_collinearity(Md6) #OK
# plot(Md6)
# plot(ranef(Md6))
# 
# qqnorm(resid(Md6, type = "normalized"))
# qqnorm(Md6, ~ranef(., level=2))

```
##D' violin plot
```{r}

violindnback <- Nback_blocks %>% 
  ggplot(aes(nback, dprime, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "WM Load", title = "WM Load x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violindduration <- Nback_blocks %>% 
  ggplot(aes(duration, dprime, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "Task Duration", title = "Duration x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))

violindILI <- Nback_blocks %>% 
  ggplot(aes(ILI, dprime, colour = ILI)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "TILI", title = "ILI x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("D' distribution vs Design",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violindnback + theme(plot.margin = margin(0, 30, 0, 0)),
  violindduration + theme(plot.margin = margin(0, 10, 0, 0)),
                           violindILI + theme(plot.margin = margin(0, 10, 0, 0)), nrow=1)
          
# jpeg("ViolinD'pro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
# jpeg("ViolinD'WMload.jpg", width = 2500, height = 2500, units = "px",res=600)
violindnback
# dev.off()
  
# jpeg("ViolinD'duration.jpg", width = 2500, height = 2500, units = "px",res=600)
violindduration
# dev.off()

# jpeg("ViolinD'ILI.jpg", width = 2500, height = 3000, units = "px",res=600)
violindILI
# dev.off()
  
```



##Models for Bias (log(Beta))
```{r}


MB1 <-lmer(logbeta ~ duration+ (1|PID), data=data,  REML=FALSE)

MB2 <-lmer(logbeta ~ duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MB1, MB2)  #p < 0.05 -> More complex model (MB2) significantly better than MB1

MB3 <-lmer(logbeta ~ duration + ILI + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB2, MB3) #p < 0.05 -> More complex model (MB3) significantly better than MB2

MB4 <-lmer(logbeta ~ ILI+ duration * nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB3, MB4)  #p < 0.05 -> More complex model (MB4) significantly better than MB3

MB5 <-lmer(logbeta ~ ILI * duration + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB5)  #p < 0.05 -> More complex model (MB5) significantly better than MB4

MB6 <-lmer(logbeta ~ ILI * nback + duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB5, MB6) #p < 0.05 -> More complex model (MB6) significantly better than MB5

MB7 <-lmer(logbeta ~ ILI * nback * duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB6, MB7) #p < 0.05 -> More complex model (MB7) significantly better than MB6

MB8 <-lmer(logbeta ~ ILI * nback * duration +(nback|PID), data=data,  REML=FALSE)
lrtest(MB7, MB8) #p < 0.05 -> More complex model (MB8) significantly better than MB7

MB9 <-lmer(logbeta ~ ILI * nback * duration +(nback + duration|PID), data=data,  REML=FALSE)
lrtest(MB8, MB9) #p < 0.05 -> More complex model (MB9) significantly better than MB8

MB10 <-lmer(logbeta ~ ILI * nback * duration +(nback + ILI|PID), data=data,  REML=FALSE)
lrtest(MB9, MB10) #p < 0.05 -> More complex model (MB10) significantly better than MB9

MB11 <-lmer(logbeta ~ ILI * nback * duration +(nback + ILI + duration|PID), data=data,  REML=FALSE)
lrtest(MB9, MB11) #p > 0.05 -> More complex model (MB11) not significantly better than MB9

compare_performance(MB1, MB2, MB3, MB4, MB5, MB6, MB7, MB8, MB9, MB10, MB11) #MB9 -> best AIC


summary(MB3)
summary(MB4)  #best model MB9 --> shows significative effects of ILI, duration, nback and duration:nback on Bias
summary(MB5)
summary(MB6)
summary(MB7)
summary(MB8)
summary(MB9)
summary(MB10)
summary(MB11)


# #Does MB4 meet assumptions ?
# 
# check_heteroscedasticity(MB4) #not OK, but graphically OK:
# plot(MB4)
# 
# check_autocorrelation(MB4) #OK
# check_collinearity(MB4)  #OK
# 
# check_normality(MB4) #not OK, but graphically OK:
# R1 <- resid(MB4) #residuals
# hist(R1, breaks = 30)


```



##Bias violin plot
```{r}

violinBiasnback <- Nback_blocks %>% 
  ggplot(aes(nback, logbeta, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load", title = "WM Load x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violinBiasduration <- Nback_blocks %>% 
  ggplot(aes(duration, logbeta, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "Task Duration", title = "Duration x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))


violinBiasILI <- Nback_blocks %>% 
  ggplot(aes(ILI, logbeta, colour = ILI)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "ILI", title = "ILI x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("Bias distribution vs Task Duration, ILI and WM Load", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violinBiasnback, violinBiasduration, violinBiasILI, nrow=1)
          
# jpeg("ViolinBiaspro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
  
  
#INTERATIONS  --> changer interactions
  violinBiasdurationnback <- Nback_blocks %>% 
    mutate(nbackduration = paste(nback, duration),
           nbackduration =  fct_relevel(nbackduration, "1back 45s", "3back 45s", "1back 90s", "3back 90s")) %>%
  ggplot(aes(nbackduration, logbeta, colour = nbackduration)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load : Task Duration", title = "Bias for different WM Load and Task Duration") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) 
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back45s","3back45S"), c("1back90s","3back90S")))

# jpeg("violinBiasprointeraction.jpg", width = 3000, height = 2500, units = "px",res=600)
  violinBiasdurationnback
# dev.off()
```





## Models for mRT
```{r}

MRT1 <-lmer(mRT ~ duration + (1|PID), data=data,  REML=FALSE)


MRT2 <- lmer(mRT ~ duration + ILI +(1|PID), data=data,  REML=FALSE)
lrtest(MRT1, MRT2) #p < 0.05 -> More complex model (MRT2) significantly better than MRT1

MRT3 <- lmer(mRT ~ duration + ILI + nback+ (1|PID), data=data,  REML=FALSE)
lrtest(MRT2, MRT3) #p < 0.05 -> More complex model (MRT3) significantly better than MRT2

MRT4 <- lmer(mRT ~ duration * nback + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT3, MRT4) #p < 0.05 -> More complex model (MRT4) significantly better than MRT3

MRT5 <- lmer(mRT ~ duration * nback * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT4, MRT5) #n.s

MRT6 <- lmer(mRT ~ duration * nback + ILI + (nback|PID), data=data,  REML=FALSE)
lrtest(MRT6, MRT4) #p < 0.05 -> More complex model (MRT6) significantly better than MRT4

MRT7 <- lmer(mRT ~ duration * nback + ILI + (nback + ILI|PID), data=data,  REML=FALSE)
lrtest(MRT7, MRT6) #p < 0.05 -> More complex model (MRT7) significantly better than MRT6

MRT8 <- lmer(mRT ~ duration * nback + ILI + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(MRT8, MRT7) #p < 0.05 -> More complex model (MRT8) significantly better than MRT7

compare_performance(MRT1, MRT2, MRT3, MRT4, MRT5, MRT6, MRT7, MRT8) #MRT6, 7 & 8 -> best AIC

summary(MRT1)
summary(MRT2) 
summary(MRT4)
summary(MRT5)
summary(MRT6)#best model --> shows significative effects of duration and ILI on mean Reaction Time
summary(MRT7)#fit is singular !
summary(MRT8)#fit is singular !

# #Does MRT6 meet assumptions ?
# 
# check_normality(MRT2) #not OK, but graphically OK:
# check_heteroscedasticity(MRT2) #not OK, but graphically OK:
# plot(MRT2)
# 
# check_autocorrelation(MRT2) #OK
# check_collinearity(MRT2) #OK




#compute emmeans
# emmeans(MB4, pairwise ~ nback | duration)
# emmeans(MB4, pairwise ~ nback)
# emmeans(MB4, "nback")
# summary(MB4)
# 
# emmeans(MB4, pairwise ~ nback)
```


##mRT violin plot
```{r}
mRTILI <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = ILI, colour = ILI)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "mRT (ms)", x ="ILI") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1400, comparison = list(c("1500ms", "1800ms")))


mRTDuration <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = duration, colour = duration)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "mRT (ms)", x ="Task Duration") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), axis.title = element_text(size = 12)) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  scale_colour_manual(values = cbPalette2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1390, comparison = list(c("45s", "90s")))


mRTDnback <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = nback, colour = nback)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "mRT (ms)", x ="WM Load") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), axis.title = element_text(size = 12)) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  scale_colour_manual(values = cbPalette4) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1390, comparison = list(c("1back", "3back")))


title <- ggdraw() + draw_label("mRT for different design", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(mRTILI, mRTDuration, mRTDnback, nrow=1)
          
# jpeg("mRTViolinRetro.jpg", width = 3000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
```






##D' violin plot
```{r}

violindnback <- Nback_blocks %>% 
  ggplot(aes(nback, dprime, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "WM Load", title = "WM Load x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violindduration <- Nback_blocks %>% 
  ggplot(aes(duration, dprime, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "Task Duration", title = "Duration x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))

violindILI <- Nback_blocks %>% 
  ggplot(aes(ILI, dprime, colour = ILI)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "TILI", title = "ILI x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("D' distribution vs Design",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violindnback + theme(plot.margin = margin(0, 30, 0, 0)),
  violindduration + theme(plot.margin = margin(0, 10, 0, 0)),
                           violindILI + theme(plot.margin = margin(0, 10, 0, 0)), nrow=1)
          
# jpeg("ViolinD'pro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
# jpeg("ViolinD'WMload.jpg", width = 2500, height = 2500, units = "px",res=600)
violindnback
# dev.off()
  
# jpeg("ViolinD'duration.jpg", width = 2500, height = 2500, units = "px",res=600)
violindduration
# dev.off()

# jpeg("ViolinD'ILI.jpg", width = 2500, height = 3000, units = "px",res=600)
violindILI
# dev.off()
  
```




























# Mixed-effect models Timing Error
```{r}
data <- Nback_blocks  #11221

M1 <-lmer(timing_error ~ duration + (1|PID), data=data, REML=FALSE)

M2 <-lmer(timing_error ~ duration + nback + (1|PID), data=data, REML=FALSE)
lrtest(M1, M2) #M1 nested #M2 more complex   p <0.05  #the complex model is significantly more accurate

M3 <-lmer(timing_error ~ duration + nback + ILI + (1|PID), data=data, REML=FALSE)
lrtest(M2, M3) #M2 nested #M3 more complex  p > 0.05  #the complex model is not significantly more accurate

M4 <-lmer(timing_error ~ duration * nback * ILI + (1|PID), data=data, REML=FALSE)
lrtest(M2, M4)   #M2 nested #M4 more complex      p <0.05  #the complex model is significantly more accurate

M5 <-lmer(timing_error ~ duration + nback + ILI + (duration|PID), data=data, REML=FALSE)
lrtest(M3, M5)  #M3 nested #5 more complex    p <0.05  #the complex model is significantly more accurate

M6 <-lmer(timing_error ~ duration + nback + ILI + (duration + nback|PID), data=data, REML=FALSE)
lrtest(M5, M6)   #M5 nested #6 more complex   p <0.05  #the complex model is significantly more accurate

M7 <-lmer(timing_error ~ duration + nback + ILI + (duration + nback + ILI|PID), data=data, REML=FALSE)
lrtest(M6, M7) # n.s

M8 <-lmer(timing_error ~ duration * nback + (duration + nback|PID), data=data, REML=FALSE)
lrtest(M6, M8) #M7 nested #8 more complex   p <0.05  #the complex model is significantly more accurate

M9 <-lmer(timing_error ~ duration * nback * ILI + (duration + nback|PID), data=data, REML=FALSE)
lrtest(M8, M9)   #M8 nested #9 more complex   p = 0.08  


 
# summary(M1)
# summary(M2)
# summary(M3)
# summary(M4)
# summary(M5)
summary(M6)
summary(M7)
summary(M8)
summary(M9)


r2(M8)
compare_performance(M6, M7, M8, M9)
#we use M8

```

#Main effects
```{r}
M8 <-lmer(timing_error ~ duration * nback + (duration + nback|PID), data=data, REML=T)
summary(M8)

stargazer(M8, type = "text",
           title = "Regression results M2",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

anova(M8)

emm_options(lmer.df ="satterthwaite")

emm_options(lmer.df = "satterthwaite")
get_emm_option("lmer.df")


emmeans(M8, ~duration)

# -- Main effect of duration --   => Significant effect
emmeans(M8, ~ duration) 

# -- Main effect of WM Load --    => Significant effect
emmeans(M8, ~ nback,  lmer.df = "satterthwaite") 

# -- Main effect of Interaction duration / nback 

emmeans(M8, pairwise ~ duration | nback,  lmer.df = "satterthwaite")

emmeans(M8, pairwise ~ nback | duration,  lmer.df = "satterthwaite")   #significant when 90s 1800ms

# interaction.emm <- emmeans(M9, pairwise ~ ILI | duration + nback)  # significant when 90s 3-back
# interaction.emm

```

# Verification of model assumptions ####
```{r}

R1 <- resid(M8)
F1 <- fitted(M8)

## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)

# shapiro.test(R1)

## homogeneity : fitted values vs normalized residuals

plot(x = F1, 
     y = R1, 
     xlab = "Fitted Values",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

#timing_error
plot(x = data$timing_error, 
     y = R1, 
     xlab = "timing_error",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)


## independance : residuals vs each model covariable

# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

# nback
boxplot(R1 ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)



# data %>%
#  ggplot(aes(timing_error, R1, colour = dprime)) + 
#            geom_point() +
#       # geom_density(aes(y = ..density..*(500 * 0.02)), alpha=.4, fill="lightgreen") +
#   labs(y = "residuals", x = "timing_error", title ="model for 1-back retrospective tasks, residuals vs TE") + 
#   theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
#   # scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
#   #                limits = c(-0.01,1.01))


```










#Main effects
```{r}
data <- data %>%
  mutate(relative_error = (as.numeric(as.character(translated)) - parse_number(as.character(duration))) / parse_number(as.character(duration)))
  



M6 <-lmer(relative_error ~ duration + nback + ILI + (duration + nback|PID), data=data, REML=T)
summary(M6)


data <- data %>%
  mutate(cdur = ifelse(cdur == 3, 9, cdur),
         cdur = ifelse(cdur == 4, 10, cdur))
  
M9 <-lmer(timing_error ~ duration  + cdur + (cdur|PID), data=data, REML= T)

stargazer(M9, type = "text",
           title = "Regression results M2",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

summary(M9)
anova(M9)



# -- Main effect of duration --   => Significant effect
duration.emm <- emmeans(M9, ~ duration) 
duration.emm
plot(duration.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
     horizontal = FALSE, colors = "darkgreen")
# pwpp(duration.emm)


# -- Main effect of WM Load --    => No significant effect
nback.emm <- emmeans(M9, ~ nback) 
nback.emm
plot(nback.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
     horizontal = FALSE, colors = "darkgreen")
# pwpp(nback.emm)

# # -- Main effect of ILI --        => No significant effect
# ILI.emm <- emmeans(M6, ~ ILI) 
# ILI.emm
# plot(ILI.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
#      horizontal = FALSE, colors = "darkgreen")
# # pwpp(ILI.emm)



# -- Main effect of Interaction duration / nback / ILI

interaction.emm <- emmeans(M9, pairwise ~ duration | nback, pbkrtest.limit = 11221)
interaction.emm
interaction.emm <- emmeans(M9, pairwise ~ nback | duration , pbkrtest.limit = 11221)   #significant when 90s 1800ms
interaction.emm
# interaction.emm <- emmeans(M9, pairwise ~ ILI | duration + nback)  # significant when 90s 3-back
# interaction.emm


```

# Verification of model assumptions ####
```{r}

M8 <-lmer(timing_error ~ duration * nback * ILI + (duration + nback|PID), data=data, REML=FALSE)
M8bis <-lmer(timing_error ~ duration * nback * ILI + estim + (duration + nback|PID), data=data, REML=FALSE)

R1 <- resid(M6)
F1 <- fitted(M6)

## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)

# shapiro.test(R1)

## homogeneity : fitted values vs normalized residuals

plot(x = F1, 
     y = R1, 
     xlab = "Fitted Values",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

# duration_deviation
plot(x = data$timing_error, 
     y = R1, 
     xlab = "timing_error",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

# Participants
boxplot(R1 ~ PID,   
        ylab = "Normalized residuals",
        data = data, xlab = "Participant")
abline(h = 0, lty = 2)


## independance : residuals vs each model covariable



# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

# nback
boxplot(R1 ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)
 
#ILI
boxplot(R1 ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)

```






#Passing of time statistic models
```{r}

data = Nback_blocks %>%
  filter(nback == "1back")

library(MASS)

m1 = polr(likert_n ~ duration, data, Hess=T)

m2 = clmm(likert_n ~ duration + nback + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m1,m2)  # p > 0.05

m3 = clmm(likert_n ~ duration * nback + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m1,m3)  # p < 0.05

m3 = clmm(likert_n ~ duration + ILI + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m1,m3) 

m4 = clmm(likert_n ~ duration + nback + ILI + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m2,m4)  # p < 0.05

m5 = clmm(likert_n ~ duration * nback * ILI + (1|PID), data, Hess=T, nAGQ= 7)
lrtest(m4,m5)  # p < 0.05

AIC<-c(AIC(m1), AIC(m2), AIC(m3), AIC(m4), AIC(m5))
model<-c("m1", "m2", "m3", "m4", "m5")
AICtable<-data.frame(Model=model, AIC=AIC)
AICtable


summary(m1)
summary(m2)
summary(m3)
summary(m4)
summary(m5)



#we choose m6
```

#Main effects
```{r}

# ----- Pairwise comparisons ----------------------

# -- Main effect of duration --

duration.emm <- emmeans(m5, ~ duration) 
duration.emm
plot(duration.emm, by = NULL, comparisons = TRUE, adjust = "mvt", 
     horizontal = FALSE, colors = "darkgreen")
pwpp(duration.emm)

# -- Main effect of nback --

nback.emm <- emmeans(m5, ~ nback) 
nback.emm
plot(nback.emm, by = NULL, comparisons = TRUE, adjust = "mvt", 
     horizontal = FALSE, colors = "darkgreen")
pwpp(nback.emm)


# -- Main effect of session --

ILI.emm <- emmeans(m5, ~ ILI) 
ILI.emm
plot(ILI.emm, by = NULL, comparisons = TRUE, adjust = "mvt", 
     horizontal = FALSE, colors = "darkgreen")
pwpp(ILI.emm)

# -- Main effect of Interaction nback / session / duration

interaction1.emm <- emmeans(m5, pairwise ~ nback | ILI + duration)
interaction1.emm

interaction2.emm <- emmeans(m5, pairwise ~ ILI |nback + duration)
interaction2.emm

interaction3.emm <- emmeans(m5, pairwise ~ duration |nback + ILI)
interaction3.emm





# chisq.test(NbackL_blocks$perf, NbackL_blocks$likert)
# chisq.test(NbackL_blocks$mRT, NbackL_blocks$likert)   #no correlation between mRT and likert
# chisq.test(NbackL_blocks$MR, NbackL_blocks$likert)
# chisq.test(NbackL_blocks$FAR, NbackL_blocks$likert)
# chisq.test(NbackL_blocks$CRR, NbackL_blocks$likert)



```






























# mean Reaction Time distribution for 1-back and 3-back 
```{r}
 mRT_1back <-  Nback_blocks %>%
  filter(nback == "1back") 
 mRT_3back <- Nback_blocks %>%
  filter(nback == "3back") 
 

# QQ plot
 title <- ggdraw() + 
   draw_label("Normal QQ plot of mean Reaction Time for 1-back and 3-back",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 0, 15 ,0))

plot_row = plot_grid(ggqqplot(mRT_1back$mRT, size = 0.2),
                     ggqqplot(mRT_3back$mRT, size = 0.2), 
                     nrow=1, labels=c('1-back', '3-back'),
  label_size = 11,
  hjust = -0.5, vjust = -0.5)
          
# jpeg("QQplotmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1))
# dev.off()

#shapiro-wilk test  H0 = normal
shapiro.test(mRT_1back$mRT)
shapiro.test(mRT_3back$mRT)


#the two distribution are skewed ! 


# jpeg("DistributionmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(mRT)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth= 30,
                   colour = "black" , fill="white") + 
      geom_density(aes(y = ..density..*(1800 * 30)), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Hit Rate", title ="Mean Reaction Time Distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1300, by = 250),
                 limits = c(0,1300))
 # dev.off()



skewness(filter(
  Nback_blocks, nback == "1back")$mRT, na.rm = TRUE)   #positive asymetrie

skewness(filter(
  Nback_blocks, nback == "3back")$mRT, na.rm = TRUE)   #positive asymetrie


Nback_blocks$normRT <- log10(Nback_blocks$mRT)
mRT_1back$normRT <- log10(mRT_1back$mRT)
mRT_3back$normRT <- log10(mRT_3back$mRT)


skewness(filter(
  Nback_blocks, nback == "1back")$normRT, na.rm = TRUE)   #positive asymetrie

skewness(filter(
  Nback_blocks, nback == "3back")$normRT, na.rm = TRUE)   #negative asymetrie
#sqrt(x) pour les données asymétriques positives ?

# jpeg("DistributionmRTS1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(normRT)) + 
  facet_grid(.~nback) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth= 0.01,
                   colour = "black" , fill="white") + 
      geom_density(aes(y = ..density..), alpha=.4, fill="lightgreen") +
  labs(y = "count", x = "Hit Rate", title ="Mean Reaction Time Distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
  # scale_x_continuous(breaks = seq(from = 0, to = 1300, by = 250),
  #                limits = c(0,1300))
 # dev.off()

shapiro.test(mRT_1back$normRT)
shapiro.test(mRT_3back$normRT)
```




#SUPPLEMENTARY CHUNKS





#N-BACK PERFORMANCE 1 (HR, FA, mRT)


##N-back Performance table and N-Back Performance Graphs for different WM load and Task duration
```{r}
perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, duration) %>%
  summarise(HR = mean(HR), mRT = mean(mRT), FA = mean(FA))

semHR <- aggregate(HR ~ nback + duration, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + duration, Nback_blocks, sem) #apply sem function 
semFA <- aggregate(FA ~ nback + duration, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)

# Hit Rate VS WM load and task duration
perf_HR = perfNback %>% ggplot (aes(x = nback, y = HR, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0.30, to = 0.90, by = 0.10), limits = c(0.29, 0.90))


# False Alarm rate VS WM load and task duration
perf_FA = perfNback %>% ggplot (aes(x = nback, y = FA, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 11),
          axis.text = element_text(size = 11),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
    legend.position = c(.7, .15))  +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2) +
  scale_y_continuous(breaks = seq(from = 0, to = 0.25, by = 0.05), limits = c(0, 0.25))


# mean Reaction Time VS WM load and task duration
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT, group = duration, colour = duration)) +
  geom_point(size = 2) +
  geom_line(aes(group = duration), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11), legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
   legend.position = c(.8, .2))  +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT), colour = "black", width = .05)  +
    scale_colour_manual(values = cbPalette2, labels = c("45s", "90s")) +
  scale_y_continuous(breaks = seq(from = 560, to = 640, by = 20), limits = c(560, 640)) 



#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA 
perf_mRT = perf_mRT + theme(legend.position = "none")

title <- ggdraw() + draw_label("N-back performance VS working memory load and task duration",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
    
# jpeg("PerfNbackDurationretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))  
# dev.off()
```




##N-back Performance table and N-Back Performance Graphs for different WM load and ILI (Inter-letter interval)
```{r}

perfNback <- Nback_blocks %>%
  filter(!is.na(mRT)) %>%
  group_by(nback, ILI) %>%
  summarise(HR = mean(HR), mRT = mean(mRT), FA = mean(FA))

semHR <- aggregate(HR ~ nback + ILI, Nback_blocks, sem) 
semmRT <- aggregate(mRT ~ nback + ILI, Nback_blocks, sem)  #apply sem function 
semFA <- aggregate(FA ~ nback + ILI, Nback_blocks, sem) 

perfNback <- bind_cols(perfNback, semHR$HR, semmRT$mRT, semFA$FA) %>% 
  rename(semHR = ...6, semmRT = ...7, semFA = ...8 )

paged_table(perfNback)


perf_HR = perfNback %>% ggplot (aes(x = nback, y = HR, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Hit Rate") +
  theme( legend.text = element_text(size = 15),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = HR - semHR, ymax = HR + semHR), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2_v2) +
  scale_y_continuous(breaks = seq(from = 0.40, to = 0.90, by = 0.10), limits = c(0.35, 0.90))


perf_FA = perfNback %>% ggplot (aes(x = nback, y = FA, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "False Alarm Rate") +
  theme( legend.text = element_text(size = 10),
          axis.text = element_text(size = 10),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13),
  legend.position = c(.72, .15)) +
  geom_errorbar(aes(ymin =FA - semFA, ymax = FA + semFA), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette2_v2)  +
  scale_y_continuous(breaks = seq(from = 0.05, to = 0.20, by = 0.05), limits = c(0.05, 0.23)) 


# mean Reaction Time VS WM load and ILI
perf_mRT = perfNback %>% 
  ggplot (aes(x = nback, y = mRT, group = ILI, colour = ILI)) +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(x = "WM load", y = "Mean Reaction Time (ms)") +
  theme( legend.text = element_text(size = 11), legend.title = element_text(size = 11),
          axis.text = element_text(size = 12),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin =mRT - semmRT, ymax = mRT + semmRT), colour = "black", width = .05) +
  scale_y_continuous(breaks = seq(from = 560, to = 660, by = 20), limits = c(550, 660)) +
  scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms"))


#merge the 3 graphs and save the final graph
perf_HR <- perf_HR + theme(legend.position = "none")
perf_FA <- perf_FA 
perf_mRT = perf_mRT + theme(legend.position = "none")

title <- ggdraw() + draw_label(
    "N-back performance VS working memory load and ILI",
    fontface = 'bold', size = 13) +
  theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(perf_HR, perf_FA, perf_mRT, nrow=1, labels=c('A', 'B', 'C'))
          
# jpeg("PerfNbackILIretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1)) 
# dev.off()
  
  
```


#Subjective vs Objective Duration (with and without ILI)
```{r}
#Duration estimation tables 

durations <- Nback_blocks %>%
  group_by(nback) %>% 
  group_by(duration, .add = T) %>% 
  summarize(DD = mean(timing_error), semDD = sem(timing_error))

durations_by_ILI <- Nback_blocks%>%
  group_by(duration, .add = T) %>%   
  group_by(ILI, .add = T) %>%
  group_by(nback, .add = T) %>%
  summarize(DD = mean(timing_error), semDD = sem(timing_error))


#Subjective vs Objective Duration graph
DD_vs_OD_Nback = durations %>% ggplot (aes(x = duration,y = DD, group = nback, colour = nback)) +
scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = .5, linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = nback), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration") +
  theme(legend.text = element_text(size = 11), legend.title  = element_text(size = 12), axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12), axis.text = element_text(size = 12),
  legend.position = c(.90, .65),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD), colour = "black", width = .05) +
  scale_colour_manual(values = cbPalette, labels = c("1-back", "3-back"), name = "WM load")

#Subjective vs Objective Duration with ILI
DD_vs_OD_ILI = durations_by_ILI %>%
  ggplot (aes(x = duration, y = DD, group = ILI, colour = ILI)) +
  scale_y_continuous(breaks = seq(from = -20, to = 0, by = 5),
                     limits = c(-23, 5)) +
  geom_hline(aes(yintercept = 0),  colour = 'black',size = .5, linetype = "dashed") +
  geom_point(size = 2) +
  geom_line(aes(group = ILI), size = 1) +
  theme_classic() +
  labs(y = "Subjective Duration Deviation (s)", x = "Objective Task Duration") +
  theme(legend.text = element_text(size = 11), legend.title  = element_text(size = 12), axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12), axis.text = element_text(size = 12),
  legend.position = c(.50, .6),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = DD - semDD, ymax = DD + semDD), colour = "black", width = .05) +
 scale_colour_manual(values = cbPalette2_v2, labels = c("1500ms", "1800ms")) +
  facet_grid(.~nback)


#Merge the two graphs
title <- ggdraw() + draw_label("Subjective Duration Deviation VS Objective Duration for different conditions",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(DD_vs_OD_Nback + theme(plot.margin = margin(0, 30, 0, 0)),
  DD_vs_OD_ILI + theme(plot.margin = margin(0, 10, 0, 0)),  
  nrow=1, labels=c('A', 'B'),  rel_widths =  c(3, 5))
          
# jpeg("SD_ODretro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()


```





#Coefficient of variation and Variance
```{r}
#Variance
SD_Var <- Nback_blocks %>% 
  group_by(nback) %>%
  group_by(duration, .add =T) %>%
  summarise(VarSD = var(estimate), 
            semSD = sd(estimate)/sqrt(n()))

SDvar_duration_nback <- ggplot(data = SD_Var,
             aes(x = nback,
                 y = VarSD,
                 group = duration,
                 fill = interaction(duration, nback))) +
  labs(x = "WM load", y = "Subjective duration variance (s²)") +
  theme_classic() +
  theme(legend.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 12),
        plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_fill_manual(values = cbPalette4, name = "Duration",
  labels = c("45s", "90s", "45s", "90s")) +
  geom_bar(stat = "identity", width = .7, position = "dodge", alpha = 0.5) 

#Coefficient of Variation
CVtime <- Nback_blocks %>%
  group_by(duration, .add =T) %>% 
  summarise(CV = sd(estimate)/mean(estimate), semCV = sem(estimate)/100)

CV_WM_duration <- CVtime %>%  
  ggplot (aes(x = duration, y = CV)) +
  geom_point(size = 2) +
  geom_line(aes(x = duration, y = CV), size = 1) +
  theme_classic() +
    labs(y = "estimation CV", x = "Task Duration") +
  theme(legend.title = element_text(size = 10), 
    legend.text = element_text(size = 9),
          axis.text = element_text(size = 12),
  legend.position = c(.8, .8),
  plot.title = element_text(face = "bold", "hjust" = 0.5), axis.title= element_text(size = 13)) +
  geom_errorbar(aes(ymin = CV - semCV, ymax = CV + semCV),
                width = .05,
                color = "black") 


title <- ggdraw() + draw_label("Subjective duration variance and CV vs Task Dr((uration",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(SDvar_duration_nback, CV_WM_duration, nrow=1, labels=c('A', 'B'), rel_widths =  c(2, 1.4))
          
# jpeg("CV_Varianceretro.jpg", width = 4000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
```

