---
title: "SCglobal_nback_prospective_analysis"
output: html_document
---

#DEF

##packages
```{r, include= F}
library(tidyverse)
library(rmarkdown)
library(ggpubr)
library(viridis)
library(cowplot)

library(lme4)
library(lmtest)
library(performance)
library(emmeans)

library(R.utils)
library(RColorBrewer)

library(factoextra)
library(moments)
library(ordinal)
library(sure)
```

##Functions
```{r, include= F}
## Standard Error of the Mean (SEM)
sem <- function(x, na.rm=FALSE) {
     if(na.rm==TRUE) x <- na.omit(x)
     sd(x)/sqrt(length(x)) 
}  #Don't forget 10 ms bruit gorilla  

##coefficent of variation
cv <- function(x){sd(x)/mean(x)}

#Z-score
z_score <- function(x){(x - mean(x)) / sd(x)}

## Outliers removal
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}

```

##Palettes
```{r, include= F}
#Palettes of colours
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")

cbPalette2 <- c("#0072B2", "#CC79A7")

cbPalette2_v2 <- c("#66c2a4", "#fc8d59")

cbPalette4 <- c( "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7")

cbPalette5 <- c( "#CC79A7", "#009E73")
```

#FORMATTING DATA AND OUTLIERS REMOVAL

##Formatting dataset
```{r}

#Extract processed data for session 1
file <- "/home/cyril/Documents/Cognition & Brain Dynamics/TimeSocialDistancing/nback_TSD/SCglobal_nback.csv"

Nback = read.csv2(file, sep = ",")  


# Each row is a participant response
#Defining if the letter is a target letter and if an answer is a hit, a correct reject, a miss or a false alarm. 
Nback_all <- Nback %>%           #138530 obs
   filter(!is.na(translated)) %>%
         mutate(PID = as.factor(PID),
         estimate = as.numeric(as.character(translated)),
         relative_timing = estimate / parse_number(as.character(duration)),
         timing_error = estimate - parse_number(as.character(duration)),
         age = as.numeric(as.character(Age)))
        


# Each row is a different trial
Nback_blocks <- Nback_all %>%    #3728 trials
  group_by(Country) %>%
  group_by(PID, .add = T) %>%
  group_by(Run, .add = T) %>%
  group_by(nback, .add =T) %>%
  group_by(ILI, duration, block_nb, .add = T) %>%
  summarise(condition = first(condition),
            # likert = first(likert),
            estimate = first(estimate),
            timing_error = first(timing_error),
            relative_timing = first(relative_timing),
            ntarget = first(ntarget),
            notarget = first(notarget),
            mRT = mean(as.numeric(as.character(Reaction_Time))),
            hit = sum(response_arrow == "Left" & Correct == T),
            miss  = sum(response_arrow == "Down" & Correct == F),
            fa = sum(response_arrow == "Left" & Correct == F),
            cr = sum(response_arrow == "Down" & Correct == T),
            HR = sum(response_arrow == "Left" & Correct == T)/ntarget,
            # HR1 = sum(response_arrow == "Left" & Correct == T)/(miss + hit),
            FA = sum(response_arrow == "Left" & Correct == F)/notarget,
            # FA1 = sum(response_arrow == "Left" & Correct == F)/(fa + cr),
            CR = sum(response_arrow == "Down" & Correct == T)/notarget,
            MR = sum(response_arrow == "Down" & Correct == F)/ntarget,
            handedness = first(Handedness),
            age = first(Age),
            sex = first(Sex),
            timestamp = first(timestamp)) %>%
  ungroup() 


 
# #translate PoTJ Likert Scale from different countries in English
# veryquickly = c("muy rápido", "Très rapidement","Πολύ Γρήγορα","Very Fast","Molto veloce","Çok hızlı","とても速かった")
# quickly = c("rápido", "Rapidement","Γρήγορα","Fast","Veloce","Hızlı","速かった")
# normally = c("Normalement", "Κανονικά", "Neutral", "Neutrale", "普通", "Nötr", "normal")
# slowly = c("lento","Lentement","Αργά","Slow","Very Slow","Lentamente","Yavaş", "遅かった") 
# veryslowly = c("Muy lento", "Très lentement","Πολύ Αργά","Molto lentamente","Çok yavaş","とても遅かった")
# 
# Nback_blocks <- Nback_blocks %>%
#   mutate(likert = ifelse(likert %in% veryquickly, "Very Quickly", as.character(likert)),
#          likert = ifelse(likert %in% quickly, "Quickly", as.character(likert)),
#          likert = ifelse(likert %in% normally, "Normally", as.character(likert)),
#          likert = ifelse(likert %in% slowly, "Slowly", as.character(likert)),
#          likert = ifelse(likert %in% veryslowly, "Very Slowly", as.character(likert))) %>%
#   mutate(likert = fct_relevel(likert, "Very Slowly", "Slowly",  "Normally", "Quickly", "Very Quickly"),
#   likert_n = as.factor(recode(likert, "Very Slowly" = -2, "Slowly" = -1, "Normally" = 0, "Quickly" = 1, "Very Quickly" = 2))) 

#dprime computation and dealing with score >= 1 or =< 0
Nback_blocks <- Nback_blocks %>%
  # filter(HR < 1.2 & MR < 1.5) %>%
  mutate(HR = ifelse(HR > 1, 1, HR),
         FA = ifelse(FA > 1, 1, FA),
         CR = ifelse(CR > 1, 1, CR),
         MR = ifelse(MR > 1, 1, CR),
         HR = ifelse(HR == 0, 0.01, HR),
  HR = ifelse(HR == 1, 0.99, HR),
  FA = ifelse(FA == 0, 0.01, FA),
  FA = ifelse(FA == 1, 0.99, FA),
  zHR = qnorm(HR),
  zFA = qnorm(FA),
  dprime = zHR - zFA,
  beta = exp(-zHR*zHR/2+zFA*zFA/2),
  logbeta = log(beta))


Nback_blocks <- Nback_blocks %>%
  dplyr::select(-ntarget, -notarget, - hit, -miss, -fa, -cr, -zHR, -zFA)




paged_table(Nback_blocks) #3728

```

##Remove retrospective tasks (first trial of the first run for each participant)
```{r}
Nback_blocks <- Nback_blocks %>%
  group_by(PID) %>%
  arrange(timestamp) %>%
  mutate(timestamp2 = as.character(timestamp)) %>%
  mutate(order = row_number()) 
  
#store retro
retroNback_blocks <- Nback_blocks %>% #199 obs
  filter(order == 1)

#Remove retrospective tasks (first trial of the first run for each participant)
Nback_blocks = Nback_blocks %>%
  filter(order != 1)

#3728 --> 3529 obs


Nback_blocks %>%
  group_by(Country, nback) %>%
  summarise(n = n())

#What is the first design condition encountered by the subject ? --> not equally distributed
Nback_blocks %>%
  group_by(condition) %>%
  count()


```



##Signal detection theory - HR, CR, FA and d' distribution (before outliers removal)
```{r}

#HR DISTRIBUTION

# jpeg("DistributionHRpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFApro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'pro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```




##Performance Outliers - no discrimination (d' = 0) or inverse discrimination (d' <0)
```{r}

#Outliers on d'

perf_outliers <- Nback_blocks %>%
filter(dprime <= 0) #476 outliers (152 out of ~1369 1-back tasks -> ~11%, 324 out of ~1397 3-back -> 23~%)

Nback_blocks <- Nback_blocks %>%
filter(dprime > 0)     #2766 --> 2290 obs (we removed ~17% of the tasks)


#HR DISTRIBUTION

# jpeg("DistributionHRpro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(HR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "HR", title ="Hit Rate (HR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#FA DISTRIBUTION

# jpeg("DistributionFApro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(FA)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "FA", title ="False alarm rate (FA) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()


#CR DISTRIBUTION

# jpeg("DistributionCRpro.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(CR)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") +
      # geom_density(aes(y = ..density..*(00 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "CR", title ="Correct Rejection Rate (CR) distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1), limits = c(-0.01,1.01))
 # dev.off()

#Dprime DISTRIBUTION

# jpeg("DistributionD'pro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime)) + 
  facet_grid(.~nback) +
  geom_histogram(aes(y = ..count..), position = "dodge", binwidth=0.02, colour = "black" , fill="white") + 
      # geom_density(aes(y = ..density..*(1000 * 0.02)), alpha=.2, fill="lightgreen") +
  theme_light() +
  labs(y = "count", x = "d'", title ="D prime distribution for 1-back and 3-back") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
 # dev.off()

```


##Outliers removal on Timing Error
```{r}
# jpeg("DistribTEpro1.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (before outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
# dev.off()


#Outliers on TE

Nback_blocks <- Nback_blocks %>%
  group_by(duration) %>%
  mutate(ZTiming = scale(timing_error)) %>%
  ungroup()

estimation_outliers <- Nback_blocks %>%
filter(abs(ZTiming) > 2)    #76  outliers --> 3% (36 for 45s)

Nback_blocks <-  Nback_blocks %>%        #2290 -> 2214 trials
  filter(abs(ZTiming) <= 2 ) %>%
  dplyr::select(-ZTiming) 


# jpeg("DistribTEpro2.jpg", width = 4000, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(timing_error)) + 
  facet_grid(.~duration) +
           geom_histogram(aes(y = ..count..), position = "dodge", binwidth=1,
                   colour = "black" , fill="white") + 
  theme_light() +
  labs(y = "count", x = "Timing Error (s)", title ="Timing Error distribution for 45s/90s tasks (after outliers removal)") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) +
  scale_x_continuous(breaks = seq(from = -90, to = 90, by = 15),
  limits = c(-91, 91))
# dev.off()
```











##Demographics
```{r}
#sex ratio
Nback_blocks %>%
  group_by(sex) %>%
  summarise(n = n()) 

#handedness ratio
Nback_blocks %>%
  group_by(Country, handedness) %>%
  summarise(n = n()) 

#Age (year + month)
Nback_blocks %>%
  filter(!is.na(age)) %>%
  summarise(mean = mean(as.numeric(as.character(age))), sd = sd(as.numeric(as.character(age))))


# #Graph density ridge, age distribution for each country
# # jpeg("DistribAge2S1.jpg", width = 4000, height = 2500, units = "px",res=600)
# Nback_blocks %>%
#    filter(age > 18) %>%
#     # filter(country != "Columbia") %>%
#   mutate(country = as.factor(Country)) %>%
#   ggplot( aes(y= country, x= age,  fill= country)) +
#     geom_density_ridges(alpha=0.6) +
#     theme_ridges() +
#     theme(legend.position="none",
#       panel.spacing = unit(0.1, "lines"),
#       strip.text.x = element_text(size = 8),
#       axis.title.y = element_text("vjust" = 0.5),
#       axis.title.x = element_text("hjust" = 0.5)) +
#   labs(y = "Country", x = "Age", title ="Age distribution of participants for each country") +
#   # scale_y_discrete(labels = c("France (278)", "Turkey (109)", "Argentina (106)", "Italy (101)", "Greece (93)",  "Japan (69)",  "India (37)",  "Canada (24)")) +
#   theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
#   scale_x_continuous(breaks = seq(from = 20, to = 75, by = 5))
# # dev.off()
# 
  nb_subjects <- Nback_blocks %>%
  group_by(PID) %>%
  summarise(Country = first(Country)) %>%
  group_by(Country) %>%
  summarise(numbersubjects = n())
nb_subjects
```








# N-BACK PERFORMANCE 2 (D', Bias, mRT)


##Mixed-effect  models on d', bias and mRT
```{r}
data <- Nback_blocks #2214

## Model for D'



Md1 <-lmer(dprime ~ duration + (1|PID), data=data,  REML=FALSE)

Md2 <-lmer(dprime ~ duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(Md1, Md2)  #p < 0.05*** -> More complex model (Md2) significantly better than Md1

Md3 <-lmer(dprime ~ duration + ILI + nback + (1|PID), data=data,  REML=FALSE)
lrtest(Md2, Md3) #p < 0.05 -> More complex model (Md3) significantly better than Md1

Md4 <-lmer(dprime ~ duration * ILI + nback + (1|PID), data=data,  REML=FALSE)   #every interaction was tested, none is significantly better than md3
lrtest(Md3, Md4) #p > 0.05 n.s complex model (Md4) is not better

Md5 <-lmer(dprime ~ duration * nback + ILI + (1|PID), data=data,  REML=FALSE)   #every interaction was tested, none is significantly better than md3
lrtest(Md3, Md5) #p > 0.05 n.s complex model (Md5) is not better

Md6 <-lmer(dprime ~ duration + nback * ILI + (1|PID), data=data,  REML=FALSE)   #every interaction was tested, none is significantly better than md3
lrtest(Md3, Md6) #p > 0.05 n.s complex model (Md6) is not better

Md7 <-lmer(dprime ~ duration + ILI + nback + (nback|PID), data=data,  REML=FALSE)
lrtest(Md3, Md7) #p < 0.05 -> More complex model (Md7) significantly better than Md3

Md8 <-lmer(dprime ~ duration + ILI + nback + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(Md7, Md8) #p < 0.05 -> More complex model (Md8) significantly better than Md7   BUT SINGULAR !

Md9 <-lmer(dprime ~ duration + ILI + nback + (nback + ILI|PID), data=data,  REML=FALSE)
lrtest(Md7, Md9) #p > 0.05 n.s complex model (Md9) is not better

compare_performance(Md1, Md3, Md6, Md7, Md8, Md9) #Md8/Md6 best AIC but failed (singular or lrtest)  Md7 better AIC than Md9

summary(Md1)
summary(Md2)
summary(Md3) 
summary(Md4)
summary(Md5) 
summary(Md6)
summary(Md7) #best model --> shows significant main effects of duration, ILI and WM Load on d'
summary(Md8) 
summary(Md9)

Md7 <-lmer(dprime ~ duration + ILI + nback + (nback|PID), data=data,  REML=T)
summary(Md7)
stargazer(Md7, type = "text",
           title = "Regression results Md7",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

emmeans(Md7, ~nback,  lmer.df = "satterthwaite")
emmeans(Md7, ~duration,  lmer.df = "satterthwaite")
emmeans(Md7, ~ILI,  lmer.df = "satterthwaite")

#Does Md7 meet assumptions ?


#autocorrelation
check_autocorrelation(Md7)
library(car)
durbinWatsonTest(resid(Md7)) # = ~2 no autocorrelation

check_heteroscedasticity(Md7) #not OK, but graphically OK
check_collinearity(Md7) #OK


lm <- lm(dprime ~ duration + ILI + nback, data = data)
plot(lm)
plot(Md7)





## residuals distribution : histogramme and shapiro test for normality
hist(resid(Md7), breaks = 30)
qqnorm(residuals(Md7))


## homogeneity : fitted values vs normalized residuals

plot(x = data$dprime, 
     y = resid(Md7), 
     xlab = "d'",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

## independance : residuals vs each model covariable

boxplot(resid(Md7) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(Md7) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(Md7) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)




#heteroscedascity between random effects
plot(Md7, as.factor(PID) ~ resid(., scaled=TRUE),abline=0,pch=16,xlab="Standardised residuals",ylab="Regions")


require("lattice")

#It is also important to check that the random effect distribution(s) match the assumed (most often Gaussian) dsitrbibution
# lattice::dotplot(ranef(Md7, condVar=TRUE))

```

##d' violin plot
```{r}

violindnback <- Nback_blocks %>% 
  ggplot(aes(nback, dprime, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "WM Load", title = "WM Load x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violindduration <- Nback_blocks %>% 
  ggplot(aes(duration, dprime, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "Task Duration", title = "Duration x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))

violindILI <- Nback_blocks %>% 
  ggplot(aes(ILI, dprime, colour = ILI)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "D'", x = "ILI", title = "ILI x D'") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("D' distribution vs Design",
    fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violindnback + theme(plot.margin = margin(0, 30, 0, 0)),
  violindduration + theme(plot.margin = margin(0, 10, 0, 0)),
                           violindILI + theme(plot.margin = margin(0, 10, 0, 0)), nrow=1)
          
# jpeg("ViolinD'pro.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
# jpeg("ViolinD'WMloadSC.jpg", width = 2500, height = 2500, units = "px",res=600)
violindnback
# dev.off()
  
# jpeg("ViolinD'durationSC.jpg", width = 2500, height = 2500, units = "px",res=600)
violindduration
# dev.off()

# jpeg("ViolinD'ILISC.jpg", width = 2500, height = 3000, units = "px",res=600)
violindILI
# dev.off()
  
```



##Models for Bias (log(Beta))
```{r}


MB1 <-lmer(logbeta ~ duration + (1|PID), data=data,  REML=FALSE)

MB2 <-lmer(logbeta ~ duration + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MB1, MB2)  #p < 0.05 -> More complex model (MB2) not significantly better than MB1

MB3 <-lmer(logbeta ~ duration + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB1, MB3) #p < 0.05 -> More complex model (MB3) significantly better than MB1

MB4 <-lmer(logbeta ~ duration * nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB3, MB4)  #p < 0.05 -> More complex model (MB4) significantly better than MB3

MB5 <-lmer(logbeta ~ ILI * duration + nback +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB5)  #p < 0.05 -> More complex model (MB5) significantly better than MB4 but MB4 has a better AIC

MB6 <-lmer(logbeta ~ ILI * nback + duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB6) #p < 0.05 -> More complex model (MB6) significantly better than MB4 but MB4 has a better AIC

MB7 <-lmer(logbeta ~ ILI * nback * duration +(1|PID), data=data,  REML=FALSE)
lrtest(MB4, MB7) #p < 0.05 -> More complex model (MB7) significantly better than MB4  but MODERATE COLLINEARITY

MB8 <-lmer(logbeta ~ ILI * nback * duration +(nback|PID), data=data,  REML=FALSE)
lrtest(MB7, MB8) #p < 0.05 -> More complex model (MB8) significantly better than MB7    but MODERATE COLLINEARITY

MB9 <-lmer(logbeta ~ ILI * nback * duration +(nback + duration|PID), data=data,  REML=FALSE)
lrtest(MB8, MB9) #p < 0.05 -> More complex model (MB9) significantly better than MB8 BUT SINGULAR

MB10 <-lmer(logbeta ~ ILI * nback * duration +(nback + ILI|PID), data=data,  REML=FALSE)
lrtest(MB8, MB10) #p < 0.05 -> More complex model (MB10) significantly better than MB8 BUT SINGULAR

MB11 <-lmer(logbeta ~ ILI * nback * duration +(nback + ILI + duration|PID), data=data,  REML=FALSE)
lrtest(MB9, MB11) #p > 0.05 -> More complex model (MB11) not significantly better than MB8 BUT SINGULAR

compare_performance(MB1, MB2, MB3, MB4, MB5, MB6, MB7, MB8, MB9, MB10, MB11) #among non singular MB8 -> best AIC, then MB7 and MB4


summary(MB3)
summary(MB4)  
summary(MB5)
summary(MB6)
summary(MB7)
summary(MB8) #best model MB9 --> shows significative  effects of ILI, duration, nback and dinteraction on Bias
summary(MB9)
summary(MB10)
summary(MB11)



MB8 <-lmer(logbeta ~ ILI * nback * duration +(nback|PID), data=data,  REML=T)
summary(MB8)
stargazer(MB8, type = "text",
           title = "Regression results MB8",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

emmeans(MB8, ~nback,  lmer.df = "satterthwaite")
emmeans(MB8, ~duration,  lmer.df = "satterthwaite")
emmeans(MB8, ~ILI,  lmer.df = "satterthwaite")
emmeans(MB8, pairwise ~ILI + nback,  lmer.df = "satterthwaite")
emmeans(MB8, pairwise ~ duration + nback,  lmer.df = "satterthwaite")
emmeans(MB8, pairwise ~ILI + duration,  lmer.df = "satterthwaite")

#Does MB8 meet assumptions ?

check_autocorrelation(MB8)
durbinWatsonTest(resid(MB8)) # = 2 no autocorrelation


check_heteroscedasticity(MB8) #not OK, but graphically OK
check_collinearity(MB8) #OK

plot(MB8)
qqnorm(residuals(MB8))

## residuals distribution : histogramme and shapiro test for normality
hist(resid(MB8), breaks = 30)

## homogeneity : fitted values vs normalized residuals
plot(x = data$logbeta, 
     y = resid(MB8), 
     xlab = "Bias",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

## independance : residuals vs each model covariable

boxplot(resid(MB8) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(MB8) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(MB8) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)
```



##Bias violin plot
```{r}

violinBiasnback <- Nback_blocks %>% 
  ggplot(aes(nback, logbeta, colour = nback)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "WM Load", title = "WM Load x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back","3back")))


violinBiasduration <- Nback_blocks %>% 
  ggplot(aes(duration, logbeta, colour = duration)) +
  geom_violin() +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
  stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "Task Duration", title = "Duration x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means( method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("45s","90s")))


violinBiasILI <- Nback_blocks %>% 
  ggplot(aes(ILI, logbeta, colour = ILI)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
   geom_hline(aes(yintercept = 0), colour = 'black', size = .3, linetype = "dashed") +
stat_summary(fun = mean)  +
  theme_classic() +
  labs(y = "Bias", x = "ILI", title = "ILI x Bias") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette2) +
   stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1500ms","1800ms")))


#Merge the two graphs
title <- ggdraw() + draw_label("Bias distribution vs Task Duration, ILI and WM Load", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row = plot_grid(violinBiasnback, violinBiasduration, violinBiasILI, nrow=1)
          
# jpeg("ViolinBiasproSC.jpg", width = 5000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
  
  
#INTERATIONS  
  violinBiasdurationnback <- Nback_blocks %>% 
    mutate(nbackduration = paste(nback, duration),
           nbackduration =  fct_relevel(nbackduration, "1back 45s", "3back 45s", "1back 90s", "3back 90s")) %>%
  ggplot(aes(nbackduration, logbeta, colour = nbackduration)) +
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
stat_summary(fun = mean)  +
      # facet_grid(ILI~.) +
  theme_classic() +
  labs(y = "Bias", x = "WM Load : Task Duration", title = "Bias for different WM Load and Task Duration") +
  theme( legend.position="none",
        axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
  scale_colour_manual(values = cbPalette4) 
  
   # stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", comparisons = list(c("1back45s","3back45S"), c("1back90s","3back90S"))) +
   
     

jpeg("violinBiasprointeractionSC.jpg", width = 5000, height = 3500, units = "px",res=600)
  violinBiasdurationnback
dev.off()
```





## Models for mRT
```{r}

MRT1 <-lmer(mRT ~ duration + (1|PID), data=data,  REML=FALSE)


MRT2 <- lmer(mRT ~ duration + ILI +(1|PID), data=data,  REML=FALSE)
lrtest(MRT1, MRT2) #p < 0.05 -> More complex model (MRT2) significantly better than MRT1

MRT3 <- lmer(mRT ~ duration + ILI + nback + (1|PID), data=data,  REML=FALSE)
lrtest(MRT2, MRT3) #p < 0.05 -> More complex model (MRT3) significantly better than MRT2

MRT4 <- lmer(mRT ~ duration + nback * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT3, MRT4) #p > 0.05 -> More complex model (MRT4) is not significantly better than MRT3

MRT5 <- lmer(mRT ~ nback + duration * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT4, MRT5) #p > 0.05 -> More complex model (MRT5)is significantly better than MRT3 and has a better AIC

MRT6 <- lmer(mRT ~ duration * nback + ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT5, MRT6) #p < 0.05 -> More complex model (MRT6) is significantly better than MRT5 and has a better AIC

MRT10 <- lmer(mRT ~ duration * nback * ILI + (1|PID), data=data,  REML=FALSE)
lrtest(MRT6, MRT10)

MRT7 <- lmer(mRT ~ duration * nback + ILI + (nback|PID), data=data,  REML=FALSE)
lrtest(MRT6, MRT7) #p < 0.05 -> More complex model (MRT7) significantly better than MRT6 and has a better AIC

MRT8 <- lmer(mRT ~ duration * nback + ILI + (nback + ILI|PID), data=data,  REML=FALSE)
lrtest(MRT8, MRT7) #p < 0.05 -> More complex model (MRT7) significantly better than MRT6 BUT SINGULAR

MRT9 <- lmer(mRT ~ duration * nback + ILI + (nback + duration|PID), data=data,  REML=FALSE)
lrtest(MRT9, MRT8) #p < 0.05 -> More complex model (MRT8) significantly better than MRT7 BUT SINGULAR

compare_performance(MRT1, MRT2, MRT3, MRT4, MRT5, MRT6, MRT7, MRT8, MRT9) #MRT7, 8 & 9 -> best AIC but 8 and 9 singular

summary(MRT1)
summary(MRT2) 
summary(MRT4)
summary(MRT5)
summary(MRT6)
summary(MRT7)#best model --> shows significative effects of duration and ILI on mean Reaction Time
summary(MRT8)#fit is singular !
summary(MRT9)#fit is singular !



MRT7 <-lmer(mRT ~ duration * nback + ILI + (nback|PID), data=data,  REML=T)
summary(MRT7)
stargazer(MRT7, type = "text",
           title = "Regression results Md7",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")

emmeans(MRT7, ~nback,  lmer.df = "satterthwaite")
emmeans(MRT7, ~duration,  lmer.df = "satterthwaite")
emmeans(MRT7, ~ILI,  lmer.df = "satterthwaite")
emmeans(MRT7, pairwise ~nback * duration,  lmer.df = "satterthwaite")

#Does MRT7 meet assumptions ?

check_heteroscedasticity(MRT7) #not OK, but graphically OK
check_collinearity(MRT7) #OK


check_autocorrelation(MRT7)
durbinWatsonTest(resid(MRT7)) #= 1.6  =~ 2 no autocorrelation


## residuals distribution : histogramme 
hist(resid(MRT7), breaks = 50)


## homogeneity : fitted values vs normalized residuals


plot(x = data$mRT, 
     y = resid(MRT7), 
     xlab = "mRT",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

plot(MRT7)

## independance : residuals vs each model covariable

boxplot(resid(MRT7) ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

boxplot(resid(MRT7) ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)

boxplot(resid(MRT7) ~ ILI,   
        ylab = "Normalized residuals",
        data = data, xlab = "ILI")
abline(h = 0, lty = 2)
```


##mRT violin plot
```{r}
mRTILI <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = ILI, colour = ILI)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "RT (ms)", x ="ILI") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1400, comparison = list(c("1500ms", "1800ms")))


mRTDuration <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = duration, colour = duration)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "RT (ms)", x ="Task Duration") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), axis.title = element_text(size = 12)) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  scale_colour_manual(values = cbPalette2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1390, comparison = list(c("45s", "90s")))


mRTDnback <- Nback_blocks %>% 
   ggplot(aes(y = mRT, x = nback, colour = nback)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "RT (ms)", x ="WM Load") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), axis.title = element_text(size = 12)) +
  scale_y_continuous(breaks = seq(from = 200, to = 1400, by = 200),
                     limits = c(150, 1500)) +
  scale_colour_manual(values = cbPalette4) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 1390, comparison = list(c("1back", "3back")))


title <- ggdraw() + draw_label("RT for different design", 
                               fontface = 'bold', size = 13) + theme(plot.margin = margin(0, 5, 10 ,0))

plot_row <- plot_grid(mRTDnback, mRTILI,  nrow=1)
          
# jpeg("mRTViolinproSC.jpg", width = 3000, height = 2500, units = "px",res=600)
  plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
# dev.off()
  
  
#   #INTERATIONS  
#   violinmRTdurationnback <- Nback_blocks %>% 
#     mutate(nbackduration = paste(nback, duration),
#            nbackduration =  fct_relevel(nbackduration, "1back 45s", "3back 45s", "1back 90s", "3back 90s")) %>%
#   ggplot(aes(nbackduration, mRT, colour = nbackduration)) +
#   geom_violin(outlier.shape=NA) +
#   geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
#   geom_hline(aes(yintercept = 0), colour = 'black', size = 0.3, linetype = "dashed") +
# stat_summary(fun = mean)  +
#   theme_classic() +
#   labs(y = "mRT", x = "WM Load : Task Duration", title = "Bias for different WM Load and Task Duration") +
#   theme( legend.position="none",
#         axis.title.x = element_text(size = 12),
#          axis.title.y = element_text(size = 12),
#         axis.text = element_text(size = 12),
#   plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) + 
#   scale_colour_manual(values = cbPalette4) 
#   
#   # jpeg("violinmRTsprointeraction.jpg", width = 5000, height = 3500, units = "px",res=600)
#   violinmRTdurationnback
# # dev.off()
```











# RELATIVE DURATION ESTIMATION MODELS






## Mixed-effect models rDE
```{r}
data <- Nback_blocks  #2214

M1 <-lmer(relative_timing ~ duration + (1|PID), data=data, REML=FALSE)

M2 <-lmer(relative_timing ~ duration + nback + (1|PID), data=data, REML=FALSE)
lrtest(M1, M2) #M1 nested #M2 more complex   p <0.05  #the complex model is significantly more accurate

M3 <-lmer(relative_timing ~ duration + nback + ILI + (1|PID), data=data, REML=FALSE)
lrtest(M2, M3) #M2 nested #M3 more complex  p > 0.05  #the complex model is not significantly more accurate

M4 <-lmer(relative_timing ~ duration + nback + dprime + (1|PID), data=data, REML=FALSE)
lrtest(M2, M4)   #M2 nested #M4 more complex      p > 0.05  #the complex model is not significantly more accurate

M5 <-lmer(relative_timing ~ duration + nback + logbeta + (1|PID), data=data, REML=FALSE)
lrtest(M2, M5)  #M2 nested #5 more complex    p > 0.05  #the complex model is not significantly more accurate

M6 <-lmer(relative_timing ~ nback + duration + dprime * ILI + (1|PID), data=data, REML=FALSE)
lrtest(M2, M6)   #M2 nested #6 more complex   p > 0.05  #the complex model is  not significantly more accurate

M7 <-lmer(relative_timing ~ nback + dprime * duration + (1|PID), data=data, REML=FALSE)
lrtest(M2, M7)   #M2 nested #7 more complex   p > 0.05  #the complex model is not significantly more accurate

M8 <-lmer(relative_timing ~ duration + nback * dprime + (1|PID), data=data, REML=FALSE)
lrtest(M2, M8)   #M2 nested #8 more complex   p > 0.05  #the complex model is not significantly more accurate


M9 <-lmer(relative_timing ~ duration + nback + logbeta * dprime + (1|PID), data=data, REML=FALSE)
lrtest(M2, M9)   #M2 nested #9 more complex   p > 0.05  #the complex model is not significantly more accurate

M10 <-lmer(relative_timing ~ duration + nback * logbeta + (1|PID), data=data, REML=FALSE)
lrtest(M2, M10)   #M2 nested #10 more complex   p > 0.05  #the complex model is not significantly more accurate

M11 <-lmer(relative_timing ~ duration * logbeta + nback + (1|PID), data=data, REML=FALSE)
lrtest(M2, M11)   #M2 nested #11 more complex   p > 0.05  #the complex model is not significantly more accurate

M12 <-lmer(relative_timing ~ duration + ILI * logbeta + nback + (1|PID), data=data, REML=FALSE)
lrtest(M2, M12)   #M2 nested #11 more complex   p > 0.05  #the complex model is not significantly more accurate

M13 <-lmer(relative_timing ~ duration + nback + (nback|PID), data=data, REML=FALSE)
lrtest(M2, M13) #M2 nested #M13 more complex   p <0.05  #the complex model is significantly more accurate

M14 <-lmer(relative_timing ~ duration + nback + (nback + duration|PID), data=data, REML=FALSE)
lrtest(M13, M14) #M13 nested #M14 more complex   p <0.05  #the complex model is significantly more accurate

M15 <-lmer(relative_timing ~ duration + nback + (nback + duration + logbeta|PID), data=data, REML=FALSE)
lrtest(M14, M15) #M14 nested #M15 more complex   p <0.05  #the complex model is significantly more accurate but add a small explaination of the variance

#add ILI, d' as a random effect slope yields in "boundary singular error" or the model failed to converge


summary(M1)
summary(M2)
summary(M3)
summary(M4)
summary(M5)
summary(M6)
summary(M7)
summary(M8)
summary(M9)
summary(M10)
summary(M11)
summary(M12)
summary(M13) 
summary(M14) #Best !
summary(M15)

compare_performance(M1, M2, M3, M4, M5, M6, M7, M8, M9, M10, M11, M12, M13, M14, M15) #M14 and M15 best AIC




```

#Main effects
```{r}
library("stargazer")

M2 <-lmer(relative_timing ~ duration + nback + (1|PID), data=data, REML=T)

summary(M2)
stargazer(M2, type = "text",
           title = "Regression results M2",
          header = FALSE,
          single.row = TRUE,
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")


# -- Main effect of duration --   => Significant effect
emmeans(M14, ~ duration) 

# -- Main effect of WM Load --    => Significant effect
emmeans(M14, ~ nback,  lmer.df = "satterthwaite") 

# emmeans(M13,  ~ dprime, at = list(dprime = c(1, 2, 3, 4,5)))

# -- Main effect of Interaction duration / nback 

# emmeans(M13, pairwise ~ duration | nback,  lmer.df = "satterthwaite")
# 
# emmeans(M13, pairwise ~ nback | duration,  lmer.df = "satterthwaite")  


# emmeans(M13, pairwise ~ dprime | duration, at = list(dprime = c(1, 2, 3, 4,5)))
```

# Verification of model assumptions ####
```{r}

R1 <- resid(M14)
F1 <- fitted(M14)

## residuals distribution : histogramme and shapiro test for normality
hist(R1, breaks = 30)

# shapiro.test(R1)

## homogeneity : fitted values vs normalized residuals

plot(x = F1, 
     y = R1, 
     xlab = "Fitted Values",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)

#timing_error
plot(x = data$relative_timing, 
     y = R1, 
     xlab = "relative_timing",
     ylab = "Normalized residuals")
abline(h = 0, lty = 2)


## independance : residuals vs each model covariable

# duration
boxplot(R1 ~ duration,   
        ylab = "Normalized residuals",
        data = data, xlab = "task duration")
abline(h = 0, lty = 2)

# nback
boxplot(R1 ~ nback,   
        ylab = "Normalized residuals",
        data = data, xlab = "nback")
abline(h = 0, lty = 2)



# data %>%
#  ggplot(aes(timing_error, R1, colour = dprime)) + 
#            geom_point() +
#       # geom_density(aes(y = ..density..*(500 * 0.02)), alpha=.4, fill="lightgreen") +
#   labs(y = "residuals", x = "timing_error", title ="model for 1-back retrospective tasks, residuals vs TE") + 
#   theme(plot.title = element_text(face = "bold", "hjust" = 0.5)) 
#   # scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
#   #                limits = c(-0.01,1.01))



check_heteroscedasticity(M14) #not OK, but graphically OK:
plot(M14)

check_autocorrelation(M14)
durbinWatsonTest(resid(M14)) # =~ 2 (1.6) no autocorrelation


```





##D' effect on Relative Duration Estimation - Visualization
```{r}

#with linear regression
# jpeg("d'pointpro.jpg", width = 2500, height = 2500, units = "px",res=600)
Nback_blocks %>%
  ggplot(aes(dprime, relative_timing)) +
  geom_point(size = 0.1) +
  geom_smooth(method="lm", fill="#69b3a2", se= T) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .3, linetype = "dashed") +
  theme_classic() +
   # scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
   #                   limits = c(0, 2.7)) +
   labs(y = "rDE", x = "d'", title = "Relative Duration Estimation vs D'") +
  theme(axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 12),
  plot.title = element_text("hjust" = 0.5), axis.title= element_text(size = 13)) 
# dev.off()


#with mixed-effect model regression

#D' 
predictions <- summary(emmeans(M13, ~ dprime, at = list(dprime = seq(0,5, by = 0.01))))

jpeg("predictionpro.jpg", width = 2500, height = 2500, units = "px",res=600)
ggplot(data, aes(dprime, relative_timing)) +
geom_point(size = 0.1) +
    geom_hline(aes(yintercept = 1), colour = 'black', size = .5, linetype = "dashed") +
  theme_classic() +
     scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
geom_point(predictions, colour ="blue", mapping = aes(y= emmean), size = 0.1) +
  labs(y = "rDE", x = "d'")
# dev.off()
```


##WM Load effect on Relative Duration Estimation - Visualization
```{r}
# jpeg("violinWMLoadrDEproSC.jpg", width = 2500, height = 2500, units = "px",res=600)

Nback_blocks %>% 
   ggplot(aes(y = relative_timing, x = nback, colour = nback)) + 
  geom_violin(outlier.shape=NA) +
  geom_boxplot(width=0.2, color="black", alpha=0.6, outlier.shape=NA) +
  geom_hline(aes(yintercept = 1), colour = 'black', size = .3, linetype = "dashed") +
  scale_y_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
  stat_summary(fun = mean)  +
   theme_classic() +  
  labs(y = "rDE", x ="WM Load") + 
  theme(plot.title = element_text(face = "bold", "hjust" = 0.3)) +
  theme( legend.position="none",
          axis.text = element_text(size = 11), 
 axis.title = element_text(size = 12)) +
  scale_colour_manual(values = cbPalette2_v2) +
 stat_compare_means(method = "wilcox.test", paired = FALSE, label = "p.format", 
                    label.y = 2.55, comparison = list(c("1back", "3back")))
# dev.off()


```







